\chapter{Dimensions}
\label{chap:dimensions}
{\small
\begin{center}
\begin{longtable}{| p{1.0in} || p{1.0in} | p{4.0in} |}
    \hline 
    {\bf Name} & {\bf Units} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Units} & {\bf Description} (Continued) \endhead
    \hline 
    \hline 
    nCells & \si{unitless} & The number of polygons in the primary grid. \\ 
    \hline
    nEdges & \si{unitless} & The number of edge midpoints in either the primary or dual grid. \\ 
    \hline
    maxEdges & \si{unitless} & The largest number of edges any polygon within the grid has. \\ 
    \hline
    maxEdges2 & \si{unitless} & Two times the largest number of edges any polygon within the grid has. \\ 
    \hline
    nVertices & \si{unitless} & The total number of cells in the dual grid. Also the number of corners in the primary grid. \\ 
    \hline
    ONE & \si{unitless} & The number one as a dimension. \\ 
    \hline
    TWO & \si{unitless} & The number two as a dimension. \\ 
    \hline
    R3 & \si{unitless} & The number three as a dimension. \\ 
    \hline
    vertexDegree & \si{unitless} & The number of cells or edges touching each vertex. \\ 
    \hline
    nVertLevels & \si{unitless} & The number of levels in the vertical direction. All vertical levels share the same horizontal locations. \\ 
    \hline
    nVertInterfaces & \si{unitless} & The number of interfaces in the vertical direction. \\ 
    \hline
    maxTracersAdvect & \si{unitless} & The maximum number of tracers to be advected. \\ 
    \hline
    nRegions & \si{unitless} & The number of regions used for AM\_regionalStats \\ 
    \hline
    nRegionGroups & \si{unitless} & The number of region groups used for AM\_regionalStats \\ 
    \hline
    maxRegionsInGroup & \si{unitless} & The maximum number of regions in a region group used for AM\_regionalStats \\ 
    \hline
\end{longtable}
\end{center}
}
