\chapter[Namelist options]{\hyperref[chap:namelist_sections]{Namelist options}}
\label{chap:namelist_tables}
Embedded links point to more detailed namelist information in the appendix.
\section[velocity\_solver]{\hyperref[sec:nm_sec_velocity_solver]{velocity\_solver}}
\label{sec:nm_tab_velocity_solver}
\input{landice/section_descriptions/velocity_solver.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hline
	\hyperref[subsec:nm_sec_config_velocity_solver]{config\_velocity\_solver} & Selection of the method for solving ice velocity. \\
	\hline
\end{longtable}
\end{center}
}
\section[advection]{\hyperref[sec:nm_sec_advection]{advection}}
\label{sec:nm_tab_advection}
\input{landice/section_descriptions/advection.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hline
	\hyperref[subsec:nm_sec_config_thickness_advection]{config\_thickness\_advection} & Selection of the method for advecting thickness. \\
	\hline
	\hyperref[subsec:nm_sec_config_tracer_advection]{config\_tracer\_advection} & Selection of the method for advecting tracers. \\
	\hline
\end{longtable}
\end{center}
}
\section[physical\_parameters]{\hyperref[sec:nm_sec_physical_parameters]{physical\_parameters}}
\label{sec:nm_tab_physical_parameters}
\input{landice/section_descriptions/physical_parameters.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hline
	\hyperref[subsec:nm_sec_config_ice_density]{config\_ice\_density} & ice density to use \\
	\hline
	\hyperref[subsec:nm_sec_config_ocean_density]{config\_ocean\_density} & ocean density to use for calculating floatation \\
	\hline
	\hyperref[subsec:nm_sec_config_sea_level]{config\_sea\_level} & sea level to use for calculating floatation \\
	\hline
	\hyperref[subsec:nm_sec_config_default_flowParamA]{config\_default\_flowParamA} & Defines the default value of the flow law parameter A to be used if it is not being calculated from ice temperature.  Defaults to the SI representation of 1.0e-16 yr$^{-1}$ Pa$^{-3}$. \\
	\hline
	\hyperref[subsec:nm_sec_config_flowLawExponent]{config\_flowLawExponent} & Defines the value of the Glen flow law exponent, n. \\
	\hline
	\hyperref[subsec:nm_sec_config_dynamic_thickness]{config\_dynamic\_thickness} & Defines the ice thickness below which dynamics are not calculated. \\
	\hline
\end{longtable}
\end{center}
}
\section[time\_integration]{\hyperref[sec:nm_sec_time_integration]{time\_integration}}
\label{sec:nm_tab_time_integration}
\input{landice/section_descriptions/time_integration.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hline
	\hyperref[subsec:nm_sec_config_dt_years]{config\_dt\_years} & Length of model time-step in years.  Will be used instead of config\_dt\_seconds if greater than zero.  Currently the model assumes there are 365.0 * 24.0 * 3600.0 seconds in a year and the calendar type is not considered for this conversion. \\
	\hline
	\hyperref[subsec:nm_sec_config_dt_seconds]{config\_dt\_seconds} & Length of model time-step in seconds.  This value will only be used if config\_dt\_years is less than or equal to zero. \\
	\hline
	\hyperref[subsec:nm_sec_config_time_integration]{config\_time\_integration} & Time integration method. \\
	\hline
\end{longtable}
\end{center}
}
\section[time\_management]{\hyperref[sec:nm_sec_time_management]{time\_management}}
\label{sec:nm_tab_time_management}
\input{landice/section_descriptions/time_management.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hline
	\hyperref[subsec:nm_sec_config_do_restart]{config\_do\_restart} & Determines if the initial conditions should be read from a restart file, or an input file.  To perform a restart, simply set this to true in the namelist.input file and modify the start time to be the time you want restart from.  A restart will read the grid information from the input field, and the restart state from the restart file.  It will perform a run normally, i.e. do all the same init. \\
	\hline
	\hyperref[subsec:nm_sec_config_start_time]{config\_start\_time} & Timestamp describing the initial time of the simulation.  If it is set to 'file', the initial time is read from restart\_timestamp \\
	\hline
	\hyperref[subsec:nm_sec_config_stop_time]{config\_stop\_time} & Timestamp describing the final time of the simulation. If it is set to 'none' the final time is determined from config\_start\_time and config\_run\_duration.  If config\_run\_duration is also specified, it takes precedence over config\_stop\_time.  Set config\_stop\_time to be equal to config\_start\_time (and config\_run\_duration to 'none') to perform a diagnostic solve of velocity. \\
	\hline
	\hyperref[subsec:nm_sec_config_run_duration]{config\_run\_duration} & Timestamp describing the length of the simulation. If it is set to 'none' the duration is determined from config\_start\_time and config\_stop\_time. config\_run\_duration overrides inconsistent values of config\_stop\_time. If a time value is specified for config\_run\_duration, it must be greater than 0. \\
	\hline
	\hyperref[subsec:nm_sec_config_calendar_type]{config\_calendar\_type} & Selection of the type of calendar that should be used in the simulation. \\
	\hline
\end{longtable}
\end{center}
}
\section[io]{\hyperref[sec:nm_sec_io]{io}}
\label{sec:nm_tab_io}
\input{landice/section_descriptions/io.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hline
	\hyperref[subsec:nm_sec_config_input_name]{config\_input\_name} & The path to the input file for the simulation. \\
	\hline
	\hyperref[subsec:nm_sec_config_output_name]{config\_output\_name} & The template path and name to the output file from the simulation. A time stamp is prepended to the extension of the file (.nc). \\
	\hline
	\hyperref[subsec:nm_sec_config_restart_name]{config\_restart\_name} & The template path and name to the restart file for the simulation. A time stamp is prepended to the extension of the file (.nc) both for input and output. \\
	\hline
	\hyperref[subsec:nm_sec_config_restart_timestamp_name]{config\_restart\_timestamp\_name} & The name of the file to which the timestamp of the latest restart file is written. This file is subsequently used to set the start time when config\_start\_time is set to 'file' and config\_do\_restart is set to .true. \\
	\hline
	\hyperref[subsec:nm_sec_config_restart_interval]{config\_restart\_interval} & Timestamp determining how often a restart file should be written.  Currently years and months are not supported, so you have to specify the restart interval in units of days! **  We could eventually propose a change to framework to fix this in subroutine mpas\_set\_timeInterval in mpas\_timekeeping module. \\
	\hline
	\hyperref[subsec:nm_sec_config_output_interval]{config\_output\_interval} & Timestamp determining how often an output file should be written. \\
	\hline
	\hyperref[subsec:nm_sec_config_stats_interval]{config\_stats\_interval} & Timestamp determining how often a global statistics files should be written. \\
	\hline
	\hyperref[subsec:nm_sec_config_write_stats_on_startup]{config\_write\_stats\_on\_startup} & Logical flag determining if statistics files should be written prior to the first time step. \\
	\hline
	\hyperref[subsec:nm_sec_config_write_output_on_startup]{config\_write\_output\_on\_startup} & Logical flag determining if an output file should be written prior to the first time step. \\
	\hline
	\hyperref[subsec:nm_sec_config_frames_per_outfile]{config\_frames\_per\_outfile} & Integer specifying how many time frames should be included in an output file. Once the maximum is reached, a new output file is created.  If 0 (or less) is specified then all time frames are included in a single file called 'output.nc'. \\
	\hline
	\hyperref[subsec:nm_sec_config_pio_num_iotasks]{config\_pio\_num\_iotasks} & Integer specifying how many IO tasks should be used within the PIO library. A value of 0 causes all MPI tasks to also be IO tasks. IO tasks are required to write contiguous blocks of data to a file. \\
	\hline
	\hyperref[subsec:nm_sec_config_pio_stride]{config\_pio\_stride} & Integer specifying the stride of each IO task. \\
	\hline
\end{longtable}
\end{center}
}
\section[decomposition]{\hyperref[sec:nm_sec_decomposition]{decomposition}}
\label{sec:nm_tab_decomposition}
\input{landice/section_descriptions/decomposition.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hline
	\hyperref[subsec:nm_sec_config_num_halos]{config\_num\_halos} & Determines the number of halo cells extending from a blocks owned cells (Called the 0-Halo). The default of 3 is the minimum that can be used with monotonic advection. \\
	\hline
	\hyperref[subsec:nm_sec_config_block_decomp_file_prefix]{config\_block\_decomp\_file\_prefix} & Defines the prefix for the block decomposition file. Can include a path. The number of blocks is appended to the end of the prefix at run-time. \\
	\hline
	\hyperref[subsec:nm_sec_config_number_of_blocks]{config\_number\_of\_blocks} & Determines the number of blocks a simulation should be run with. If it is set to 0, the number of blocks is the same as the number of MPI tasks at run-time. \\
	\hline
	\hyperref[subsec:nm_sec_config_explicit_proc_decomp]{config\_explicit\_proc\_decomp} & Determines if an explicit processor decomposition should be used. This is only useful if multiple blocks per processor are used. \\
	\hline
	\hyperref[subsec:nm_sec_config_proc_decomp_file_prefix]{config\_proc\_decomp\_file\_prefix} & Defines the prefix for the processor decomposition file. This file is only read if config\_explicit\_proc\_decomp is .true. The number of processors is appended to the end of the prefix at run-time. \\
	\hline
\end{longtable}
\end{center}
}
\section[debug]{\hyperref[sec:nm_sec_debug]{debug}}
\label{sec:nm_tab_debug}
\input{landice/section_descriptions/debug.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hline
	\hyperref[subsec:nm_sec_config_print_thickness_advection_info]{config\_print\_thickness\_advection\_info} & Prints additional information about thickness advection. \\
	\hline
\end{longtable}
\end{center}
}
