\section{Dimensions}
\label{sec:forward_dimensions}
{\small
\begin{center}
\begin{longtable}{| p{1.2in} || p{1.0in} | p{4.0in} |}
	\hline 
	{\bf Name} & {\bf Units} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Units} & {\bf Description} (Continued) \endhead
	\hline 
	\hline 
	nCells & $unitless$ & The number of polygons in the primary grid. \\ 
	\hline
	nEdges & $unitless$ & The number of edge midpoints in either the primary or dual grid. \\ 
	\hline
	maxEdges & $unitless$ & The largest number of edges any polygon within the grid has. \\ 
	\hline
	maxEdges2 & $unitless$ & Two times the largest number of edges any polygon within the grid has. \\ 
	\hline
	nVertices & $unitless$ & The total number of cells in the dual grid. Also the number of corners in the primary grid. \\ 
	\hline
	TWO & $unitless$ & The number two as a dimension. \\ 
	\hline
	R3 & $unitless$ & The number three as a dimension. \\ 
	\hline
	vertexDegree & $unitless$ & The number of cells or edges touching each vertex. \\ 
	\hline
	nVertLevels & $unitless$ & The number of levels in the vertical direction. All vertical levels share the same horizontal locations. \\ 
	\hline
	nVertLevelsP1 & $unitless$ & The number of interfaces in the vertical direction. \\ 
	\hline
\end{longtable}
\end{center}
}
\section[Namelist options]{\hyperref[chap:namelist_sections]{Namelist options}}
\label{sec:forward_namelist_tables}
Embedded links point to more detailed namelist information in the appendix.
\subsection[velocity\_solver]{velocity\_solver}
\label{subsec:forward_nm_tab_velocity_solver}
\input{landice/section_descriptions/velocity_solver.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hline
	\hyperref[sec:nm_sec_config_velocity_solver]{config\_velocity\_solver} & Selection of the method for solving ice velocity. \\
	\hline
\end{longtable}
\end{center}
}
\subsection[advection]{advection}
\label{subsec:forward_nm_tab_advection}
\input{landice/section_descriptions/advection.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hline
	\hyperref[sec:nm_sec_config_thickness_advection]{config\_thickness\_advection} & Selection of the method for advecting thickness. \\
	\hline
	\hyperref[sec:nm_sec_config_tracer_advection]{config\_tracer\_advection} & Selection of the method for advecting tracers. \\
	\hline
\end{longtable}
\end{center}
}
\subsection[physical\_parameters]{physical\_parameters}
\label{subsec:forward_nm_tab_physical_parameters}
\input{landice/section_descriptions/physical_parameters.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hline
	\hyperref[sec:nm_sec_config_ice_density]{config\_ice\_density} & ice density to use \\
	\hline
	\hyperref[sec:nm_sec_config_ocean_density]{config\_ocean\_density} & ocean density to use for calculating floatation \\
	\hline
	\hyperref[sec:nm_sec_config_sea_level]{config\_sea\_level} & sea level to use for calculating floatation \\
	\hline
	\hyperref[sec:nm_sec_config_default_flowParamA]{config\_default\_flowParamA} &  Defines the default value of the flow law parameter A to be used if it is not being calculated from ice temperature.  Defaults to the SI representation of 1.0e-16 yr $^{-1}$  Pa $^{-3}$ . \\
	\hline
	\hyperref[sec:nm_sec_config_flowLawExponent]{config\_flowLawExponent} & Defines the value of the Glen flow law exponent, n. \\
	\hline
	\hyperref[sec:nm_sec_config_dynamic_thickness]{config\_dynamic\_thickness} & Defines the ice thickness below which dynamics are not calculated. \\
	\hline
\end{longtable}
\end{center}
}
\subsection[time\_integration]{time\_integration}
\label{subsec:forward_nm_tab_time_integration}
\input{landice/section_descriptions/time_integration.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hline
	\hyperref[sec:nm_sec_config_dt]{config\_dt} & Length of model time step defined as a time interval. \\
	\hline
	\hyperref[sec:nm_sec_config_time_integration]{config\_time\_integration} & Time integration method. \\
	\hline
\end{longtable}
\end{center}
}
\subsection[time\_management]{time\_management}
\label{subsec:forward_nm_tab_time_management}
\input{landice/section_descriptions/time_management.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hline
	\hyperref[sec:nm_sec_config_do_restart]{config\_do\_restart} & Determines if the initial conditions should be read from a restart file, or an input file.  To perform a restart, simply set this to true in the namelist.input file and modify the start time to be the time you want restart from.  A restart will read the grid information from the input field, and the restart state from the restart file.  It will perform a run normally, except velocity will not be solved on a restart. \\
	\hline
	\hyperref[sec:nm_sec_config_restart_timestamp_name]{config\_restart\_timestamp\_name} & Path to the filename for restart timestamps to be read and written from. \\
	\hline
	\hyperref[sec:nm_sec_config_start_time]{config\_start\_time} & Timestamp describing the initial time of the simulation.  If it is set to 'file', the initial time is read from restart\_timestamp \\
	\hline
	\hyperref[sec:nm_sec_config_stop_time]{config\_stop\_time} & Timestamp describing the final time of the simulation. If it is set to 'none' the final time is determined from config\_start\_time and config\_run\_duration.  If config\_run\_duration is also specified, it takes precedence over config\_stop\_time.  Set config\_stop\_time to be equal to config\_start\_time (and config\_run\_duration to 'none') to perform a diagnostic solve only. \\
	\hline
	\hyperref[sec:nm_sec_config_run_duration]{config\_run\_duration} & Timestamp describing the length of the simulation. If it is set to 'none' the duration is determined from config\_start\_time and config\_stop\_time. config\_run\_duration overrides inconsistent values of config\_stop\_time. If a time value is specified for config\_run\_duration, it must be greater than 0. \\
	\hline
	\hyperref[sec:nm_sec_config_calendar_type]{config\_calendar\_type} & Selection of the type of calendar that should be used in the simulation. \\
	\hline
\end{longtable}
\end{center}
}
\subsection[io]{io}
\label{subsec:forward_nm_tab_io}
\input{landice/section_descriptions/io.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hline
	\hyperref[sec:nm_sec_config_write_output_on_startup]{config\_write\_output\_on\_startu-}\hyperref[sec:nm_sec_config_write_output_on_startup]{p}& Logical flag determining if an output file should be written prior to the first time step. \\
	\hline
	\hyperref[sec:nm_sec_config_pio_num_iotasks]{config\_pio\_num\_iotasks} & Integer specifying how many IO tasks should be used within the PIO library. A value of 0 causes all MPI tasks to also be IO tasks. IO tasks are required to write contiguous blocks of data to a file. \\
	\hline
	\hyperref[sec:nm_sec_config_pio_stride]{config\_pio\_stride} & Integer specifying the stride of each IO task. \\
	\hline
	\hyperref[sec:nm_sec_config_year_digits]{config\_year\_digits} & Integer specifying the number of digits used to represent the year in time strings. \\
	\hline
\end{longtable}
\end{center}
}
\subsection[decomposition]{decomposition}
\label{subsec:forward_nm_tab_decomposition}
\input{landice/section_descriptions/decomposition.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hline
	\hyperref[sec:nm_sec_config_num_halos]{config\_num\_halos} & Determines the number of halo cells extending from a blocks owned cells (Called the 0-Halo). The default of 3 is the minimum that can be used with monotonic advection. \\
	\hline
	\hyperref[sec:nm_sec_config_block_decomp_file_prefix]{config\_block\_decomp\_file\_prefix} & Defines the prefix for the block decomposition file. Can include a path. The number of blocks is appended to the end of the prefix at run-time. \\
	\hline
	\hyperref[sec:nm_sec_config_number_of_blocks]{config\_number\_of\_blocks} & Determines the number of blocks a simulation should be run with. If it is set to 0, the number of blocks is the same as the number of MPI tasks at run-time. \\
	\hline
	\hyperref[sec:nm_sec_config_explicit_proc_decomp]{config\_explicit\_proc\_decomp} & Determines if an explicit processor decomposition should be used. This is only useful if multiple blocks per processor are used. \\
	\hline
	\hyperref[sec:nm_sec_config_proc_decomp_file_prefix]{config\_proc\_decomp\_file\_prefix} & Defines the prefix for the processor decomposition file. This file is only read if config\_explicit\_proc\_decomp is .true. The number of processors is appended to the end of the prefix at run-time. \\
	\hline
\end{longtable}
\end{center}
}
\subsection[debug]{debug}
\label{subsec:forward_nm_tab_debug}
\input{landice/section_descriptions/debug.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} || p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hline
	\hyperref[sec:nm_sec_config_print_thickness_advection_info]{config\_print\_thickness\_advectio-}\hyperref[sec:nm_sec_config_print_thickness_advection_info]{n\_info}& Prints additional information about thickness advection. \\
	\hline
\end{longtable}
\end{center}
}
\section[Variable definitions]{\hyperref[chap:variable_sections]{Variable definitions}}
\label{sec:forward_variable_tables}
Embedded links point to more detailed variable information in the appendix.
\subsection[state]{\hyperref[sec:var_sec_state]{state}}
\label{subsec:forward_var_tab_state}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hyperref[subsec:var_sec_state_xtime]{xtime} & model time, with format 'YYYY-MM-DD\_HH:MM:SS' \\
	\hline
	\hyperref[subsec:var_sec_state_thickness]{thickness} & ice thickness \\
	\hline
	\hyperref[subsec:var_sec_state_layerThickness]{layerThickness} & layer thickness \\
	\hline
	\hyperref[subsec:var_sec_state_temperature]{temperature} & ice temperature \\
	\hline
	\hyperref[subsec:var_sec_state_lowerSurface]{lowerSurface} & elevation at bottom of ice \\
	\hline
	\hyperref[subsec:var_sec_state_upperSurface]{upperSurface} & elevation at top of ice \\
	\hline
	\hyperref[subsec:var_sec_state_layerThicknessEdge]{layerThicknessEdge} & layer thickness on cell edges \\
	\hline
	\hyperref[subsec:var_sec_state_upperSurfaceVertex]{upperSurfaceVertex} & elevation at top of ice on vertices (currently only needed by shallow ice solver) \\
	\hline
	\hyperref[subsec:var_sec_state_cellMask]{cellMask} & bitmask indicating various properties about the ice sheet on cells.  cellMask only needs to be a restart field if config\_allow\_additional\_advance = false (to keep the mask of initial ice extent) \\
	\hline
	\hyperref[subsec:var_sec_state_edgeMask]{edgeMask} & bitmask indicating various properties about the ice sheet on edges. \\
	\hline
	\hyperref[subsec:var_sec_state_vertexMask]{vertexMask} & bitmask indicating various properties about the ice sheet on vertices. \\
	\hline
	\hyperref[subsec:var_sec_state_normalVelocity]{normalVelocity} & horizonal velocity, normal component to an edge \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructX]{uReconstructX} & x-component of velocity reconstructed on cell centers \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructY]{uReconstructY} & y-component of velocity reconstructed on cell centers \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructZ]{uReconstructZ} & z-component of velocity reconstructed on cell centers \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructZonal]{uReconstructZonal} & zonal velocity reconstructed on cell centers \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructMeridional]{uReconstructMeridional} & meridional velocity reconstructed on cell centers \\
	\hline
\end{longtable}
\end{center}
}
\subsection[tend]{\hyperref[sec:var_sec_tend]{tend}}
\label{subsec:forward_var_tab_tend}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hyperref[subsec:var_sec_tend_tend_layerThickness]{tend\_layerThickness} & time tendency of layer thickness \\
	\hline
	\hyperref[subsec:var_sec_tend_tend_temperature]{tend\_temperature} & time tendency of ice temperature \\
	\hline
\end{longtable}
\end{center}
}
\subsection[mesh]{\hyperref[sec:var_sec_mesh]{mesh}}
\label{subsec:forward_var_tab_mesh}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \endfirsthead
	\hline 
	{\bf Name} & {\bf Description} (Continued) \endhead
	\hline
	\hyperref[subsec:var_sec_mesh_latCell]{latCell} & Latitude location of cell centers in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_lonCell]{lonCell} & Longitude location of cell centers in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_xCell]{xCell} & X Coordinate in cartesian space of cell centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_yCell]{yCell} & Y Coordinate in cartesian space of cell centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_zCell]{zCell} & Z Coordinate in cartesian space of cell centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_indexToCellID]{indexToCellID} & List of global cell IDs. \\
	\hline
	\hyperref[subsec:var_sec_mesh_latEdge]{latEdge} & Latitude location of edge midpoints in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_lonEdge]{lonEdge} & Longitude location of edge midpoints in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_xEdge]{xEdge} & X Coordinate in cartesian space of edge midpoints. \\
	\hline
	\hyperref[subsec:var_sec_mesh_yEdge]{yEdge} & Y Coordinate in cartesian space of edge midpoints. \\
	\hline
	\hyperref[subsec:var_sec_mesh_zEdge]{zEdge} & Z Coordinate in cartesian space of edge midpoints. \\
	\hline
	\hyperref[subsec:var_sec_mesh_indexToEdgeID]{indexToEdgeID} & List of global edge IDs. \\
	\hline
	\hyperref[subsec:var_sec_mesh_latVertex]{latVertex} & Latitude location of vertices in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_lonVertex]{lonVertex} & Longitude location of vertices in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_xVertex]{xVertex} & X Coordinate in cartesian space of vertices. \\
	\hline
	\hyperref[subsec:var_sec_mesh_yVertex]{yVertex} & Y Coordinate in cartesian space of vertices. \\
	\hline
	\hyperref[subsec:var_sec_mesh_zVertex]{zVertex} & Z Coordinate in cartesian space of vertices. \\
	\hline
	\hyperref[subsec:var_sec_mesh_indexToVertexID]{indexToVertexID} & List of global vertex IDs. \\
	\hline
	\hyperref[subsec:var_sec_mesh_cellsOnEdge]{cellsOnEdge} & List of cells that straddle each edge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_nEdgesOnCell]{nEdgesOnCell} & Number of edges that border each cell. \\
	\hline
	\hyperref[subsec:var_sec_mesh_nEdgesOnEdge]{nEdgesOnEdge} & Number of edges that surround each of the cells that straddle each edge. These edges are used to reconstruct the tangential velocities. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgesOnCell]{edgesOnCell} & List of edges that border each cell. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgesOnEdge]{edgesOnEdge} & List of edges that border each of the cells that straddle each edge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_weightsOnEdge]{weightsOnEdge} & Reconstruction weights associated with each of the edgesOnEdge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_dvEdge]{dvEdge} & Length of each edge, computed as the distance between verticesOnEdge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_dcEdge]{dcEdge} & Length of each edge, computed as the distance between cellsOnEdge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_angleEdge]{angleEdge} & Angle the edge normal makes with local eastward direction. \\
	\hline
	\hyperref[subsec:var_sec_mesh_areaCell]{areaCell} & Area of each cell in the primary grid. \\
	\hline
	\hyperref[subsec:var_sec_mesh_areaTriangle]{areaTriangle} & Area of each cell (triangle) in the dual grid. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgeNormalVectors]{edgeNormalVectors} & Normal vector defined at an edge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_localVerticalUnitVectors]{localVerticalUnitVectors} & Unit surface normal vectors defined at cell centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_cellTangentPlane]{cellTangentPlane} & The two vectors that define a tangent plane at a cell center. \\
	\hline
	\hyperref[subsec:var_sec_mesh_cellsOnCell]{cellsOnCell} & List of cells that neighbor each cell. \\
	\hline
	\hyperref[subsec:var_sec_mesh_verticesOnCell]{verticesOnCell} & List of vertices that border each cell. \\
	\hline
	\hyperref[subsec:var_sec_mesh_verticesOnEdge]{verticesOnEdge} & List of vertices that straddle each edge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgesOnVertex]{edgesOnVertex} & List of edges that share a vertex as an endpoint. \\
	\hline
	\hyperref[subsec:var_sec_mesh_cellsOnVertex]{cellsOnVertex} & List of cells that share a vertex. \\
	\hline
	\hyperref[subsec:var_sec_mesh_kiteAreasOnVertex]{kiteAreasOnVertex} & Area of the portions of each dual cell that are part of each cellsOnVertex. \\
	\hline
	\hyperref[subsec:var_sec_mesh_coeffs_reconstruct]{coeffs\_reconstruct} & Coefficients to reconstruct velocity vectors at cells centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgeSignOnCell]{edgeSignOnCell} & Sign of edge contributions to a cell for each edge on cell. Used for bit-reproducible loops. Represents directionality of vector connecting cells. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgeSignOnVertex]{edgeSignOnVertex} & Sign of edge contributions to a vertex for each edge on vertex. Used for bit-reproducible loops. Represents directionality of vector connecting vertices. \\
	\hline
	\hyperref[subsec:var_sec_mesh_layerThicknessFractions]{layerThicknessFractions} & Fractional thickness of each sigma layer \\
	\hline
	\hyperref[subsec:var_sec_mesh_layerCenterSigma]{layerCenterSigma} & Sigma (fractional) level at center of each layer \\
	\hline
	\hyperref[subsec:var_sec_mesh_layerInterfaceSigma]{layerInterfaceSigma} & Sigma (fractional) level at interface between each layer (including top and bottom) \\
	\hline
	\hyperref[subsec:var_sec_mesh_bedTopography]{bedTopography} & Elevation of ice sheet bed.  Once isostasy is added to the model, this should become a state variable. \\
	\hline
	\hyperref[subsec:var_sec_mesh_sfcMassBal]{sfcMassBal} & Surface mass balance \\
	\hline
\end{longtable}
\end{center}
}
