\chapter{MPAS-Land Ice Quick Start Guide}
\label{chap:quick_start}

This chapter provides MPAS-Land Ice users with a quick start description of how to
build and run the model. It is meant merely as a brief overview of the process,
while the more detailed descriptions of each step are provided in later
sections.

In general, the build process follows the following steps.

\begin{enumerate}
	\item Build MPI Layer (OpenMPI, MVAPICH2, etc.)
	\item Build serial NetCDF library (v3.6.3, v4.1.3, etc.)
	\item Build Parallel-NetCDF library (v1.2.1, v1.3.0, etc.)
	\item Build Parallel I/O library (v1.4.1, v1.6.1, etc.)
	\item (Optional) Build METIS library and executables (v4.0, v5.0.2, etc.)
	\item Checkout MPAS-Land Ice from repository
	\item Build Land Ice core
\end{enumerate}

After step 7, an executable should be created called landice\_model.exe. Once the executable is built, one can begin the run process as follows:

\begin{enumerate}
	\item Create run directory.
	\item Copy executable to run directory.
	\item Copy namelist.input into run directory.
	\item (Optional) Copy input and graph files into run directory.
	\item Edit namelist.input to have the proper parameters. \\
		  If step 4 was skipped, ensure paths to input and graph files are appropriately set.
	\item (Optional) Create graph files, using METIS executable (pmetis or gpmetis depending on version). \\
		  A graph file is required for each processor count you want to use.
	\item Run MPAS-Land Ice.
	\item Visualize output file, and perform analysis.
\end{enumerate}
