\chapter[Variable definitions]{\hyperref[chap:variable_sections]{Variable definitions}}
\label{chap:variable_tables}
Embedded links point to more detailed variable information in the appendix.
\section[state]{\hyperref[sec:var_sec_state]{state}}
\label{sec:var_tab_state}
\input{landice/section_descriptions/state.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hyperref[subsec:var_sec_state_xtime]{xtime} & model time, with format 'YYYY-MM-DD\_HH:MM:SS' \\
	\hline
	\hyperref[subsec:var_sec_state_thickness]{thickness} & ice thickness \\
	\hline
	\hyperref[subsec:var_sec_state_layerThickness]{layerThickness} & layer thickness \\
	\hline
	\hyperref[subsec:var_sec_state_temperature]{temperature} & ice temperature \\
	\hline
	\hyperref[subsec:var_sec_state_lowerSurface]{lowerSurface} & elevation at bottom of ice \\
	\hline
	\hyperref[subsec:var_sec_state_upperSurface]{upperSurface} & elevation at top of ice \\
	\hline
	\hyperref[subsec:var_sec_state_layerThicknessEdge]{layerThicknessEdge} & layer thickness on cell edges \\
	\hline
	\hyperref[subsec:var_sec_state_cellMask]{cellMask} & bitmask indicating various properties about the ice sheet on cells.  cellMask only needs to be a restart field if config\_allow\_additional\_advance = false (to keep the mask of initial ice extent) \\
	\hline
	\hyperref[subsec:var_sec_state_edgeMask]{edgeMask} & bitmask indicating various properties about the ice sheet on edges. \\
	\hline
	\hyperref[subsec:var_sec_state_vertexMask]{vertexMask} & bitmask indicating various properties about the ice sheet on vertices. \\
	\hline
	\hyperref[subsec:var_sec_state_normalVelocity]{normalVelocity} & horizonal velocity, normal component to an edge \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructX]{uReconstructX} & x-component of velocity reconstructed on cell centers \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructY]{uReconstructY} & y-component of velocity reconstructed on cell centers \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructZ]{uReconstructZ} & z-component of velocity reconstructed on cell centers \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructZonal]{uReconstructZonal} & zonal velocity reconstructed on cell centers \\
	\hline
	\hyperref[subsec:var_sec_state_uReconstructMeridional]{uReconstructMeridional} & meridional velocity reconstructed on cell centers \\
	\hline
\end{longtable}
\end{center}
}
\section[tend]{\hyperref[sec:var_sec_tend]{tend}}
\label{sec:var_tab_tend}
\input{landice/section_descriptions/tend.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hyperref[subsec:var_sec_tend_tend_layerThickness]{tend\_layerThickness} & time tendency of layer thickness \\
	\hline
	\hyperref[subsec:var_sec_tend_tend_temperature]{tend\_temperature} & time tendency of ice temperature \\
	\hline
\end{longtable}
\end{center}
}
\section[mesh]{\hyperref[sec:var_sec_mesh]{mesh}}
\label{sec:var_tab_mesh}
\input{landice/section_descriptions/mesh.tex}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
	\hline
	{\bf Name} & {\bf Description} \\
	\hline
	\hyperref[subsec:var_sec_mesh_latCell]{latCell} & Latitude location of cell centers in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_lonCell]{lonCell} & Longitude location of cell centers in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_xCell]{xCell} & X Coordinate in cartesian space of cell centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_yCell]{yCell} & Y Coordinate in cartesian space of cell centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_zCell]{zCell} & Z Coordinate in cartesian space of cell centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_indexToCellID]{indexToCellID} & List of global cell IDs. \\
	\hline
	\hyperref[subsec:var_sec_mesh_latEdge]{latEdge} & Latitude location of edge midpoints in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_lonEdge]{lonEdge} & Longitude location of edge midpoints in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_xEdge]{xEdge} & X Coordinate in cartesian space of edge midpoints. \\
	\hline
	\hyperref[subsec:var_sec_mesh_yEdge]{yEdge} & Y Coordinate in cartesian space of edge midpoints. \\
	\hline
	\hyperref[subsec:var_sec_mesh_zEdge]{zEdge} & Z Coordinate in cartesian space of edge midpoints. \\
	\hline
	\hyperref[subsec:var_sec_mesh_indexToEdgeID]{indexToEdgeID} & List of global edge IDs. \\
	\hline
	\hyperref[subsec:var_sec_mesh_latVertex]{latVertex} & Latitude location of vertices in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_lonVertex]{lonVertex} & Longitude location of vertices in radians. \\
	\hline
	\hyperref[subsec:var_sec_mesh_xVertex]{xVertex} & X Coordinate in cartesian space of vertices. \\
	\hline
	\hyperref[subsec:var_sec_mesh_yVertex]{yVertex} & Y Coordinate in cartesian space of vertices. \\
	\hline
	\hyperref[subsec:var_sec_mesh_zVertex]{zVertex} & Z Coordinate in cartesian space of vertices. \\
	\hline
	\hyperref[subsec:var_sec_mesh_indexToVertexID]{indexToVertexID} & List of global vertex IDs. \\
	\hline
	\hyperref[subsec:var_sec_mesh_cellsOnEdge]{cellsOnEdge} & List of cells that straddle each edge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_nEdgesOnCell]{nEdgesOnCell} & Number of edges that border each cell. \\
	\hline
	\hyperref[subsec:var_sec_mesh_nEdgesOnEdge]{nEdgesOnEdge} & Number of edges that surround each of the cells that straddle each edge. These edges are used to reconstruct the tangential velocities. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgesOnCell]{edgesOnCell} & List of edges that border each cell. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgesOnEdge]{edgesOnEdge} & List of edges that border each of the cells that straddle each edge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_weightsOnEdge]{weightsOnEdge} & Reconstruction weights associated with each of the edgesOnEdge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_dvEdge]{dvEdge} & Length of each edge, computed as the distance between verticesOnEdge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_dcEdge]{dcEdge} & Length of each edge, computed as the distance between cellsOnEdge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_angleEdge]{angleEdge} & Angle the edge normal makes with local eastward direction. \\
	\hline
	\hyperref[subsec:var_sec_mesh_areaCell]{areaCell} & Area of each cell in the primary grid. \\
	\hline
	\hyperref[subsec:var_sec_mesh_areaTriangle]{areaTriangle} & Area of each cell (triangle) in the dual grid. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgeNormalVectors]{edgeNormalVectors} & Normal vector defined at an edge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_localVerticalUnitVectors]{localVerticalUnitVectors} & Unit surface normal vectors defined at cell centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_cellTangentPlane]{cellTangentPlane} & The two vectors that define a tangent plane at a cell center. \\
	\hline
	\hyperref[subsec:var_sec_mesh_cellsOnCell]{cellsOnCell} & List of cells that neighbor each cell. \\
	\hline
	\hyperref[subsec:var_sec_mesh_verticesOnCell]{verticesOnCell} & List of vertices that border each cell. \\
	\hline
	\hyperref[subsec:var_sec_mesh_verticesOnEdge]{verticesOnEdge} & List of vertices that straddle each edge. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgesOnVertex]{edgesOnVertex} & List of edges that share a vertex as an endpoint. \\
	\hline
	\hyperref[subsec:var_sec_mesh_cellsOnVertex]{cellsOnVertex} & List of cells that share a vertex. \\
	\hline
	\hyperref[subsec:var_sec_mesh_kiteAreasOnVertex]{kiteAreasOnVertex} & Area of the portions of each dual cell that are part of each cellsOnVertex. \\
	\hline
	\hyperref[subsec:var_sec_mesh_coeffs_reconstruct]{coeffs\_reconstruct} & Coefficients to reconstruct velocity vectors at cells centers. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgeSignOnCell]{edgeSignOnCell} & Sign of edge contributions to a cell for each edge on cell. Used for bit-reproducible loops. Represents directionality of vector connecting cells. \\
	\hline
	\hyperref[subsec:var_sec_mesh_edgeSignOnVertex]{edgeSignOnVertex} & Sign of edge contributions to a vertex for each edge on vertex. Used for bit-reproducible loops. Represents directionality of vector connecting vertices. \\
	\hline
	\hyperref[subsec:var_sec_mesh_layerThicknessFractions]{layerThicknessFractions} & Fractional thickness of each sigma layer \\
	\hline
	\hyperref[subsec:var_sec_mesh_layerCenterSigma]{layerCenterSigma} & Sigma (fractional) level at center of each layer \\
	\hline
	\hyperref[subsec:var_sec_mesh_layerInterfaceSigma]{layerInterfaceSigma} & Sigma (fractional) level at interface between each layer (including top and bottom) \\
	\hline
	\hyperref[subsec:var_sec_mesh_bedTopography]{bedTopography} & Elevation of ice sheet bed.  Once isostasy is added to the model, this should become a state variable. \\
	\hline
	\hyperref[subsec:var_sec_mesh_sfcMassBal]{sfcMassBal} & Surface mass balance \\
	\hline
\end{longtable}
\end{center}
}
