\documentclass[11pt,titlepage,twoside]{article}

\textwidth=6.5in
\textheight=9.8in
\topmargin=0.2in
\headsep=0.0in
\headheight=0.0in
\oddsidemargin=-0.25in
\evensidemargin=-0.25in

\begin{document}

\today
\section{Trunk Testing Plan}

\subsection{Purpose}
To create a standard test to be executed every time the ocean core trunk is modified.\\

\subsection{Evaluation criteria}
\begin{enumerate}
\item {\bf Stability} Model should run from typical initialization for a long duration without crashing.
\item {\bf Accuracy} Statistics should be a bit-for-bit match to previous test, unless documented as a non-matching commit.
\item {\bf Convergence} Time-stepping schemes should converge with the expected order.
\item {\bf Realism} Namelist flags should be representative of standard settings.  Some runs must include topography and complex boundaries.
\item {\bf Simplicity} The above criteria should be met with as few tests as possible.
\item {\bf Automation} Full suite of tests should be setup, submitted, and evaluted with simple script commands.
\end{enumerate}

\subsection{Proposed Test Suite, high priority}
\begin{enumerate}
\item {\bf Global 120km, six months.} Full topography, z-level, 3rd order advection, jm eos, split explicit with dt=3000s.  Write stats daily, compare global avg KE to reference value.
\item {\bf Global 30km, 15 days.} Full topography, z-star, flux corrected transport advection, jm eos, split explicit with dt=800s(?).  Write stats daily, compare global avg KE to reference value.
\item {\bf Baroclinic Channel, 320s} Flat bottom, z-star, flux corrected transport advection, linear eos.  Convergence study of timestepping schemes: RK4, unsplit, split explicit with 1 subcycle, split explicit with 20 subcycles.  Timesteps of 5, 10, 20, 40, 80, 160 seconds compared to reference case of RK4 with dt=1s.  Measure convergence rates of KE, divergence, vorticity, temperature, compare to reference convergence rates.
\item {\bf EOS unit test} as a module that can be run with the normal executable, with pass/fail result.
\end{enumerate}

\subsection{Proposed Test Suite, lower priority}
\begin{enumerate}
\item {\bf Isopycnal test} 
\item {\bf Advection test} rotating disk
\item {\bf Baroclinic Channel, 320s} Flat bottom, z-star, flux corrected transport advection, linear eos.  Convergence study of timestepping schemes: RK4, unsplit, split explicit with 1 subcycle, split explicit with 20 subcycles.  Timesteps of 5, 10, 20, 40, 80, 160 seconds compared to reference case of RK4 with dt=1s.  Measure convergence rates of KE, divergence, vorticity, temperature, compare to reference convergence rates.
\item {\bf All other unit tests} vertical mixing, i/o, halo update, namelist read, etc
\end{enumerate}

\end{document}
