\chapter*{Copyright}
\label{chap:copyright}

{\bf Copyright \copyright 2013,  Los Alamos National Security, LLC (LANSL) and the University Corporation for Atmospheric Research (UCAR). All rights reserved.} \\

This software was produced under U.S. Government contract $xxx$. LANSL is the operator of the Los Alamos National Laboratory under Contract No. DE-AC52-06NA25396 with the U.S. Department of Energy.  UCAR manages the National Center for Atmospheric Research under Cooperative Agreement $xxx$ with the National Science Foundation.  The U.S. Government has rights to use, reproduce, and distribute this software.  NO WARRANTY, EXPRESS OR IMPLIED IS OFFERED BY LANSL, UCAR OR THE GOVERNMENT AND NONE OF THEM ASSUME ANY LIABILITY FOR THE USE OF THIS SOFTWARE.  If software is modified to produce derivative works, such modified software should be clearly marked, so as not to confuse it with the version available from LANSL and UCAR.\\

Additionally, redistribution and use in source and binary forms, with or without modification, are permitted provided that the following conditions are met:\\

Redistributions of source code must retain the above copyright notice, this list of conditions and the following disclaimer.\\

Redistributions in binary form must reproduce the above copyright notice, this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.\\

None of the names of LANSL, UCAR or the names of its contributors, if any, may be used to endorse or promote products derived from this software without specific prior written permission.\\

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.

\newpage
