\chapter{Dimensions}
\label{chap:dimensions}
{\small
\begin{center}
\begin{longtable}{| p{1.0in} || p{1.0in} | p{4.0in} |}
    \hline 
    {\bf Name} & {\bf Units} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Units} & {\bf Description} (Continued) \endhead
    \hline 
    \hline 
    nCells & \si{unitless} & The number of polygons in the primary grid. \\ 
    \hline
    nCellsP1 & \si{unitless} & The number of polygons in the primary grid. \\ 
    \hline
    nEdges & \si{unitless} & The number of edge midpoints in either the primary or dual grid. \\ 
    \hline
    nEdgesP1 & \si{unitless} & The number of edge midpoints in either the primary or dual grid. \\ 
    \hline
    maxEdges & \si{unitless} & The largest number of edges any polygon within the grid has. \\ 
    \hline
    maxEdges2 & \si{unitless} & Two times the largest number of edges any polygon within the grid has. \\ 
    \hline
    nAdvectionCells & \si{unitless} & The largest number of advection cells for any edge. \\ 
    \hline
    nVertices & \si{unitless} & The total number of cells in the dual grid. Also the number of corners in the primary grid. \\ 
    \hline
    nVerticesP1 & \si{unitless} & The total number of cells in the dual grid. Also the number of corners in the primary grid. \\ 
    \hline
    TWO & \si{unitless} & The number two as a dimension. \\ 
    \hline
    R3 & \si{unitless} & The number three as a dimension. \\ 
    \hline
    FOUR & \si{unitless} & The number four as a dimension. \\ 
    \hline
    SIX & \si{unitless} & The number six as a dimension. \\ 
    \hline
    FIFTEEN & \si{unitless} & The number 15 as a dimension. \\ 
    \hline
    TWENTYONE & \si{unitless} & The number 21 as a dimension. \\ 
    \hline
    vertexDegree & \si{unitless} & The number of cells or edges touching each vertex. \\ 
    \hline
    nVertLevels & \si{unitless} & The number of levels in the vertical direction. All vertical levels share the same horizontal locations. \\ 
    \hline
    nVertLevelsP1 & \si{unitless} & The number of interfaces in the vertical direction. \\ 
    \hline
    nPoints & \si{unitless} & The number of points for AM\_pointwiseStats \\ 
    \hline
    nPointGroups & \si{unitless} & The number of points groups \\ 
    \hline
    maxPointsInGroup & \si{unitless} & The maximum number of points in any group. \\ 
    \hline
    nRegions & \si{unitless} & Number of regions. \\ 
    \hline
    nRegionGroups & \si{unitless} & Number of groups of regions. \\ 
    \hline
    maxRegionsInGroup & \si{unitless} & Maximum number of regions in a group. \\ 
    \hline
    nTransects & \si{unitless} & The number of transects for AM transectTransport \\ 
    \hline
    nTransectGroups & \si{unitless} & Number of groups of regions. \\ 
    \hline
    maxTransectsInGroup & \si{unitless} & Maximum number of regions in a group. \\ 
    \hline
    maxEdgesInTransect & \si{unitless} & Max number of edges in a transect for AM transectTransport \\ 
    \hline
    nForcingGroupsMax & {\bf \color{red} MISSING} & Number of forcing groups \\ 
    \hline
    nDepthTracerIC & \si{unitless} & The number of levels in the vertical direction for tracer initial conditions \\ 
    \hline
    nDepthEcosysIC & \si{unitless} & The number of levels in the vertical direction for ecosystem tracer initial conditions \\ 
    \hline
    nSfcAreaWeightedAvgFields & \si{unitless} & A number equal to or greater than the number of var arrays in the surfaceAreaWeightedAveragesAM var structure below. \\ 
    \hline
    nOceanRegions & \si{unitless} & The number of regions defined within the global ocean (will eventually be moved up and used uniformly across MPAS-O. \\ 
    \hline
    nTemperatureBins & \si{unitless} & The number of temperature bins to be used to span from minTemperature to maxTemperature \\ 
    \hline
    nSalinityBins & \si{unitless} & The number of salinity bins to be used to span from minSalinity to maxSalinity \\ 
    \hline
    nTemperatureBinsP1 & \si{unitless} & The number of temperature bin edge values to be used to span from minTemperature to maxTemperature \\ 
    \hline
    nSalinityBinsP1 & \si{unitless} & The number of salinity bins edge values to be used to span from minSalinity to maxSalinity \\ 
    \hline
    nOceanRegionsTmpCensus & \si{unitless} & The number of regions defined within the global ocean (will eventually be moved up and used uniformly across MPAS-O. \\ 
    \hline
    nLayerVolWeightedAvgFields & \si{unitless} & A number equal to or greater than the number of var arrays in the layerVolumeWeightedAverageAM var structure below. \\ 
    \hline
    nOceanRegionsTmp & \si{unitless} & The number of regions defined within the global ocean (will eventually be moved up and used uniformly across MPAS-O. \\ 
    \hline
    nZonalMeanBins & \si{unitless} & Number of bins for zonal mean. \\ 
    \hline
    nZonalMeanBinsP1 & \si{unitless} & Number of bins for zonal mean, plus one. \\ 
    \hline
    nMerHeatTransBins & \si{unitless} & Maximum number of bins for meridional heat transport. \\ 
    \hline
    nMerHeatTransBinsP1 & \si{unitless} & Maximum number of bins for meridional heat transport, plus one. \\ 
    \hline
    nParticles & \si{unitless} & The total number of particles in the simlulation. \\ 
    \hline
    nBuoyancySurfaces & \si{unitless} & The total number of buoyancy surfaces on which to interpolate velocity. \\ 
    \hline
    nBuoyancyLayers & {\bf \color{red} MISSING} & The number of buoyancy layers used for buoyancy coordinates. \\ 
    \hline
    nBuoyancyLayersP1 & {\bf \color{red} MISSING} & The number of interfaces between buoyancy layers used for buoyancy coordinates. \\ 
    \hline
    nMocStreamfunctionBins & \si{unitless} & Maximum number of bins in South-to-North direction for moc streamfunction. \\ 
    \hline
    nMocStreamfunctionBinsP1 & \si{unitless} & Maximum number of Lat bins for moc streamfunction, plus one. \\ 
    \hline
\end{longtable}
\end{center}
}
