\chapter[Variable definitions]{\hyperref[chap:variable_sections]{Variable definitions}}
\label{chap:variable_tables}
Embedded links point to more detailed variable information in the appendix.
\section[state]{\hyperref[sec:var_sec_state]{state}}
\label{sec:var_tab_state}
\input{ocean/section_descriptions/state_struct.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_state_normalVelocity]{normalVelocity} & horizontal velocity, normal component to an edge \\
    \hline
    \hyperref[subsec:var_sec_state_layerThickness]{layerThickness} & layer thickness \\
    \hline
    \hyperref[subsec:var_sec_state_ssh]{ssh} & sea surface height \\
    \hline
    \hyperref[subsec:var_sec_state_highFreqThickness]{highFreqThickness} & high frequency-filtered layer thickness \\
    \hline
    \hyperref[subsec:var_sec_state_lowFreqDivergence]{lowFreqDivergence} & low frequency-filtered divergence \\
    \hline
    \hyperref[subsec:var_sec_state_accumulatedFrazilIceMass]{accumulatedFrazilIceMass} & Mass per unit area of frazil ice produced. Reset to zero at each coupling interval \\
    \hline
    \hyperref[subsec:var_sec_state_accumulatedFrazilIceSalinity]{accumulatedFrazilIceSalinity} & Salinity associated with accumulatedFrazilIceMass. Reset to zero at each coupling interval \\
    \hline
    \hyperref[subsec:var_sec_state_accumulatedLandIceFrazilSalinity]{accumulatedLandIceFrazil\-Salinity} & Salinity associated with accumulatedFrazilIceMass. Reset to zero at each coupling interval \\
    \hline
    \hyperref[subsec:var_sec_state_accumulatedLandIceMass]{accumulatedLandIceMass} & Mass per unit area of land ice produced at land ice-ocean interface. Only computed in 'standalone' mode where land-ice fluxes are computed in MPAS-O. \\
    \hline
    \hyperref[subsec:var_sec_state_accumulatedLandIceHeat]{accumulatedLandIceHeat} & Heat per unit area stored in land ice produced at land ice-ocean interface. Only computed in 'standalone' mode where land-ice fluxes are computed in MPAS-O. \\
    \hline
    \hyperref[subsec:var_sec_state_accumulatedLandIceFrazilMass]{accumulatedLandIceFrazilMass} & Mass per unit area of frazil ice produced under land ice.  Only computed when not coupled to a dynamic land-ice model. \\
    \hline
    \hyperref[subsec:var_sec_state_normalBarotropicVelocity]{normalBarotropicVelocity} & barotropic velocity, used in split-explicit time-stepping \\
    \hline
    \hyperref[subsec:var_sec_state_normalBarotropicVelocitySubcycle]{normalBarotropicVelocity\-Subcycle} & barotropic velocity, used in subcycling in stage 2 of split-explicit time-stepping \\
    \hline
    \hyperref[subsec:var_sec_state_sshSubcycle]{sshSubcycle} & sea surface height, used in subcycling in stage 2 of split-explicit time-stepping \\
    \hline
    \hyperref[subsec:var_sec_state_normalBaroclinicVelocity]{normalBaroclinicVelocity} & baroclinic velocity, used in split-explicit time-stepping \\
    \hline
    \hyperref[subsec:var_sec_state_effectiveDensityInLandIce]{effectiveDensityInLandIce} & The effective ocean density within ice shelves based on Archimedes' principle. \\
    \hline
    \hyperref[subsec:var_sec_state_gotmVertViscTopOfCell]{gotmVertViscTopOfCell} & GOTM: vertical viscosity defined at the cell center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_state_gotmVertDiffTopOfCell]{gotmVertDiffTopOfCell} & GOTM: vertical diffusion defined at the cell center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_state_gotmTKETopOfCell]{gotmTKETopOfCell} & GOTM: turbulent kenetic energy defined at the cell center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_state_gotmKbTopOfCell]{gotmKbTopOfCell} & GOTM: (half) buoyancy variance defined at the cell center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_state_gotmEpsbTopOfCell]{gotmEpsbTopOfCell} & GOTM: destruction of buoyancy variance defined at the cell center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_state_gotmDissTopOfCell]{gotmDissTopOfCell} & GOTM: rate of dissipation defined at the cell center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_state_gotmLengthTopOfCell]{gotmLengthTopOfCell} & GOTM: turbulent length scale defined at the cell center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_state_layerThicknessLag]{layerThicknessLag} & The layerThickness after the Lagrangian step, prior to remapping. \\
    \hline
    \hyperref[subsec:var_sec_state_temperature]{temperature} & potential temperature \\
    \hline
    \hyperref[subsec:var_sec_state_salinity]{salinity} & salinity in grams salt per kilogram seawater \\
    \hline
    \hyperref[subsec:var_sec_state_tracer1]{tracer1} & tracer for debugging purposes \\
    \hline
    \hyperref[subsec:var_sec_state_tracer2]{tracer2} & tracer for debugging purposes \\
    \hline
    \hyperref[subsec:var_sec_state_tracer3]{tracer3} & tracer for debugging purposes \\
    \hline
    \hyperref[subsec:var_sec_state_PO4]{PO4} & Dissolved Inorganic Phosphate \\
    \hline
    \hyperref[subsec:var_sec_state_NO3]{NO3} & Dissolved Inorganic Nitrate \\
    \hline
    \hyperref[subsec:var_sec_state_SiO3]{SiO3} & Dissolved Inorganic Silicate \\
    \hline
    \hyperref[subsec:var_sec_state_NH4]{NH4} & Dissolved Ammonia \\
    \hline
    \hyperref[subsec:var_sec_state_Fe]{Fe} & Dissolved Inorganic Iron \\
    \hline
    \hyperref[subsec:var_sec_state_Lig]{Lig} & Iron Binding Ligand \\
    \hline
    \hyperref[subsec:var_sec_state_O2]{O2} & Dissolved Oxygen \\
    \hline
    \hyperref[subsec:var_sec_state_DIC]{DIC} & Dissolved Inorganic Carbon \\
    \hline
    \hyperref[subsec:var_sec_state_DIC_ALT_CO2]{DIC\_ALT\_CO2} & Dissolved Inorganic Carbon, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_state_ALK]{ALK} & Alkalinity \\
    \hline
    \hyperref[subsec:var_sec_state_ALK_ALT_CO2]{ALK\_ALT\_CO2} & Alkalinity Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_state_DOC]{DOC} & Dissolved Organic Carbon \\
    \hline
    \hyperref[subsec:var_sec_state_DON]{DON} & Dissolved Organic Nitrogen \\
    \hline
    \hyperref[subsec:var_sec_state_DOP]{DOP} & Dissolved Organic Phosphorus \\
    \hline
    \hyperref[subsec:var_sec_state_DOPr]{DOPr} & Refractory DOP \\
    \hline
    \hyperref[subsec:var_sec_state_DONr]{DONr} & Refractory DON \\
    \hline
    \hyperref[subsec:var_sec_state_DOCr]{DOCr} & Refractory DOC \\
    \hline
    \hyperref[subsec:var_sec_state_zooC]{zooC} & Zooplankton Carbon \\
    \hline
    \hyperref[subsec:var_sec_state_spChl]{spChl} & Small Phytoplankton Chlorophyll \\
    \hline
    \hyperref[subsec:var_sec_state_spC]{spC} & Small Phytoplankton Carbon \\
    \hline
    \hyperref[subsec:var_sec_state_spFe]{spFe} & Small Phytoplankton Iron \\
    \hline
    \hyperref[subsec:var_sec_state_spP]{spP} & Small Phytoplankton Phosphorus \\
    \hline
    \hyperref[subsec:var_sec_state_spCaCO3]{spCaCO3} & Small Phytoplankton Calcium Carbonate \\
    \hline
    \hyperref[subsec:var_sec_state_diatChl]{diatChl} & Diatom Chlorophyll \\
    \hline
    \hyperref[subsec:var_sec_state_diatC]{diatC} & Diatom Carbon \\
    \hline
    \hyperref[subsec:var_sec_state_diatFe]{diatFe} & Diatom Iron \\
    \hline
    \hyperref[subsec:var_sec_state_diatP]{diatP} & Diatom Phosphorus \\
    \hline
    \hyperref[subsec:var_sec_state_diatSi]{diatSi} & Diatom Silicate \\
    \hline
    \hyperref[subsec:var_sec_state_diazChl]{diazChl} & Diazotroph Chlorophyll \\
    \hline
    \hyperref[subsec:var_sec_state_diazC]{diazC} & Diazotroph Carbon \\
    \hline
    \hyperref[subsec:var_sec_state_diazFe]{diazFe} & Diazotroph Iron \\
    \hline
    \hyperref[subsec:var_sec_state_diazP]{diazP} & Diazotroph Phosphorus \\
    \hline
    \hyperref[subsec:var_sec_state_DMS]{DMS} & Dimethyl Sulfide \\
    \hline
    \hyperref[subsec:var_sec_state_DMSP]{DMSP} & Dimethyl Sulfoniopropionate \\
    \hline
    \hyperref[subsec:var_sec_state_PROT]{PROT} & Proteins \\
    \hline
    \hyperref[subsec:var_sec_state_POLY]{POLY} & Polysaccharides \\
    \hline
    \hyperref[subsec:var_sec_state_LIP]{LIP} & Lipids \\
    \hline
    \hyperref[subsec:var_sec_state_iAge]{iAge} & tracer for ideal age \\
    \hline
    \hyperref[subsec:var_sec_state_CFC11]{CFC11} & CFC11 \\
    \hline
    \hyperref[subsec:var_sec_state_CFC12]{CFC12} & CFC12 \\
    \hline
\end{longtable}
\end{center}
}
\section[mesh]{\hyperref[sec:var_sec_mesh]{mesh}}
\label{sec:var_tab_mesh}
\input{ocean/section_descriptions/mesh_struct.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_mesh_latCell]{latCell} & Latitude location of cell centers in radians. \\
    \hline
    \hyperref[subsec:var_sec_mesh_lonCell]{lonCell} & Longitude location of cell centers in radians. \\
    \hline
    \hyperref[subsec:var_sec_mesh_xCell]{xCell} & X Coordinate in cartesian space of cell centers. \\
    \hline
    \hyperref[subsec:var_sec_mesh_yCell]{yCell} & Y Coordinate in cartesian space of cell centers. \\
    \hline
    \hyperref[subsec:var_sec_mesh_zCell]{zCell} & Z Coordinate in cartesian space of cell centers. \\
    \hline
    \hyperref[subsec:var_sec_mesh_indexToCellID]{indexToCellID} & List of global cell IDs. \\
    \hline
    \hyperref[subsec:var_sec_mesh_latEdge]{latEdge} & Latitude location of edge midpoints in radians. \\
    \hline
    \hyperref[subsec:var_sec_mesh_lonEdge]{lonEdge} & Longitude location of edge midpoints in radians. \\
    \hline
    \hyperref[subsec:var_sec_mesh_xEdge]{xEdge} & X Coordinate in cartesian space of edge midpoints. \\
    \hline
    \hyperref[subsec:var_sec_mesh_yEdge]{yEdge} & Y Coordinate in cartesian space of edge midpoints. \\
    \hline
    \hyperref[subsec:var_sec_mesh_zEdge]{zEdge} & Z Coordinate in cartesian space of edge midpoints. \\
    \hline
    \hyperref[subsec:var_sec_mesh_indexToEdgeID]{indexToEdgeID} & List of global edge IDs. \\
    \hline
    \hyperref[subsec:var_sec_mesh_latVertex]{latVertex} & Latitude location of vertices in radians. \\
    \hline
    \hyperref[subsec:var_sec_mesh_lonVertex]{lonVertex} & Longitude location of vertices in radians. \\
    \hline
    \hyperref[subsec:var_sec_mesh_xVertex]{xVertex} & X Coordinate in cartesian space of vertices. \\
    \hline
    \hyperref[subsec:var_sec_mesh_yVertex]{yVertex} & Y Coordinate in cartesian space of vertices. \\
    \hline
    \hyperref[subsec:var_sec_mesh_zVertex]{zVertex} & Z Coordinate in cartesian space of vertices. \\
    \hline
    \hyperref[subsec:var_sec_mesh_indexToVertexID]{indexToVertexID} & List of global vertex IDs. \\
    \hline
    \hyperref[subsec:var_sec_mesh_meshDensity]{meshDensity} & Value of density function used to generate a particular mesh at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_mesh_meshScalingDel2]{meshScalingDel2} & Coefficient to Laplacian mixing terms in momentum and tracer equations, so that viscosity and diffusion scale with mesh. \\
    \hline
    \hyperref[subsec:var_sec_mesh_meshScalingDel4]{meshScalingDel4} & Coefficient to biharmonic mixing terms in momentum and tracer equations, so that biharmonic viscosity and diffusion coefficients scale with mesh. \\
    \hline
    \hyperref[subsec:var_sec_mesh_cellsOnEdge]{cellsOnEdge} & List of cells that straddle each edge. \\
    \hline
    \hyperref[subsec:var_sec_mesh_nEdgesOnCell]{nEdgesOnCell} & Number of edges that border each cell. \\
    \hline
    \hyperref[subsec:var_sec_mesh_nEdgesOnEdge]{nEdgesOnEdge} & Number of edges that surround each of the cells that straddle each edge. These edges are used to reconstruct the tangential velocities. \\
    \hline
    \hyperref[subsec:var_sec_mesh_edgesOnCell]{edgesOnCell} & List of edges that border each cell. \\
    \hline
    \hyperref[subsec:var_sec_mesh_edgesOnEdge]{edgesOnEdge} & List of edges that border each of the cells that straddle each edge. \\
    \hline
    \hyperref[subsec:var_sec_mesh_weightsOnEdge]{weightsOnEdge} & Reconstruction weights associated with each of the edgesOnEdge, used to reconstruct the tangentialVelocity from normalVelocities on neighboring edges. \\
    \hline
    \hyperref[subsec:var_sec_mesh_dvEdge]{dvEdge} & Length of each edge, computed as the distance between verticesOnEdge. \\
    \hline
    \hyperref[subsec:var_sec_mesh_dcEdge]{dcEdge} & Length of each edge, computed as the distance between cellsOnEdge. \\
    \hline
    \hyperref[subsec:var_sec_mesh_angleEdge]{angleEdge} & Angle the edge normal makes with local eastward direction. \\
    \hline
    \hyperref[subsec:var_sec_mesh_areaCell]{areaCell} & Area of each cell in the primary grid. \\
    \hline
    \hyperref[subsec:var_sec_mesh_areaTriangle]{areaTriangle} & Area of each cell (triangle) in the dual grid. \\
    \hline
    \hyperref[subsec:var_sec_mesh_edgeNormalVectors]{edgeNormalVectors} & Normal unit vector defined at an edge. \\
    \hline
    \hyperref[subsec:var_sec_mesh_edgeTangentVectors]{edgeTangentVectors} & Tangent unit vector defined at an edge. \\
    \hline
    \hyperref[subsec:var_sec_mesh_localVerticalUnitVectors]{localVerticalUnitVectors} & Unit surface normal vectors defined at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_mesh_cellTangentPlane]{cellTangentPlane} & The two vectors that define a tangent plane at a cell center. \\
    \hline
    \hyperref[subsec:var_sec_mesh_cellsOnCell]{cellsOnCell} & List of cells that neighbor each cell. \\
    \hline
    \hyperref[subsec:var_sec_mesh_verticesOnCell]{verticesOnCell} & List of vertices that border each cell. \\
    \hline
    \hyperref[subsec:var_sec_mesh_verticesOnEdge]{verticesOnEdge} & List of vertices that straddle each edge. \\
    \hline
    \hyperref[subsec:var_sec_mesh_edgesOnVertex]{edgesOnVertex} & List of edges that share a vertex as an endpoint. \\
    \hline
    \hyperref[subsec:var_sec_mesh_cellsOnVertex]{cellsOnVertex} & List of cells that share a vertex. \\
    \hline
    \hyperref[subsec:var_sec_mesh_kiteAreasOnVertex]{kiteAreasOnVertex} & Area of the portions of each dual cell that are part of each cellsOnVertex. \\
    \hline
    \hyperref[subsec:var_sec_mesh_fEdge]{fEdge} & Coriolis parameter at edges. \\
    \hline
    \hyperref[subsec:var_sec_mesh_fVertex]{fVertex} & Coriolis parameter at vertices. \\
    \hline
    \hyperref[subsec:var_sec_mesh_fCell]{fCell} & Coriolis parameter at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_mesh_bed_elevation]{bed\_elevation} & Depth of the bottom of the ocean. Given as negative distance from sea level. Used as input to replace topography input file. \\
    \hline
    \hyperref[subsec:var_sec_mesh_bottomDepth]{bottomDepth} & Depth of the bottom of the ocean. Given as a positive distance from sea level. \\
    \hline
    \hyperref[subsec:var_sec_mesh_bottomDepthObserved]{bottomDepthObserved} & Depth of the bottom of the ocean, before any alterations for modeling purposes. Given as a positive distance from sea level. \\
    \hline
    \hyperref[subsec:var_sec_mesh_oceanFracObserved]{oceanFracObserved} & fraction of each cell containing ocean, used to determine which cells are culled as land. \\
    \hline
    \hyperref[subsec:var_sec_mesh_coeffs_reconstruct]{coeffs\_reconstruct} & Coefficients to reconstruct velocity vectors at cells centers. \\
    \hline
    \hyperref[subsec:var_sec_mesh_minLevelCell]{minLevelCell} & Index to the first active ocean cell in each column. \\
    \hline
    \hyperref[subsec:var_sec_mesh_maxLevelCell]{maxLevelCell} & Index to the last active ocean cell in each column. \\
    \hline
    \hyperref[subsec:var_sec_mesh_minLevelEdgeTop]{minLevelEdgeTop} & Index to the first edge in a column with at least one active ocean cell on either side of it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_maxLevelEdgeTop]{maxLevelEdgeTop} & Index to the last edge in a column with active ocean cells on both sides of it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_minLevelEdgeBot]{minLevelEdgeBot} & Index to the first edge in a column with active ocean cells on both sides of it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_maxLevelEdgeBot]{maxLevelEdgeBot} & Index to the last edge in a column with at least one active ocean cell on either side of it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_minLevelVertexTop]{minLevelVertexTop} & Index to the first vertex in a column with at least one active ocean cell around it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_maxLevelVertexTop]{maxLevelVertexTop} & Index to the last vertex in a column with all active cells around it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_minLevelVertexBot]{minLevelVertexBot} & Index to the first vertex in a column with all active cells around it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_maxLevelVertexBot]{maxLevelVertexBot} & Index to the last vertex in a column with at least one active ocean cell around it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_refBottomDepth]{refBottomDepth} & Reference depth of ocean for each vertical level. Used in 'z-level' type runs. \\
    \hline
    \hyperref[subsec:var_sec_mesh_refBottomDepthTopOfCell]{refBottomDepthTopOfCell} & Reference depth of ocean for each vertical interface. Used in 'z-level' type runs. \\
    \hline
    \hyperref[subsec:var_sec_mesh_vertCoordMovementWeights]{vertCoordMovementWeights} & Weights used for distribution of sea surface height perturbations through multiple vertical levels. \\
    \hline
    \hyperref[subsec:var_sec_mesh_boundaryEdge]{boundaryEdge} & Mask for determining boundary edges. A boundary edge has only one active ocean cell neighboring it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_boundaryVertex]{boundaryVertex} & Mask for determining boundary vertices. A boundary vertex has at least one inactive cell neighboring it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_boundaryCell]{boundaryCell} & Mask for determining boundary cells. A boundary cell has at least one inactive cell neighboring it. \\
    \hline
    \hyperref[subsec:var_sec_mesh_edgeMask]{edgeMask} & Mask on edges that determines if computations should be done on edges. \\
    \hline
    \hyperref[subsec:var_sec_mesh_vertexMask]{vertexMask} & Mask on vertices that determines if computations should be done on vertices. \\
    \hline
    \hyperref[subsec:var_sec_mesh_cellMask]{cellMask} & Mask on cells that determines if computations should be done on cells. \\
    \hline
    \hyperref[subsec:var_sec_mesh_edgeSignOnCell]{edgeSignOnCell} & Sign of edge contributions to a cell for each edge on cell. Used for bit-reproducible loops. Represents directionality of vector connecting cells. \\
    \hline
    \hyperref[subsec:var_sec_mesh_edgeSignOnVertex]{edgeSignOnVertex} & Sign of edge contributions to a vertex for each edge on vertex. Used for bit-reproducible loops. Represents directionality of vector connecting vertices. \\
    \hline
    \hyperref[subsec:var_sec_mesh_kiteIndexOnCell]{kiteIndexOnCell} & Index of kite in dual grid, based on verticesOnCell. \\
    \hline
    \hyperref[subsec:var_sec_mesh_cullCell]{cullCell} & Array to hold integers that represent logicals determining if a cell should be culled or not by the MpasCellCuller tool. \\
    \hline
    \hyperref[subsec:var_sec_mesh_distanceToCoast]{distanceToCoast} & Distance of each cell to nearest coastline cell. \\
    \hline
\end{longtable}
\end{center}
}
\section[verticalMesh]{\hyperref[sec:var_sec_verticalMesh]{verticalMesh}}
\label{sec:var_tab_verticalMesh}
\input{ocean/section_descriptions/verticalMesh_struct.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_verticalMesh_restingThickness]{restingThickness} & Layer thickness when the ocean is at rest, i.e. without SSH or internal perturbations. \\
    \hline
    \hyperref[subsec:var_sec_verticalMesh_refZMid]{refZMid} & Reference mid z-coordinate of ocean for each vertical level. This has a negative value. \\
    \hline
    \hyperref[subsec:var_sec_verticalMesh_refLayerThickness]{refLayerThickness} & Reference layerThickness of ocean for each vertical level. \\
    \hline
\end{longtable}
\end{center}
}
\section[tend]{\hyperref[sec:var_sec_tend]{tend}}
\label{sec:var_tab_tend}
\input{ocean/section_descriptions/tend_struct.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_tend_tendNormalVelocity]{tendNormalVelocity} & time tendency of normal component of velocity \\
    \hline
    \hyperref[subsec:var_sec_tend_tendLayerThickness]{tendLayerThickness} & time tendency of layer thickness \\
    \hline
    \hyperref[subsec:var_sec_tend_tendSSH]{tendSSH} & time tendency of sea-surface height \\
    \hline
    \hyperref[subsec:var_sec_tend_tendHighFreqThickness]{tendHighFreqThickness} & time tendency of high frequency-filtered layer thickness \\
    \hline
    \hyperref[subsec:var_sec_tend_tendLowFreqDivergence]{tendLowFreqDivergence} & time tendency of low frequency-filtered divergence \\
    \hline
    \hyperref[subsec:var_sec_tend_temperatureTend]{temperatureTend} & time tendency of potential temperature measured as change in degrees times layerThickness per second \\
    \hline
    \hyperref[subsec:var_sec_tend_salinityTend]{salinityTend} & time tendency of salinity measured as change in practical salinity units times layerThickness per second \\
    \hline
    \hyperref[subsec:var_sec_tend_tracer1Tend]{tracer1Tend} & Tendency for tracer1 \\
    \hline
    \hyperref[subsec:var_sec_tend_tracer2Tend]{tracer2Tend} & Tendency for tracer2 \\
    \hline
    \hyperref[subsec:var_sec_tend_tracer3Tend]{tracer3Tend} & Tendency for tracer3 \\
    \hline
    \hyperref[subsec:var_sec_tend_PO4Tend]{PO4Tend} & Dissolved Inorganic Phosphate Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_NO3Tend]{NO3Tend} & Dissolved Inorganic Nitrate Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_SiO3Tend]{SiO3Tend} & Dissolved Inorganic Silicate Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_NH4Tend]{NH4Tend} & Dissolved Ammonia Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_FeTend]{FeTend} & Dissolved Inorganic Iron Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_LigTend]{LigTend} & Ligand Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_O2Tend]{O2Tend} & Dissolved Oxygen Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DICTend]{DICTend} & Dissolved Inorganic Carbon Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DIC_ALT_CO2Tend]{DIC\_ALT\_CO2Tend} & Dissolved Inorganic Carbon, Alternative CO2 Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_ALKTend]{ALKTend} & Alkalinity Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_ALK_ALT_CO2Tend]{ALK\_ALT\_CO2Tend} & Alkalinity Tendency, Alternative CO2 Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DOCTend]{DOCTend} & Dissolved Organic Carbon Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DONTend]{DONTend} & Dissolved Organic Nitrogen Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DOPTend]{DOPTend} & Dissolved Organic Phosphorus Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DOPrTend]{DOPrTend} & Refractory DOP Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DONrTend]{DONrTend} & Refractory DON Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DOCrTend]{DOCrTend} & Refractory DOC Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_zooCTend]{zooCTend} & Zooplankton Carbon Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_spChlTend]{spChlTend} & Small Phytoplankton Chlorophyll Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_spCTend]{spCTend} & Small Phytoplankton Carbon Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_spFeTend]{spFeTend} & Small Phytoplankton Iron Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_spPTend]{spPTend} & Small Phytoplankton Phosphorus Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_spCaCO3Tend]{spCaCO3Tend} & Small Phytoplankton Calcium Carbonate Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_diatChlTend]{diatChlTend} & Diatom Chlorophyll Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_diatCTend]{diatCTend} & Diatom Carbon Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_diatFeTend]{diatFeTend} & Diatom Iron Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_diatPTend]{diatPTend} & Diatom Phosphorus Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_diatSiTend]{diatSiTend} & Diatom Silicate Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_diazChlTend]{diazChlTend} & Diazotroph Chlorophyll Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_diazCTend]{diazCTend} & Diazotroph Carbon Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_diazFeTend]{diazFeTend} & Diazotroph Iron Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_diazPTend]{diazPTend} & Diazotroph Phosphorus Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DMSTend]{DMSTend} & Dimethyl Sulfide Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_DMSPTend]{DMSPTend} & Dimethyl Sulfoniopropionate Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_PROTTend]{PROTTend} & Proteins Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_POLYTend]{POLYTend} & Polysaccharides Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_LIPTend]{LIPTend} & Lipids Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_iAgeTend]{iAgeTend} & Tendency for iAge \\
    \hline
    \hyperref[subsec:var_sec_tend_CFC11Tend]{CFC11Tend} & CFC11 Tendency \\
    \hline
    \hyperref[subsec:var_sec_tend_CFC12Tend]{CFC12Tend} & CFC12 Tendency \\
    \hline
\end{longtable}
\end{center}
}
\section[diagnostics]{\hyperref[sec:var_sec_diagnostics]{diagnostics}}
\label{sec:var_tab_diagnostics}
\input{ocean/section_descriptions/diagnostics_struct.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_diagnostics_xtime]{xtime} & model time, with format 'YYYY-MM-DD\_HH:MM:SS' \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_Time]{Time} & time \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_Time_bnds]{Time\_bnds} & time bounds \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_simulationStartTime]{simulationStartTime} & start time of first simulation, with format 'YYYY-MM-DD\_HH:MM:SS' \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_daysSinceStartOfSim]{daysSinceStartOfSim} & Time since simulationStartTime, for plotting \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinitySurfaceRestoringTendency]{salinitySurfaceRestoringTendency} & salinity tendency due to surface restoring \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureSurfaceFluxTendency]{temperatureSurfaceFluxTendency} & potential temperature tendency due to surface fluxes \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinitySurfaceFluxTendency]{salinitySurfaceFluxTendency} & salinity tendency due to surface fluxes \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureShortWaveTendency]{temperatureShortWaveTendency} & potential temperature tendency due to penetrating shortwave \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureHorMixTendency]{temperatureHorMixTendency} & potential temperature tendency due to horizontal mixing (including Redi) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinityHorMixTendency]{salinityHorMixTendency} & salinity tendency due to horizontal mixing (including Redi) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureNonLocalTendency]{temperatureNonLocalTendency} & potential temperature tendency due to kpp non-local flux \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinityNonLocalTendency]{salinityNonLocalTendency} & salinity tendency due to kpp non-local flux \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureVerticalAdvectionTopFlux]{temperatureVerticalAdvection\-TopFlux} & potential temperature vertical advective flux through top of cell \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinityVerticalAdvectionTopFlux]{salinityVerticalAdvectionTop\-Flux} & salinity advective vertical advective flux through top of cell \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureHorizontalAdvectionEdgeFlux]{temperatureHorizontalAdvection\-EdgeFlux} & potential temperature advective flux due to horizontal advection through edges \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinityHorizontalAdvectionEdgeFlux]{salinityHorizontalAdvectionEdge\-Flux} & salinity advective flux due to horizontal advection through edges \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureHorizontalAdvectionTendency]{temperatureHorizontalAdvection\-Tendency} & potential temperature tendency due to horizontal advection \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinityHorizontalAdvectionTendency]{salinityHorizontalAdvection\-Tendency} & salinity tendency due to horizontal advection \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureVerticalAdvectionTendency]{temperatureVerticalAdvection\-Tendency} & potential temperature tendency due to vertical advection \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinityVerticalAdvectionTendency]{salinityVerticalAdvection\-Tendency} & salinity tendency due to vertical advection \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureVertMixTendency]{temperatureVertMixTendency} & potential temperature tendency due to vertical mixing \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinityVertMixTendency]{salinityVertMixTendency} & salinity tendency due to vertical mixing \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureSurfaceValue]{temperatureSurfaceValue} & potential temperature extrapolated to ocean surface \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinitySurfaceValue]{salinitySurfaceValue} & salinity extrapolated to ocean surface \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_temperatureSurfaceLayerValue]{temperatureSurfaceLayerValue} & potential temperature averaged over ocean surface layer (generally 0.1 of the ocean boundary layer) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_salinitySurfaceLayerValue]{salinitySurfaceLayerValue} & salinity averaged over ocean surface layer (generally 0.1 of the ocean boundary layer) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_normalVelocitySurfaceLayer]{normalVelocitySurfaceLayer} & normal velocity averaged over ocean surface layer (generally 0.1 of the ocean boundary layer) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_surfaceVelocityZonal]{surfaceVelocityZonal} & Zonal surface velocity reconstructed at cell centers \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_surfaceVelocityMeridional]{surfaceVelocityMeridional} & Meridional surface velocity reconstructed at cell centers \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_surfacePressure]{surfacePressure} & Pressure at the sea surface due to atmosphere, sea ice, frazil and land ice \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SSHGradientZonal]{SSHGradientZonal} & Zonal gradient of SSH reconstructed at cell centers \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SSHGradientMeridional]{SSHGradientMeridional} & Meridional gradient of SSH reconstructed at cell centers \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_zMid]{zMid} & z-coordinate of the mid-depth of the layer \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_zTop]{zTop} & z-coordinate of the top of the layer \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_density]{density} & density \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_displacedDensity]{displacedDensity} & Density displaced adiabatically to the mid-depth one layer deeper.  That is, layer k has been displaced to the depth of layer k+1. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_potentialDensity]{potentialDensity} & potential density: density displaced adiabatically to the mid-depth of top layer \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_inSituThermalExpansionCoeff]{inSituThermalExpansionCoeff} & Thermal expansion coefficient (alpha), defined as $-1/\rho d\rho/dT$ (note negative sign).  This is in situ, i.e. not displaced to another depth. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_inSituSalineContractionCoeff]{inSituSalineContractionCoeff} & Saline contraction coefficient (beta), defined as $1/\rho d\rho/dS$.  This is also called the haline contraction coefficient.  This is in situ, i.e. not displaced to another depth. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_BruntVaisalaFreqTop]{BruntVaisalaFreqTop} & Brunt Vaisala frequency defined at the center (horizontally) and top (vertically) of cell \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_montgomeryPotential]{montgomeryPotential} & Montgomery potential, may be used as the pressure for isopycnal coordinates. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_pressure]{pressure} & pressure used in the momentum equation \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_modifyLandIcePressureMask]{modifyLandIcePressureMask} & A mask indicating where landIcePressure can be modified during iterative init.  The mask is 1 under (and perhaps near) ice shelves and 0 elsewhere. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_normalTransportVelocity]{normalTransportVelocity} & horizontal velocity used to transport mass and tracers \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_wettingVelocityFactor]{wettingVelocityFactor} & Scaling factor for normalVelocity and its tendency to prevent drying of cell between 0 (no scaling) and 1 (normalVelocity and tendency set to 0). \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_vertAleTransportTop]{vertAleTransportTop} & vertical transport through the layer interface at the top of the cell \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_vertVelocityTop]{vertVelocityTop} & vertical velocity defined at center (horizontally) and top (vertically) of cell \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_vertTransportVelocityTop]{vertTransportVelocityTop} & vertical tracer-transport velocity defined at center (horizontally) and top (vertically) of cell.  This is not the vertical ALE transport, but is Eulerian (fixed-frame) in the vertical, and computed from the continuity equation from the horizontal total tracer-transport velocity. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_vertGMBolusVelocityTop]{vertGMBolusVelocityTop} & vertical tracer-transport velocity defined at center (horizontally) and top (vertically) of cell.  This is not the vertical ALE transport, but is Eulerian (fixed-frame) in the vertical, and computed from the continuity equation from the horizontal GM Bolus velocity. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_vertMLEBolusVelocityTop]{vertMLEBolusVelocityTop} & vertical tracer-transport velocity defined at center (horizontally) and top (vertically) of cell.  This is not the vertical ALE transport, but is Eulerian (fixed-frame) in the vertical, and computed from the continuity equation from the horizontal MLE (submesoscale) Bolus velocity. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_tangentialVelocity]{tangentialVelocity} & horizontal velocity, tangential to an edge \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_layerThicknessEdgeDrag]{layerThicknessEdgeDrag} & layer thickness to be used for drag terms \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_layerThicknessEdgeMean]{layerThicknessEdgeMean} & layer thickness averaged from cell center to edges \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_layerThicknessEdgeFlux]{layerThicknessEdgeFlux} & layer thickness used for fluxes through edges. May be centered, upwinded, or a combination of the two. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_layerThicknessVertex]{layerThicknessVertex} & layer thickness averaged from cell center to vertices \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_kineticEnergyCell]{kineticEnergyCell} & kinetic energy of horizontal velocity on cells \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_viscosity]{viscosity} & horizontal viscosity \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_divergence]{divergence} & divergence of horizontal velocity \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_circulation]{circulation} & area-integrated vorticity \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_relativeVorticity]{relativeVorticity} & curl of horizontal velocity, defined at vertices \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_relativeVorticityCell]{relativeVorticityCell} & curl of horizontal velocity, averaged from vertices to cell centers \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_normalizedRelativeVorticityEdge]{normalizedRelativeVorticityEdge} & curl of horizontal velocity divided by layer thickness, averaged from vertices to edges \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_normalizedPlanetaryVorticityEdge]{normalizedPlanetaryVorticity\-Edge} & earth's rotational rate (Coriolis parameter, f) divided by layer thickness, averaged from vertices to edges \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_normalizedRelativeVorticityCell]{normalizedRelativeVorticityCell} & curl of horizontal velocity divided by layer thickness, averaged from vertices to cell centers \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_barotropicForcing]{barotropicForcing} & Barotropic tendency computed from the baroclinic equations in stage 1 of the split-explicit algorithm. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_barotropicThicknessFlux]{barotropicThicknessFlux} & Barotropic thickness flux at each edge, used to advance sea surface height in each subcycle of stage 2 of the split-explicit algorithm. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_velocityX]{velocityX} & component of horizontal velocity in the x-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_velocityY]{velocityY} & component of horizontal velocity in the y-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_velocityZ]{velocityZ} & component of horizontal velocity in the z-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_velocityZonal]{velocityZonal} & component of horizontal velocity in the eastward direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_velocityMeridional]{velocityMeridional} & component of horizontal velocity in the northward direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_transportVelocityX]{transportVelocityX} & component of horizontal velocity used to transport mass and tracers in the x-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_transportVelocityY]{transportVelocityY} & component of horizontal velocity used to transport mass and tracers in the y-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_transportVelocityZ]{transportVelocityZ} & component of horizontal velocity used to transport mass and tracers in the z-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_transportVelocityZonal]{transportVelocityZonal} & component of horizontal velocity used to transport mass and tracers in the eastward direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_transportVelocityMeridional]{transportVelocityMeridional} & component of horizontal velocity used to transport mass and tracers in the northward direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gradSSH]{gradSSH} & Gradient of sea surface height at edges. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gradSSHX]{gradSSHX} & X Component of the gradient of sea surface height at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gradSSHY]{gradSSHY} & Y Component of the gradient of sea surface height at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gradSSHZ]{gradSSHZ} & Z Component of the gradient of sea surface height at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gradSSHZonal]{gradSSHZonal} & Zonal Component of the gradient of sea surface height at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gradSSHMeridional]{gradSSHMeridional} & Meridional Component of the gradient of sea surface height at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_normalGMBolusVelocity]{normalGMBolusVelocity} & Bolus velocity in Gent-McWilliams eddy parameterization \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_normalMLEvelocity]{normalMLEvelocity} & Velocity from mixed layer eddies (fox kemper 2011 submesoscale parameterization) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_cGMphaseSpeed]{cGMphaseSpeed} & phase speed for the bolus velocity calculation \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_betaEdge]{betaEdge} & meridional gradient of the coriolis parameter, used in the mesoscale eddy parameterization schemes \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gmKappaScaling]{gmKappaScaling} & spatially and depth varying GM kappa.  The scaling is based on the Brunt Vaisala Frequency relative to a maximum value below the mixed layer, follows from Danabasoglu and Marshall 2007.  If config\_GM\_closure is not set to N2\_dependent the scaling value is set to 1 everywhere. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_RediKappaSfcTaper]{RediKappaSfcTaper} & Scaling coefficient for Redi kappa. Varies from 0 to 1. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_rediLimiterCount]{rediLimiterCount} & count of times redi limiter is invoked on a timestep \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gradDensityEddy]{gradDensityEddy} & horizontal gradient of density at cell edge and interfaces in vertical.  this is used for the GM parameterization and the submesoscale eddy parameterization \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_mleVelocityZonal]{mleVelocityZonal} & Bolus velocity in fox-kemper mle parameterization, zonal-direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_mleVelocityMeridional]{mleVelocityMeridional} & Bolus velocity in fox-kemper mle parameterization, meridional-direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_eddyVelocityX]{eddyVelocityX} & Bolus velocity in Gent-McWilliams eddy or submesoscale parameterization, x-direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_eddyVelocityY]{eddyVelocityY} & Bolus velocity in Gent-McWilliams or submesoscale eddy parameterization, y-direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_eddyVelocityZ]{eddyVelocityZ} & eddy Bolus velocity in Gent-McWilliams or submesoscale eddy parameterization, z-direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_GMBolusVelocityZonal]{GMBolusVelocityZonal} & Bolus velocity in Gent-McWilliams eddy parameterization, zonal-direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_GMBolusVelocityMeridional]{GMBolusVelocityMeridional} & Bolus velocity in Gent-McWilliams eddy parameterization, meridional-direction \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_RiTopOfCell]{RiTopOfCell} & gradient Richardson number defined at the center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_RiTopOfEdge]{RiTopOfEdge} & gradient Richardson number defined at the edge (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_vertViscTopOfEdge]{vertViscTopOfEdge} & vertical viscosity defined at the edge (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_vertViscTopOfCell]{vertViscTopOfCell} & vertical viscosity defined at the cell center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_vertDiffTopOfCell]{vertDiffTopOfCell} & vertical diffusion defined at the cell center (horizontally) and top (vertically) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_bulkRichardsonNumber]{bulkRichardsonNumber} & CVMix/KPP: bulk Richardson number \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_bulkRichardsonNumberBuoy]{bulkRichardsonNumberBuoy} & CVMix/KPP: contribution of buoyancy to bulk Richardson number \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_bulkRichardsonNumberShear]{bulkRichardsonNumberShear} & CVMix/KPP: contribution of shear to bulk Richardson number \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_unresolvedShear]{unresolvedShear} & CVMix/KPP: contribution of unresolved velocity to vertical shear \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_boundaryLayerDepth]{boundaryLayerDepth} & CVMix/KPP: diagnosed depth of the ocean surface boundary layer \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_boundaryLayerDepthSmooth]{boundaryLayerDepthSmooth} & CVMix/KPP: smoothed boundary layer depth \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_boundaryLayerDepthEdge]{boundaryLayerDepthEdge} & CVMix/KPP: diagnosed depth of the ocean surface boundary layer averaged to cell edges \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_vertNonLocalFluxTemp]{vertNonLocalFluxTemp} & CVMix/KPP: nonlocal boundary layer mixing term for temperature \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_indexBoundaryLayerDepth]{indexBoundaryLayerDepth} & CVMix/KPP: int(indexBoundaryLayerDepth) is vertical layer within which boundaryLayerDepth resides. mod(indexBoundaryLayerDepth) indicates whether boundaryLayerDepth resides above layer center (value = 0.25) or below layer center (value=0.75) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_indexSurfaceLayerDepth]{indexSurfaceLayerDepth} & CVMix/KPP: surface layer entirely encompasses int(indexSurfaceLayerDepth) vertical layers and fraction(indexSurfaceLayerDepth) of the int(indexSurfaceLayerDepth)+1 layer. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_surfaceFrictionVelocity]{surfaceFrictionVelocity} & CVMix/KPP: diagnosed surface friction velocity defined as square root of (mag(wind stress) / reference density) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_penetrativeTemperatureFluxOBL]{penetrativeTemperatureFluxOBL} & CVMix/KPP: Penetrative temperature flux at the bottom of boundary layer due to solar radiation. Positive is into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_bottomLayerShortwaveTemperatureFlux]{bottomLayerShortwave\-TemperatureFlux} & Solar flux that reaches bottom of the ocean and does not impact temperature \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_surfaceBuoyancyForcing]{surfaceBuoyancyForcing} & CVMix/KPP: diagnosed surface buoyancy flux due to heat, salt and freshwater fluxes. Positive flux increases buoyancy. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_indMLD]{indMLD} & index of model where mixed layer depth occurs (always one past) \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_dThreshMLD]{dThreshMLD} & mixed layer depth based on density threshold \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_slopeTriadUp]{slopeTriadUp} & Magnitude of slope of isopycnal surface, using triad through this cell and edge, angled up. Uses expansion of equation of state. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_slopeTriadDown]{slopeTriadDown} & Magnitude of slope of isopycnal surface, using triad through this cell and edge, angled up. Uses expansion of equation of state. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_limiterUp]{limiterUp} & Magnitude of slope of isopycnal surface, using triad through this cell and edge, angled up. Uses expansion of equation of state. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_limiterDown]{limiterDown} & Magnitude of slope of isopycnal surface, using triad through this cell and edge, angled up. Uses expansion of equation of state. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_k33]{k33} & The (3,3) entry of the Redi diffusion tensor. Added to the model vertical diffusion. Defined at the top of cell k \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gmStreamFuncTopOfEdge]{gmStreamFuncTopOfEdge} & GM stream function \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_GMStreamFuncX]{GMStreamFuncX} & GM stream function \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_GMStreamFuncY]{GMStreamFuncY} & GM stream function \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_GMStreamFuncZ]{GMStreamFuncZ} & GM stream function \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_GMStreamFuncZonal]{GMStreamFuncZonal} & GM stream function \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_GMStreamFuncMeridional]{GMStreamFuncMeridional} & GM stream function \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gmBolusKappa]{gmBolusKappa} & GM Bolus Kappa value.  On output, it has NOT been multiplied by the horizontal taper array gmHorizontalTaper, because that is applied at the end to the normalGMBolusVelocity variable, not to the gmBolusKappa. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_RediKappa]{RediKappa} & Redi Kappa value.  On output, it has already been multiplied by the horizontal taper array RediHorizontalTaper (as opposed to gmBolusKappa, which has not been multiplied by the horizontal taper). \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_RediHorizontalTaper]{RediHorizontalTaper} & Horizontal tapering for Redi. Varies between 0 and 1. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_gmHorizontalTaper]{gmHorizontalTaper} & Horizontal tapering for GM. Varies between 0 and 1. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_RossbyRadius]{RossbyRadius} & Rossby Radius, computed in GM routine for some settings \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_surfaceFluxAttenuationCoefficient]{surfaceFluxAttenuation\-Coefficient} & The spatially-dependent length scale of exponential decay of surface fluxes. Fluxes are multiplied by $e^{z/\gamma}$, where this coefficient is $\gamma$. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_surfaceFluxAttenuationCoefficientRunoff]{surfaceFluxAttenuation\-CoefficientRunoff} & The spatially-dependent length scale of exponential decay of river runoff. Fluxes are multiplied by $e^{z/\gamma}$, where this coefficient is $\gamma$. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_topographic_wave_drag]{topographic\_wave\_drag} & wave drag coefficient or 1/(rinv) where rinv is the e-folding time used in HyCOM \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_landIceFrictionVelocity]{landIceFrictionVelocity} & The friction velocity $u_*$ under land ice \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_topDrag]{topDrag} & Top drag at the surface of the ocean defined at edge midpoints. Magnitude in direction of edge normal. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_topDragMagnitude]{topDragMagnitude} & Magnitude of top drag at the surface of the ocean, at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_landIceBoundaryLayerTemperature]{landIceBoundaryLayer\-Temperature} & The temperature averaged over the sub-ice-shelf boundary layer \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_landIceBoundaryLayerSalinity]{landIceBoundaryLayerSalinity} & The salinity averaged over the sub-ice-shelf boundary layer \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_landIceHeatTransferVelocity]{landIceHeatTransferVelocity} & friction velocity times nondimensional heat transfer coefficient \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_landIceSaltTransferVelocity]{landIceSaltTransferVelocity} & friction velocity times nondimensional salt transfer coefficient \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_rx1Cell]{rx1Cell} & The Haney number (rx1), a measure of hydrostatic consistency, at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_rx1Edge]{rx1Edge} & The Haney number (rx1), a measure of hydrostatic consistency, at edges. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_rx1MaxCell]{rx1MaxCell} & The Haney number (rx1) is ratio of vertical displacement to cell thickness between two neighboring horizontal cells.  It is computed at each edge.  This cell-based value is the maximum over all edges and vertical levels of each cell. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_rx1MaxEdge]{rx1MaxEdge} & The maximum Haney number (rx1) in a vertical column, measured at edges. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_globalRx1Max]{globalRx1Max} & The global maximum Haney number (rx1). \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_globalVerticalStretchMax]{globalVerticalStretchMax} & The global maximum stretching of the vertical grid compared with z-level. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_globalVerticalStretchMin]{globalVerticalStretchMin} & The global minimum stretching of the vertical grid compared with z-level. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_rx1InitSmoothingMask]{rx1InitSmoothingMask} & A mask indicating where layer interface and thickness smoothing is to be performed during Haney number constrained initializaiton. \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_verticalStretch]{verticalStretch} & the stretch factor of each layer compared with the default z-level coordinate \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_pressureAdjustedSSH]{pressureAdjustedSSH} & sea surface height adjusted by sea surface pressure \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_barotropicCoriolisTerm]{barotropicCoriolisTerm} & f * uPerp for the split-implicit time stepping \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_r0]{SIvec\_r0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_r1]{SIvec\_r1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_rh0]{SIvec\_rh0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_rh1]{SIvec\_rh1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_r00]{SIvec\_r00} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_ph0]{SIvec\_ph0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_ph1]{SIvec\_ph1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_v0]{SIvec\_v0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_s0]{SIvec\_s0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_s1]{SIvec\_s1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_sh0]{SIvec\_sh0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_sh1]{SIvec\_sh1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_w0]{SIvec\_w0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_w1]{SIvec\_w1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_wh0]{SIvec\_wh0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_wh1]{SIvec\_wh1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_q0]{SIvec\_q0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_q1]{SIvec\_q1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_qh0]{SIvec\_qh0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_qh1]{SIvec\_qh1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_z0]{SIvec\_z0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_z1]{SIvec\_z1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_zh0]{SIvec\_zh0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_zh1]{SIvec\_zh1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_t0]{SIvec\_t0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_t1]{SIvec\_t1} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_SIvec_y0]{SIvec\_y0} & A vector used in the split-implicit barotropic mode solver \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_ssh_sal]{ssh\_sal} & sea surface height perturbation from self-attraction and loading \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_ssh_sal_grad]{ssh\_sal\_grad} & gradient of sea surface height perturbation from self-attraction and loading \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_normalVelocityTendOld]{normalVelocityTendOld} & time tendency of normal component of velocity at the previous time step used in the split-explicit AB2 time stepping \\
    \hline
    \hyperref[subsec:var_sec_diagnostics_CoriolisTermOld]{CoriolisTermOld} & Coriolis term at the previous time step used in the split-explicit AB2 time stepping \\
    \hline
\end{longtable}
\end{center}
}
\section[shortwave]{\hyperref[sec:var_sec_shortwave]{shortwave}}
\label{sec:var_tab_shortwave}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_shortwave_chlorophyllData]{chlorophyllData} & concentration of chlorophyll data \\
    \hline
    \hyperref[subsec:var_sec_shortwave_zenithAngle]{zenithAngle} & the cos of the solar zenith angle \\
    \hline
    \hyperref[subsec:var_sec_shortwave_clearSkyRadiation]{clearSkyRadiation} & the fractional cloudiness (between 0 and 1) \\
    \hline
\end{longtable}
\end{center}
}
\section[forcing]{\hyperref[sec:var_sec_forcing]{forcing}}
\label{sec:var_tab_forcing}
\input{ocean/section_descriptions/forcing_struct.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_forcing_surfaceStress]{surfaceStress} & The component of the total surface stress on the ocean defined at edge midpoints and pointing in the direction of the edge normal.  This field the sum of constituent stresses (e.g. wind stress and top drag) and is used to compute a tendency in the normal velocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_surfaceStressMagnitude]{surfaceStressMagnitude} & Magnitude of surface stress, at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_forcing_surfaceThicknessFlux]{surfaceThicknessFlux} & Flux of mass through the ocean surface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_surfaceThicknessFluxRunoff]{surfaceThicknessFluxRunoff} & Flux of mass through the ocean surface due to river runoff. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_windStressZonal]{windStressZonal} & Zonal (eastward) component of wind stress at cell centers from coupler. Positive eastward. \\
    \hline
    \hyperref[subsec:var_sec_forcing_windStressMeridional]{windStressMeridional} & Meridional (northward) component of wind stress at cell centers from coupler. Positive northward. \\
    \hline
    \hyperref[subsec:var_sec_forcing_bottomDrag]{bottomDrag} & Bottom drag Cd coefficient in cells. \\
    \hline
    \hyperref[subsec:var_sec_forcing_nForcingGroupCounter]{nForcingGroupCounter} & {\bf \color{red} MISSING} \\
    \hline
    \hyperref[subsec:var_sec_forcing_forcingGroupNames]{forcingGroupNames} & {\bf \color{red} MISSING} \\
    \hline
    \hyperref[subsec:var_sec_forcing_forcingGroupRestartTimes]{forcingGroupRestartTimes} & {\bf \color{red} MISSING} \\
    \hline
    \hyperref[subsec:var_sec_forcing_seaIcePressure]{seaIcePressure} & Pressure at the sea surface due to sea ice. \\
    \hline
    \hyperref[subsec:var_sec_forcing_atmosphericPressure]{atmosphericPressure} & Pressure at the sea surface due to the atmosphere. \\
    \hline
    \hyperref[subsec:var_sec_forcing_seaIceEnergy]{seaIceEnergy} & Energy per unit area trapped in frazil ice formation. Always $\ge$ 0.0. \\
    \hline
    \hyperref[subsec:var_sec_forcing_penetrativeTemperatureFlux]{penetrativeTemperatureFlux} & Penetrative temperature flux at the surface due to solar radiation. Positive is into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_fractionAbsorbed]{fractionAbsorbed} & Divergence of transmission through interfaces of surface fluxes below the surface layer at cell centers. These are not applied to short wave. \\
    \hline
    \hyperref[subsec:var_sec_forcing_fractionAbsorbedRunoff]{fractionAbsorbedRunoff} & Divergence of transmission through interfaces of surface fluxes below the surface layer at cell centers. These are applied only to river runoff. \\
    \hline
    \hyperref[subsec:var_sec_forcing_latentHeatFlux]{latentHeatFlux} & Latent heat flux at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_sensibleHeatFlux]{sensibleHeatFlux} & Sensible heat flux at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_longWaveHeatFluxUp]{longWaveHeatFluxUp} & Upward long wave heat flux at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_longWaveHeatFluxDown]{longWaveHeatFluxDown} & Downward long wave heat flux at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_seaIceHeatFlux]{seaIceHeatFlux} & Sea ice heat flux at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_icebergHeatFlux]{icebergHeatFlux} & Iceberg heat flux at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_shortWaveHeatFlux]{shortWaveHeatFlux} & Short wave flux at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_rainTemperatureFlux]{rainTemperatureFlux} & Heat flux associated with rain at cell centers sent to coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_evapTemperatureFlux]{evapTemperatureFlux} & Heat flux associated with Evaporation at cell centers sent to coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_seaIceTemperatureFlux]{seaIceTemperatureFlux} & Heat flux associated with sea ice melt water at cell centers sent to coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_icebergTemperatureFlux]{icebergTemperatureFlux} & Heat flux associated with iceberg melt at cell centers sent to coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_totalFreshWaterTemperatureFlux]{totalFreshWaterTemperatureFlux} & Sum of heat fluxes associated with water fluxes cell centers sent to coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_evaporationFlux]{evaporationFlux} & Evaporation flux at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_seaIceSalinityFlux]{seaIceSalinityFlux} & Sea ice salinity flux at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_seaIceFreshWaterFlux]{seaIceFreshWaterFlux} & Fresh water flux from sea ice at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_icebergFreshWaterFlux]{icebergFreshWaterFlux} & Fresh water flux from iceberg melt at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverRunoffFlux]{riverRunoffFlux} & Fresh water flux from river runoff at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_removedRiverRunoffFlux]{removedRiverRunoffFlux} & Fresh water flux from river runoff from the coupler that was removed due to config\_remove\_AIS\_coupler\_runoff option. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_totalRemovedRiverRunoffFlux]{totalRemovedRiverRunoffFlux} & Global sum of fresh water flux from river runoff from the coupler that was removed due to config\_remove\_AIS\_coupler\_runoff option. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceRunoffFlux]{iceRunoffFlux} & Fresh water flux from ice runoff at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_removedIceRunoffFlux]{removedIceRunoffFlux} & Fresh water flux from ice runoff from the coupler that was removed due to config\_remove\_AIS\_coupler\_runoff option. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_totalRemovedIceRunoffFlux]{totalRemovedIceRunoffFlux} & Global sum of fresh water flux from ice runoff from the coupler that was removed due to config\_remove\_AIS\_coupler\_runoff option. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_rainFlux]{rainFlux} & Fresh water flux from rain at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_snowFlux]{snowFlux} & Fresh water flux from snow at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFraction]{iceFraction} & Fraction of sea ice coverage at cell centers from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_windSpeed10m]{windSpeed10m} & Wind speed at 10 meter. \\
    \hline
    \hyperref[subsec:var_sec_forcing_stokesDriftZonal]{stokesDriftZonal} & Zonal component of the wave-induced Stokes drift current. \\
    \hline
    \hyperref[subsec:var_sec_forcing_stokesDriftMeridional]{stokesDriftMeridional} & Meridional component of the wave-induced Stokes drift current. \\
    \hline
    \hyperref[subsec:var_sec_forcing_stokesDriftSurfaceZonal]{stokesDriftSurfaceZonal} & Zonal component of the wave-induced Stokes surface drift current. \\
    \hline
    \hyperref[subsec:var_sec_forcing_stokesDriftSurfaceMeridional]{stokesDriftSurfaceMeridional} & Meridional component of the wave-induced Stokes surface drift current. \\
    \hline
    \hyperref[subsec:var_sec_forcing_significantWaveHeight]{significantWaveHeight} & Significant wave height is the average of the highest 1/3 of the waves \\
    \hline
    \hyperref[subsec:var_sec_forcing_peakWaveFrequency]{peakWaveFrequency} & Frequency of peak of wave spectrum \\
    \hline
    \hyperref[subsec:var_sec_forcing_peakWaveDirection]{peakWaveDirection} & Direction of peak of wave spectrum \\
    \hline
    \hyperref[subsec:var_sec_forcing_langmuirNumber]{langmuirNumber} & Projected surface layer averaged Langmuir number from Van Roekel et al. 2012. \\
    \hline
    \hyperref[subsec:var_sec_forcing_stokesDriftZonalWavenumber]{stokesDriftZonalWavenumber} & Zonal component of the partitioned wave-induced Stokes drift current. Wavenumbers 1-6 are used to recontruct the full depth-dependent Stokes drift profile \\
    \hline
    \hyperref[subsec:var_sec_forcing_stokesDriftMeridionalWavenumber]{stokesDriftMeridional\-Wavenumber} & Meridional component of the partitioned wave-induced Stokes drift current. Wavenumbers 1-6 are used to recontruct the full depth-dependent Stokes drift profile \\
    \hline
    \hyperref[subsec:var_sec_forcing_nAccumulatedCoupled]{nAccumulatedCoupled} & Number of accumulations in time averaging of coupler fields \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgTemperatureSurfaceValue]{avgTemperatureSurfaceValue} & Time averaged potential temperature extrapolated to ocean surface \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgSalinitySurfaceValue]{avgSalinitySurfaceValue} & Time averaged salinity extrapolated to ocean surface \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgSurfaceVelocityZonal]{avgSurfaceVelocityZonal} & Time averaged zonal surface velocity \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgSurfaceVelocityMeridional]{avgSurfaceVelocityMeridional} & Time averaged meridional surface velocity \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgSSHGradientZonal]{avgSSHGradientZonal} & Time averaged zonal gradient of SSH \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgSSHGradientMeridional]{avgSSHGradientMeridional} & Time averaged meridional gradient of SSH \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgTotalFreshWaterTemperatureFlux]{avgTotalFreshWaterTemperature\-Flux} & Sum of heat fluxes associated with water fluxes cell centers sent to coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceFraction]{landIceFraction} & The fraction of each cell covered by land ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceMask]{landIceMask} & Mask indicating where land-ice is present (1) or absent (0) \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceFloatingFraction]{landIceFloatingFraction} & The fraction of each cell covered by an ice shelf \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceFloatingMask]{landIceFloatingMask} & Mask indicating where an ice shelf is present (1) or absent (0) \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIcePressure]{landIcePressure} & Pressure defined at the sea surface due to land ice. \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceDraft]{landIceDraft} & The elevation of the interface between land ice and the ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceSurfaceTemperature]{landIceSurfaceTemperature} & temperature at the surface of land ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceInterfaceTemperature]{landIceInterfaceTemperature} & The temperature at the land ice-ocean interface (the local freezing temperature) \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceInterfaceSalinity]{landIceInterfaceSalinity} & The salinity at the land ice-ocean interface \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceFreshwaterFlux]{landIceFreshwaterFlux} & Flux of mass through the ocean surface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_landIceHeatFlux]{landIceHeatFlux} & Flux of heat into the ocean at land ice-ocean interface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_heatFluxToLandIce]{heatFluxToLandIce} & Flux of heat out of ice at land ice-ocean interface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgLandIceBoundaryLayerTemperature]{avgLandIceBoundaryLayer\-Temperature} & The time-averaged temperature averaged over the sub-ice-shelf boundary layer \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgLandIceBoundaryLayerSalinity]{avgLandIceBoundaryLayer\-Salinity} & The time-averaged salinity averaged over the sub-ice-shelf boundary layer \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgLandIceHeatTransferVelocity]{avgLandIceHeatTransferVelocity} & time-averaged friction velocity times nondimensional heat transfer coefficient \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgLandIceSaltTransferVelocity]{avgLandIceSaltTransferVelocity} & time-averaged friction velocity times nondimensional salt transfer coefficient \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgEffectiveDensityInLandIce]{avgEffectiveDensityInLandIce} & The time-averaged effective ocean density within ice shelves based on Archimedes' principle. \\
    \hline
    \hyperref[subsec:var_sec_forcing_dataLandIceFreshwaterFlux]{dataLandIceFreshwaterFlux} & Flux of mass through the ocean surface, as read in from a forcing file. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_dataLandIceHeatFlux]{dataLandIceHeatFlux} & Flux of heat into the ocean at land ice-ocean interface, as read in from a forcing file. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalInputMask]{tidalInputMask} & Input mask for application of tidal forcing where 1 is applied tidal forcing \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalBCValue]{tidalBCValue} & Value of ssh height in cell for tidal boundary condition \\
    \hline
    \hyperref[subsec:var_sec_forcing_vegetationHeight]{vegetationHeight} & Stem height of the vegetation \\
    \hline
    \hyperref[subsec:var_sec_forcing_vegetationDiameter]{vegetationDiameter} & Stem diameter of the vegetation \\
    \hline
    \hyperref[subsec:var_sec_forcing_vegetationDensity]{vegetationDensity} & Stem density of the vegetation per unit area \\
    \hline
    \hyperref[subsec:var_sec_forcing_vegetationMask]{vegetationMask} & Mask value 1 as vegetated cell, and 0 as non-vegetated cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_vegetationManning]{vegetationManning} & Manning roughness coefficient induced by vegetation \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalLayerThicknessTendency]{tidalLayerThicknessTendency} & layer thickness tendency due to tidal forcing \\
    \hline
    \hyperref[subsec:var_sec_forcing_frazilLayerThicknessTendency]{frazilLayerThicknessTendency} & layer thickness tendency due to frazil processes \\
    \hline
    \hyperref[subsec:var_sec_forcing_frazilTemperatureTendency]{frazilTemperatureTendency} & temperature tendency due to frazil processes \\
    \hline
    \hyperref[subsec:var_sec_forcing_frazilSalinityTendency]{frazilSalinityTendency} & salinity tendency due to frazil processes \\
    \hline
    \hyperref[subsec:var_sec_forcing_frazilSurfacePressure]{frazilSurfacePressure} & surface pressure forcing due to weight of frazil ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalPotentialEta]{tidalPotentialEta} & Equilibrium tidal potential \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalPotentialConstituentFrequency]{tidalPotentialConstituent\-Frequency} & Frequency of tidal constituents \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalPotentialConstituentAmplitude]{tidalPotentialConstituent\-Amplitude} & Amplitude of tidal constituents \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalPotentialConstituentLoveNumbers]{tidalPotentialConstituentLove\-Numbers} & Love number combinations for tidal constituents \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalPotentialConstituentNodalAmplitude]{tidalPotentialConstituentNodal\-Amplitude} & Amplitude nodal factor for tidal constituents \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalPotentialConstituentNodalPhase]{tidalPotentialConstituentNodal\-Phase} & Phase nodal factor for tidal constituents \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalPotentialConstituentAstronomical]{tidalPotentialConstituent\-Astronomical} & Astronomical argument for tidal constituents \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalPotentialConstituentType]{tidalPotentialConstituentType} & Spieces code for tidal constituents: long-period = 0, diurnal = 1, semi-diurnal = 2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tidalPotentialLatitudeFunction]{tidalPotentialLatitudeFunction} & Latitude function for tidal constituents: long-period = $3\sin^2(\phi)-1$, diurnal = $\sin(2\phi)$, semi-diurnal = $\cos^2(\phi)$ \\
    \hline
    \hyperref[subsec:var_sec_forcing_sshSubcycleCurWithTides]{sshSubcycleCurWithTides} & SSH - tidal potential in split explicit  \\
    \hline
    \hyperref[subsec:var_sec_forcing_sshSubcycleNewWithTides]{sshSubcycleNewWithTides} & SSH - tidal potential in split explicit  \\
    \hline
    \hyperref[subsec:var_sec_forcing_coastalSmoothingFactor]{coastalSmoothingFactor} & Multiplication factors to smooth ssh at coastlines for SAL caculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperatureSurfaceFlux]{temperatureSurfaceFlux} & Flux of temperature through the ocean surface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinitySurfaceFlux]{salinitySurfaceFlux} & Flux of salinity through the ocean surface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperatureSurfaceFluxRunoff]{temperatureSurfaceFluxRunoff} & Flux of temperature through the ocean surface due to river runoff. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinitySurfaceFluxRunoff]{salinitySurfaceFluxRunoff} & Flux of salinity through the ocean surface due to river runoff. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperatureSurfaceFluxRemoved]{temperatureSurfaceFluxRemoved} & Flux of temperature that is ignored coming into the ocean. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinitySurfaceFluxRemoved]{salinitySurfaceFluxRemoved} & Flux of salinity that is ignored coming into the ocean. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_nonLocalTemperatureSurfaceFlux]{nonLocalTemperatureSurfaceFlux} & total flux of temperature (including thickness contributions) through ocean surface \\
    \hline
    \hyperref[subsec:var_sec_forcing_nonLocalSalinitySurfaceFlux]{nonLocalSalinitySurfaceFlux} & total flux of salinity (including thickness contributions) through ocean surface \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperaturePistonVelocity]{temperaturePistonVelocity} & A non-negative field controlling the rate at which temperature is restored to temperatureSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinityPistonVelocity]{salinityPistonVelocity} & A non-negative field controlling the rate at which salinity is restored to salinitySurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperatureSurfaceRestoringValue]{temperatureSurfaceRestoring\-Value} & Temperature is restored toward this field at a rate controlled by temperaturePistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinitySurfaceRestoringValue]{salinitySurfaceRestoringValue} & Salinity is restored toward this field at a rate controlled by salinityPistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperatureInteriorRestoringRate]{temperatureInteriorRestoringRate} & A non-negative field controlling the rate at which temperature is restored to temperatureInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinityInteriorRestoringRate]{salinityInteriorRestoringRate} & A non-negative field controlling the rate at which salinity is restored to salinityInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperatureInteriorRestoringValue]{temperatureInteriorRestoring\-Value} & Temperature is restored toward this field at a rate controlled by temperatureInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinityInteriorRestoringValue]{salinityInteriorRestoringValue} & Salinity is restored toward this field at a rate controlled by salinityInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperatureExponentialDecayRate]{temperatureExponentialDecay\-Rate} & A non-negative field controlling the exponential decay of temperature \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinityExponentialDecayRate]{salinityExponentialDecayRate} & A non-negative field controlling the exponential decay of salinity \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperatureIdealAgeMask]{temperatureIdealAgeMask} & In top layer, temperature is reset to temperature * temperatureIdealAgeMask, valid values of temperatureIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinityIdealAgeMask]{salinityIdealAgeMask} & In top layer, salinity is reset to salinity * salinityIdealAgeMask, valid values of salinityIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_temperatureTTDMask]{temperatureTTDMask} & In top layer, temperature is reset to TTDMask, valid values of temperatureTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_salinityTTDMask]{salinityTTDMask} & In top layer, salinity is reset to salinityTTDMask, valid values of salinityTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1SurfaceFlux]{tracer1SurfaceFlux} & Flux of tracer1 through the ocean surface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2SurfaceFlux]{tracer2SurfaceFlux} & Flux of tracer2 through the ocean surface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3SurfaceFlux]{tracer3SurfaceFlux} & Flux of tracer3 through the ocean surface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1SurfaceFluxRunoff]{tracer1SurfaceFluxRunoff} & Flux of tracer1 through the ocean surface due to river runoff. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2SurfaceFluxRunoff]{tracer2SurfaceFluxRunoff} & Flux of tracer2 through the ocean surface due to river runoff. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3SurfaceFluxRunoff]{tracer3SurfaceFluxRunoff} & Flux of tracer3 through the ocean surface due to river runoff. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1SurfaceFluxRemoved]{tracer1SurfaceFluxRemoved} & Flux of tracer1 that is ignored coming into the ocean. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2SurfaceFluxRemoved]{tracer2SurfaceFluxRemoved} & Flux of tracer2 that is ignored coming into the ocean. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3SurfaceFluxRemoved]{tracer3SurfaceFluxRemoved} & Flux of tracer3 that is ignored coming into the ocean. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1PistonVelocity]{tracer1PistonVelocity} & A non-negative field controlling the rate at which tracer1 is restored to tracer1SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2PistonVelocity]{tracer2PistonVelocity} & A non-negative field controlling the rate at which tracer2 is restored to tracer2SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3PistonVelocity]{tracer3PistonVelocity} & A non-negative field controlling the rate at which tracer3 is restored to tracer3SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1SurfaceRestoringValue]{tracer1SurfaceRestoringValue} & tracer1 is restored toward this field at a rate controlled by tracer1PistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2SurfaceRestoringValue]{tracer2SurfaceRestoringValue} & tracer2 is restored toward this field at a rate controlled by tracer2PistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3SurfaceRestoringValue]{tracer3SurfaceRestoringValue} & tracer3 is restored toward this field at a rate controlled by tracer3PistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1InteriorRestoringRate]{tracer1InteriorRestoringRate} & A non-negative field controlling the rate at which tracer1 is restored to tracer1InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2InteriorRestoringRate]{tracer2InteriorRestoringRate} & A non-negative field controlling the rate at which tracer2 is restored to tracer2InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3InteriorRestoringRate]{tracer3InteriorRestoringRate} & A non-negative field controlling the rate at which tracer3 is restored to tracer3InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1InteriorRestoringValue]{tracer1InteriorRestoringValue} & tracer1 is restored toward this field at a rate controlled by tracer1InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2InteriorRestoringValue]{tracer2InteriorRestoringValue} & tracer2 is restored toward this field at a rate controlled by tracer2InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3InteriorRestoringValue]{tracer3InteriorRestoringValue} & tracer3 is restored toward this field at a rate controlled by tracer3InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1ExponentialDecayRate]{tracer1ExponentialDecayRate} & A non-negative field controlling the exponential decay of tracer1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2ExponentialDecayRate]{tracer2ExponentialDecayRate} & A non-negative field controlling the exponential decay of tracer2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3ExponentialDecayRate]{tracer3ExponentialDecayRate} & A non-negative field controlling the exponential decay of tracer3 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1IdealAgeMask]{tracer1IdealAgeMask} & In top layer, tracer1 is reset to tracer1 * tracer1IdealAgeMask, valid values of tracer1IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2IdealAgeMask]{tracer2IdealAgeMask} & In top layer, tracer2 is reset to tracer2 * tracer2IdealAgeMask, valid values of tracer2IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3IdealAgeMask]{tracer3IdealAgeMask} & In top layer, tracer3 is reset to tracer3 * tracer3IdealAgeMask, valid values of tracer3IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer1TTDMask]{tracer1TTDMask} & In top layer, tracer1 is reset to TTDMask, valid values of tracer1TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer2TTDMask]{tracer2TTDMask} & In top layer, tracer2 is reset to TTDMask, valid values of tracer2TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_tracer3TTDMask]{tracer3TTDMask} & In top layer, tracer3 is reset to TTDMask, valid values of tracer3TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4SurfaceFlux]{PO4SurfaceFlux} & Dissolved Inorganic Phosphate Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3SurfaceFlux]{NO3SurfaceFlux} & Dissolved Inorganic Nitrate Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3SurfaceFlux]{SiO3SurfaceFlux} & Dissolved Inorganic Silicate Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4SurfaceFlux]{NH4SurfaceFlux} & Dissolved Ammonia Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_FeSurfaceFlux]{FeSurfaceFlux} & Dissolved Inorganic Iron Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigSurfaceFlux]{LigSurfaceFlux} & Ligand Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2SurfaceFlux]{O2SurfaceFlux} & Dissolved Oxygen Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICSurfaceFlux]{DICSurfaceFlux} & Dissolved Inorganic Carbon Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2SurfaceFlux]{DIC\_ALT\_CO2SurfaceFlux} & Dissolved Inorganic Carbon, Alternative CO2 Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKSurfaceFlux]{ALKSurfaceFlux} & Alkalinity Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2SurfaceFlux]{ALK\_ALT\_CO2SurfaceFlux} & Alkalinity Surface Flux, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCSurfaceFlux]{DOCSurfaceFlux} & Dissolved Organic Carbon Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONSurfaceFlux]{DONSurfaceFlux} & Dissolved Organic Nitrogen Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPSurfaceFlux]{DOPSurfaceFlux} & Dissolved Organic Phosphorus Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrSurfaceFlux]{DOPrSurfaceFlux} & Refractory DOP Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrSurfaceFlux]{DONrSurfaceFlux} & Refractory DON Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrSurfaceFlux]{DOCrSurfaceFlux} & Zooplankton Carbon Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCSurfaceFlux]{zooCSurfaceFlux} & Zooplankton Carbon Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlSurfaceFlux]{spChlSurfaceFlux} & Small Phytoplankton Chlorophyll Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCSurfaceFlux]{spCSurfaceFlux} & Small Phytoplankton Carbon Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFeSurfaceFlux]{spFeSurfaceFlux} & Small Phytoplankton Iron Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPSurfaceFlux]{spPSurfaceFlux} & Small Phytoplankton Phosphorus Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3SurfaceFlux]{spCaCO3SurfaceFlux} & Small Phytoplankton Calcium Carbonate Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlSurfaceFlux]{diatChlSurfaceFlux} & Diatom Chlorophyll Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCSurfaceFlux]{diatCSurfaceFlux} & Diatom Carbon Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFeSurfaceFlux]{diatFeSurfaceFlux} & Diatom Iron Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPSurfaceFlux]{diatPSurfaceFlux} & Diatom Phosphorus Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiSurfaceFlux]{diatSiSurfaceFlux} & Diatom Silicate Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlSurfaceFlux]{diazChlSurfaceFlux} & Diazotroph Chlorophyll Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCSurfaceFlux]{diazCSurfaceFlux} & Diazotroph Carbon Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFeSurfaceFlux]{diazFeSurfaceFlux} & Diazotroph Iron Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazPSurfaceFlux]{diazPSurfaceFlux} & Diazotroph Phosphorus Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4SurfaceFluxRunoff]{PO4SurfaceFluxRunoff} & Dissolved Inorganic Phosphate Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3SurfaceFluxRunoff]{NO3SurfaceFluxRunoff} & Dissolved Inorganic Nitrate Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3SurfaceFluxRunoff]{SiO3SurfaceFluxRunoff} & Dissolved Inorganic Silicate Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4SurfaceFluxRunoff]{NH4SurfaceFluxRunoff} & Dissolved Ammonia Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_FeSurfaceFluxRunoff]{FeSurfaceFluxRunoff} & Dissolved Inorganic Iron Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigSurfaceFluxRunoff]{LigSurfaceFluxRunoff} & Ligand Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2SurfaceFluxRunoff]{O2SurfaceFluxRunoff} & Dissolved Oxygen Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICSurfaceFluxRunoff]{DICSurfaceFluxRunoff} & Dissolved Inorganic Carbon Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2SurfaceFluxRunoff]{DIC\_ALT\_CO2SurfaceFlux\-Runoff} & Dissolved Inorganic Carbon, Alternative CO2 Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKSurfaceFluxRunoff]{ALKSurfaceFluxRunoff} & Alkalinity Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2SurfaceFluxRunoff]{ALK\_ALT\_CO2SurfaceFlux\-Runoff} & Alkalinity Surface Flux Due to Runoff, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCSurfaceFluxRunoff]{DOCSurfaceFluxRunoff} & Dissolved Organic Carbon Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONSurfaceFluxRunoff]{DONSurfaceFluxRunoff} & Dissolved Organic Nitrogen Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPSurfaceFluxRunoff]{DOPSurfaceFluxRunoff} & Dissolved Organic Phosphorus Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrSurfaceFluxRunoff]{DOPrSurfaceFluxRunoff} & Refractory DOP Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrSurfaceFluxRunoff]{DONrSurfaceFluxRunoff} & Refractory DON Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrSurfaceFluxRunoff]{DOCrSurfaceFluxRunoff} & Zooplankton Carbon Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCSurfaceFluxRunoff]{zooCSurfaceFluxRunoff} & Zooplankton Carbon Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlSurfaceFluxRunoff]{spChlSurfaceFluxRunoff} & Small Phytoplankton Chlorophyll Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCSurfaceFluxRunoff]{spCSurfaceFluxRunoff} & Small Phytoplankton Carbon Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFeSurfaceFluxRunoff]{spFeSurfaceFluxRunoff} & Small Phytoplankton Iron Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPSurfaceFluxRunoff]{spPSurfaceFluxRunoff} & Small Phytoplankton Phosphorus Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3SurfaceFluxRunoff]{spCaCO3SurfaceFluxRunoff} & Small Phytoplankton Calcium Carbonate Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlSurfaceFluxRunoff]{diatChlSurfaceFluxRunoff} & Diatom Chlorophyll Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCSurfaceFluxRunoff]{diatCSurfaceFluxRunoff} & Diatom Carbon Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFeSurfaceFluxRunoff]{diatFeSurfaceFluxRunoff} & Diatom Iron Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPSurfaceFluxRunoff]{diatPSurfaceFluxRunoff} & Diatom Phosphorus Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiSurfaceFluxRunoff]{diatSiSurfaceFluxRunoff} & Diatom Silicate Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlSurfaceFluxRunoff]{diazChlSurfaceFluxRunoff} & Diazotroph Chlorophyll Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCSurfaceFluxRunoff]{diazCSurfaceFluxRunoff} & Diazotroph Carbon Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFeSurfaceFluxRunoff]{diazFeSurfaceFluxRunoff} & Diazotroph Iron Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazPSurfaceFluxRunoff]{diazPSurfaceFluxRunoff} & Diazotroph Phosphorus Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4SurfaceFluxRemoved]{PO4SurfaceFluxRemoved} & Dissolved Inorganic Phosphate Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3SurfaceFluxRemoved]{NO3SurfaceFluxRemoved} & Dissolved Inorganic Nitrate Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3SurfaceFluxRemoved]{SiO3SurfaceFluxRemoved} & Dissolved Inorganic Silicate Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4SurfaceFluxRemoved]{NH4SurfaceFluxRemoved} & Dissolved Ammonia Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_FeSurfaceFluxRemoved]{FeSurfaceFluxRemoved} & Dissolved Inorganic Iron Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigSurfaceFluxRemoved]{LigSurfaceFluxRemoved} & Dissolved Oxygen Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2SurfaceFluxRemoved]{O2SurfaceFluxRemoved} & Dissolved Oxygen Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICSurfaceFluxRemoved]{DICSurfaceFluxRemoved} & Dissolved Inorganic Carbon Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2SurfaceFluxRemoved]{DIC\_ALT\_CO2SurfaceFlux\-Removed} & Dissolved Inorganic Carbon, Alternative CO2 Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKSurfaceFluxRemoved]{ALKSurfaceFluxRemoved} & Alkalinity Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2SurfaceFluxRemoved]{ALK\_ALT\_CO2SurfaceFlux\-Removed} & Alkalinity Surface Flux that is ignored, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCSurfaceFluxRemoved]{DOCSurfaceFluxRemoved} & Dissolved Organic Carbon Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONSurfaceFluxRemoved]{DONSurfaceFluxRemoved} & Dissolved Organic Nitrogen Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPSurfaceFluxFluxRemoved]{DOPSurfaceFluxFluxRemoved} & Dissolved Organic Phosphorus Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrSurfaceFluxRemoved]{DOPrSurfaceFluxRemoved} & Refractory DOP Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrSurfaceFluxRemoved]{DONrSurfaceFluxRemoved} & Refractory DON Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrSurfaceFluxRemoved]{DOCrSurfaceFluxRemoved} & Refractory DOC Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCSurfaceFluxRemoved]{zooCSurfaceFluxRemoved} & Zooplankton Carbon Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlSurfaceFluxRemoved]{spChlSurfaceFluxRemoved} & Small Phytoplankton Chlorophyll Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCSurfaceFluxRemoved]{spCSurfaceFluxRemoved} & Small Phytoplankton Carbon Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFeSurfaceFluxRemoved]{spFeSurfaceFluxRemoved} & Small Phytoplankton Iron Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPSurfaceFluxRemoved]{spPSurfaceFluxRemoved} & Small Phytoplankton Phosphorus Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3SurfaceFluxRemoved]{spCaCO3SurfaceFluxRemoved} & Small Phytoplankton Calcium Carbonate Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlSurfaceFluxRemoved]{diatChlSurfaceFluxRemoved} & Diatom Chlorophyll Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCSurfaceFluxRemoved]{diatCSurfaceFluxRemoved} & Diatom Carbon Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFeSurfaceFluxRemoved]{diatFeSurfaceFluxRemoved} & Diatom Iron Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPSurfaceFluxRemoved]{diatPSurfaceFluxRemoved} & Diatom Phosphorus Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiSurfaceFluxRemoved]{diatSiSurfaceFluxRemoved} & Diatom Silicate Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlSurfaceFluxRemoved]{diazChlSurfaceFluxRemoved} & Diazotroph Chlorophyll Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCSurfaceFluxRemoved]{diazCSurfaceFluxRemoved} & Diazotroph Carbon Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFeSurfaceFluxRemoved]{diazFeSurfaceFluxRemoved} & Diazotroph Iron Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazPSurfaceFluxRemoved]{diazPSurfaceFluxRemoved} & Diazotroph Phosphorus Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_PH_PREV_3D]{PH\_PREV\_3D} & pH (3D) from previous timestep \\
    \hline
    \hyperref[subsec:var_sec_forcing_PH_PREV_ALT_CO2_3D]{PH\_PREV\_ALT\_CO2\_3D} & pH (3D) of alternate CO2 from previous timestep \\
    \hline
    \hyperref[subsec:var_sec_forcing_FESEDFLUX]{FESEDFLUX} & Sedimentary Fe Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_dust_FLUX_IN]{dust\_FLUX\_IN} & Surface Dust Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_IRON_FLUX_IN]{IRON\_FLUX\_IN} & Surface Fe Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_PAR_surface]{PAR\_surface} & Photosynthetically Available Radiation at Ocean Surface \\
    \hline
    \hyperref[subsec:var_sec_forcing_windSpeedSquared10m]{windSpeedSquared10m} & Wind Speed at 10m Squared \\
    \hline
    \hyperref[subsec:var_sec_forcing_atmosphericCO2]{atmosphericCO2} & Atmospheric CO2 Concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_atmosphericCO2_ALT_CO2]{atmosphericCO2\_ALT\_CO2} & Atmospheric CO2 Concentration for Alternate CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_PH_PREV]{PH\_PREV} & pH (2D) from previous timestep \\
    \hline
    \hyperref[subsec:var_sec_forcing_PH_PREV_ALT_CO2]{PH\_PREV\_ALT\_CO2} & pH (2D) of alternate CO2 from previous timestep \\
    \hline
    \hyperref[subsec:var_sec_forcing_depositionFluxNO3]{depositionFluxNO3} & Atmospheric Deposition of NO3 \\
    \hline
    \hyperref[subsec:var_sec_forcing_depositionFluxNH4]{depositionFluxNH4} & Atmospheric Deposition of NH4 \\
    \hline
    \hyperref[subsec:var_sec_forcing_pocToSed]{pocToSed} & Flux of POC into bottom sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverFluxNO3]{riverFluxNO3} & River Runoff Flux of NO3 \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverFluxPO4]{riverFluxPO4} & River Runoff Flux of PO4 \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverFluxSiO3]{riverFluxSiO3} & River Runoff Flux of SiO3 \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverFluxFe]{riverFluxFe} & River Runoff Flux of Fe \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverFluxDOC]{riverFluxDOC} & River Runoff Flux of DOC \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverFluxDON]{riverFluxDON} & River Runoff Flux of DON \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverFluxDOP]{riverFluxDOP} & River Runoff Flux of DOP \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverFluxDIC]{riverFluxDIC} & River Runoff Flux of DIC \\
    \hline
    \hyperref[subsec:var_sec_forcing_riverFluxALK]{riverFluxALK} & River Runoff Flux of ALK \\
    \hline
    \hyperref[subsec:var_sec_forcing_CO2_gas_flux]{CO2\_gas\_flux} & CO2 Gas Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_CO2_alt_gas_flux]{CO2\_alt\_gas\_flux} & CO2 Gas Flux for Alternate CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgCO2_gas_flux]{avgCO2\_gas\_flux} & CO2 Gas Flux averaged over a coupling interval \\
    \hline
    \hyperref[subsec:var_sec_forcing_total_Chl]{total\_Chl} & Total depth-integrated chlorophyll \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfacePhytoC]{avgOceanSurfacePhytoC} & Ocean Surface phytoplankton carbon concentration: (1,2,3) corresponds to (diat,sp,phaeo) \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceDIC]{avgOceanSurfaceDIC} & Ocean Surface DIC concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceDOCSemiLabile]{avgOceanSurfaceDOCSemiLabile} & Total Ocean Surface DOC semi-labile concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceNO3]{avgOceanSurfaceNO3} & Ocean Surface NO3 concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceSiO3]{avgOceanSurfaceSiO3} & Ocean Surface SiO3 concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceNH4]{avgOceanSurfaceNH4} & Ocean Surface NH4 concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceDOCr]{avgOceanSurfaceDOCr} & Ocean Surface DOCr (Humics) concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceFeParticulate]{avgOceanSurfaceFeParticulate} & Ocean Surface particulate Fe concentration (set to zero) \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceFeDissolved]{avgOceanSurfaceFeDissolved} & Ocean Surface dissolved bioavailable Fe concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxPhytoC]{iceFluxPhytoC} & Surface phytoplankton carbon flux from sea ice: (1,2,3) corresponds to (diat,sp,phaeo) \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxDIC]{iceFluxDIC} & Surface DIC flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxNO3]{iceFluxNO3} & Surface NO3 flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxSiO3]{iceFluxSiO3} & Surface SiO3 flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxNH4]{iceFluxNH4} & Surface NH4 flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxDOCr]{iceFluxDOCr} & Surface DOCr (Humics) flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxFeParticulate]{iceFluxFeParticulate} & Surface particulate Fe flux from sea ice (set to zero) \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxFeDissolved]{iceFluxFeDissolved} & Surface dissolved bioavailable Fe flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxDust]{iceFluxDust} & Surface dust flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxDOC]{iceFluxDOC} & Surface Organics flux from sea ice: (1,2,3)=>(polysaccharides,lipids,proteins) \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxDON]{iceFluxDON} & Surface Organic Proteins flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoC_TOT_zint]{ecosys\_diag\_photoC\_TOT\_zint} & Total C Fixation Vertical Integral \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoC_NO3_TOT_zint]{ecosys\_diag\_photoC\_NO3\_\-TOT\_zint} & Total C Fixation from NO3 Vertical Integral \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_O2_ZMIN]{ecosys\_diag\_O2\_ZMIN} & Vertical Minimum of O2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_O2_ZMIN_DEPTH]{ecosys\_diag\_O2\_ZMIN\_\-DEPTH} & Depth of Vertical Minimum of O2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Chl_TOT_zint_100m]{ecosys\_diag\_Chl\_TOT\_zint\_\-100m} & Vertical Integral of Total Chlorophyll in Top 100m \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Jint_Ctot]{ecosys\_diag\_Jint\_Ctot} & Vertical Integral of Conservative Subterms of Source Sink Term for Ctot \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Jint_Ntot]{ecosys\_diag\_Jint\_Ntot} & Vertical Integral of Conservative Subterms of Source Sink Term for Ntot \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Jint_Ptot]{ecosys\_diag\_Jint\_Ptot} & Vertical Integral of Conservative Subterms of Source Sink Term for Ptot \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Jint_Sitot]{ecosys\_diag\_Jint\_Sitot} & Vertical Integral of Conservative Subterms of Source Sink Term for Sitot \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Jint_Fetot]{ecosys\_diag\_Jint\_Fetot} & Vertical Integral of Conservative Subterms of Source Sink Term for Fetot \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoC_zint]{ecosys\_diag\_photoC\_zint} & C Fixation Vertical Integral for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoC_NO3_zint]{ecosys\_diag\_photoC\_NO3\_zint} & C Fixation from NO3 Vertical Integral for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_PAR_avg]{ecosys\_diag\_PAR\_avg} & PAR Average over Model Cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POC_FLUX_IN]{ecosys\_diag\_POC\_FLUX\_IN} & POC Flux into Cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POP_FLUX_IN]{ecosys\_diag\_POP\_FLUX\_IN} & POP Flux into Cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CaCO3_FLUX_IN]{ecosys\_diag\_CaCO3\_FLUX\_IN} & CaCO3 Flux into Cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CaCO3_ALT_CO2_FLUX_IN]{ecosys\_diag\_CaCO3\_ALT\_\-CO2\_FLUX\_IN} & Alt CO2 CaCO3 Flux into Cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_graze_auto_TOT]{ecosys\_diag\_graze\_auto\_TOT} & Total Autotroph Grazing \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_zoo_loss]{ecosys\_diag\_zoo\_loss} & Zooplankton Loss \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_zoo_loss_poc]{ecosys\_diag\_zoo\_loss\_poc} & Zooplankton Loss to particles \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_zoo_loss_doc]{ecosys\_diag\_zoo\_loss\_doc} & Zooplankton Loss to DOC \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_graze_zoo]{ecosys\_diag\_graze\_zoo} & Zooplankton Grazing \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_graze_zoo_poc]{ecosys\_diag\_graze\_zoo\_poc} & Zooplankton Grazing of particles \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_graze_zoo_doc]{ecosys\_diag\_graze\_zoo\_doc} & Zooplankton Grazing of DOC \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_graze_zoo_zoo]{ecosys\_diag\_graze\_zoo\_zoo} & Zooplankton Grazing of ZooC \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_x_graze_zoo]{ecosys\_diag\_x\_graze\_zoo} & Zooplankton Grazing Gain of ZooC \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoC_TOT]{ecosys\_diag\_photoC\_TOT} & Total C Fixation Vertical Integral \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoC_NO3_TOT]{ecosys\_diag\_photoC\_NO3\_\-TOT} & Total C Fixation from NO3 Vertical Integral \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_NITRIF]{ecosys\_diag\_NITRIF} & Nitrification \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DENITRIF]{ecosys\_diag\_DENITRIF} & Denitrification \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_calcToSed]{ecosys\_diag\_calcToSed} & CaCO3 Flux to Sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_calcToSed_ALT_CO2]{ecosys\_diag\_calcToSed\_ALT\_\-CO2} & CaCO3 Flux to Sediments for Alternate CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_pocToSed]{ecosys\_diag\_pocToSed} & POC Flux to Sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_pfeToSed]{ecosys\_diag\_pfeToSed} & Fe Flux to Sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_SedDenitrif]{ecosys\_diag\_SedDenitrif} & Nitrogen Loss in Sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_tot_Nfix]{ecosys\_diag\_tot\_Nfix} & Total N Fixation \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_O2_PRODUCTION]{ecosys\_diag\_O2\_\-PRODUCTION} & O2 Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_O2_CONSUMPTION]{ecosys\_diag\_O2\_\-CONSUMPTION} & O2 Consumption \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_AOU]{ecosys\_diag\_AOU} & Apparent O2 Utilization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_pH_3D]{ecosys\_diag\_pH\_3D} & pH \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POC_PROD]{ecosys\_diag\_POC\_PROD} & POC Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POC_REMIN_DOCr]{ecosys\_diag\_POC\_REMIN\_\-DOCr} & POC Remineralization to DOCr \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POC_REMIN_DIC]{ecosys\_diag\_POC\_REMIN\_\-DIC} & POC Remineralization to DIC \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POC_ACCUM]{ecosys\_diag\_POC\_ACCUM} & POC Accumulation \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POP_FLUX_IN]{ecosys\_diag\_POP\_FLUX\_IN} & POP Flux into cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POP_PROD]{ecosys\_diag\_POP\_PROD} & POP Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POP_REMIN_DOPr]{ecosys\_diag\_POP\_REMIN\_\-DOPr} & POP Remineralization to DOPr \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_POP_REMIN_PO4]{ecosys\_diag\_POP\_REMIN\_\-PO4} & POP Remineralization to PO4 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_PON_REMIN_DONr]{ecosys\_diag\_PON\_REMIN\_\-DONr} & PON Remineralization to DONr \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_PON_REMIN_NH4]{ecosys\_diag\_PON\_REMIN\_\-NH4} & PON Remineralization to NH4 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Qp]{ecosys\_diag\_Qp} & P/C Ratio \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_N_lim_surf]{ecosys\_diag\_N\_lim\_surf} & N Surface Limitation for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_P_lim_surf]{ecosys\_diag\_P\_lim\_surf} & P Surface Limitation for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Fe_lim_surf]{ecosys\_diag\_Fe\_lim\_surf} & Fe Surface Limitation for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_SiO3_lim_surf]{ecosys\_diag\_SiO3\_lim\_surf} & SiO3 Surface Limitation for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_light_lim_surf]{ecosys\_diag\_light\_lim\_surf} & Light Surface Limitation for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoC]{ecosys\_diag\_photoC} & C Fixation for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoC_NO3]{ecosys\_diag\_photoC\_NO3} & C Fixation from NO3 for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoFe]{ecosys\_diag\_photoFe} & Fe Uptake \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoNO3]{ecosys\_diag\_photoNO3} & NO3 Uptake \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_photoNH4]{ecosys\_diag\_photoNH4} & NH4 Uptake \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DOP_uptake]{ecosys\_diag\_DOP\_uptake} & DOP Uptake \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_PO4_uptake]{ecosys\_diag\_PO4\_uptake} & PO4 Uptake \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_auto_graze]{ecosys\_diag\_auto\_graze} & Grazing for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_auto_graze_poc]{ecosys\_diag\_auto\_graze\_poc} & Grazing loss to poc for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_auto_graze_doc]{ecosys\_diag\_auto\_graze\_doc} & Grazing loss to doc for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_auto_graze_zoo]{ecosys\_diag\_auto\_graze\_zoo} & Grazing by zoo plankton for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_auto_loss]{ecosys\_diag\_auto\_loss} & Loss for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_auto_loss_poc]{ecosys\_diag\_auto\_loss\_poc} & Loss to POC for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_auto_loss_doc]{ecosys\_diag\_auto\_loss\_doc} & Loss to DOC for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_auto_agg]{ecosys\_diag\_auto\_agg} & Aggregate for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Nfix]{ecosys\_diag\_Nfix} & N Fixation for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_pistonVel_O2]{ecosys\_diag\_pistonVel\_O2} & Piston Velocity for O2 Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_pistonVel_CO2]{ecosys\_diag\_pistonVel\_CO2} & Piston Velocity for CO2 Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Schmidt_O2]{ecosys\_diag\_Schmidt\_O2} & O2 Schmidt Number \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Schmidt_CO2]{ecosys\_diag\_Schmidt\_CO2} & CO2 Schmidt Number \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_O2_saturation]{ecosys\_diag\_O2\_saturation} & Surface O2 Saturation \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_xkw]{ecosys\_diag\_xkw} & Schmidt Number Independent Piston Velocity Factor \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_u10sqr]{ecosys\_diag\_u10sqr} & 10 meter wind squared seen by ecosys \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_ifrac]{ecosys\_diag\_ifrac} & Ice Fraction seen by ecosys \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_atmPressure]{ecosys\_diag\_atmPressure} & Atmospheric Pressure Seen by ecosys \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CO2star]{ecosys\_diag\_CO2star} & CO2 Star \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_dCO2star]{ecosys\_diag\_dCO2star} & d CO2 Star \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_pCO2surface]{ecosys\_diag\_pCO2surface} & Surface pCO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_dpCO2]{ecosys\_diag\_dpCO2} & d Surface pCO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CO2star_ALT_CO2]{ecosys\_diag\_CO2star\_ALT\_\-CO2} & CO2 Star for Alternate CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_dCO2star_ALT_CO2]{ecosys\_diag\_dCO2star\_ALT\_\-CO2} & d CO2 Star for Alternate CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_pCO2surface_ALT_CO2]{ecosys\_diag\_pCO2surface\_\-ALT\_CO2} & Surface pCO2 for Alternate CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_dpCO2_ALT_CO2]{ecosys\_diag\_dpCO2\_ALT\_CO2} & d Surface pCO2 for Alternate CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_tot_bSi_form]{ecosys\_diag\_tot\_bSi\_form} & Si Uptake \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_SiO2_FLUX_IN]{ecosys\_diag\_SiO2\_FLUX\_IN} & SiO2 Flux into Cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_SiO2_PROD]{ecosys\_diag\_SiO2\_PROD} & SiO2 Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_SiO2_REMIN]{ecosys\_diag\_SiO2\_REMIN} & SiO2 Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_dust_FLUX_IN]{ecosys\_diag\_dust\_FLUX\_IN} & Dust Flux into Cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_dust_REMIN]{ecosys\_diag\_dust\_REMIN} & Dust Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_P_iron_FLUX_IN]{ecosys\_diag\_P\_iron\_FLUX\_\-IN} & P\_iron Flux into Cell \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_P_iron_PROD]{ecosys\_diag\_P\_iron\_PROD} & P\_iron Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_P_iron_REMIN]{ecosys\_diag\_P\_iron\_REMIN} & P\_iron Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DOC_prod]{ecosys\_diag\_DOC\_prod} & DOC Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DOC_remin]{ecosys\_diag\_DOC\_remin} & DOC Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DOCr_remin]{ecosys\_diag\_DOCr\_remin} & DOCr Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DON_prod]{ecosys\_diag\_DON\_prod} & DON Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DON_remin]{ecosys\_diag\_DON\_remin} & DON Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DOP_prod]{ecosys\_diag\_DOP\_prod} & DOP Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DOP_remin]{ecosys\_diag\_DOP\_remin} & DOP Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Fe_scavenge]{ecosys\_diag\_Fe\_scavenge} & Iron Scavenging \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Fe_scavenge_rate]{ecosys\_diag\_Fe\_scavenge\_rate} & Iron Scavenging Rate \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Lig_prod]{ecosys\_diag\_Lig\_prod} & Ligand Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Lig_loss]{ecosys\_diag\_Lig\_loss} & Ligand Loss \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Lig_scavenge]{ecosys\_diag\_Lig\_scavenge} & Ligand Scavenging \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Fefree]{ecosys\_diag\_Fefree} & Free Iron \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Lig_photochem]{ecosys\_diag\_Lig\_photochem} & Ligand Photochemistry \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_Lig_deg]{ecosys\_diag\_Lig\_deg} & Ligand Degradation \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DONr_remin]{ecosys\_diag\_DONr\_remin} & DONr Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_DOPr_remin]{ecosys\_diag\_DOPr\_remin} & DOPr Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_ponToSed]{ecosys\_diag\_ponToSed} & N Burial Flux to Sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_popToSed]{ecosys\_diag\_popToSed} & P Flux to Sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_bsiToSed]{ecosys\_diag\_bsiToSed} & Biogenic Si Flux to Sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_dustToSed]{ecosys\_diag\_dustToSed} & Dust Flux to Sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_OtherRemin]{ecosys\_diag\_OtherRemin} & Non-Oxic, Non-Dentr Remineralization in Sediments \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_bSi_form]{ecosys\_diag\_bSi\_form} & Si Uptake for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_tot_CaCO3_form_zint]{ecosys\_diag\_tot\_CaCO3\_form\_\-zint} & Total CaCO3 Formation Vertical Integral \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_zsatcalc]{ecosys\_diag\_zsatcalc} & Calcite Saturation Depth \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_zsatarag]{ecosys\_diag\_zsatarag} & Aragonite Saturation Depth \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CaCO3_form_zint]{ecosys\_diag\_CaCO3\_form\_zint} & CaCO3 Formation Vertical Integral for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CaCO3_PROD]{ecosys\_diag\_CaCO3\_PROD} & CaCO3 Production \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CaCO3_REMIN]{ecosys\_diag\_CaCO3\_REMIN} & CaCO3 Remineralization \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CaCO3_ALT_CO2_PROD]{ecosys\_diag\_CaCO3\_ALT\_\-CO2\_PROD} & CaCO3 Production for Alternate CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CaCO3_ALT_CO2_REMIN]{ecosys\_diag\_CaCO3\_ALT\_\-CO2\_REMIN} & CaCO3 Remineralization for Alternate CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_tot_CaCO3_form]{ecosys\_diag\_tot\_CaCO3\_form} & Total CaCO3 Formation \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CO3]{ecosys\_diag\_CO3} & Carbonate Ion Concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_HCO3]{ecosys\_diag\_HCO3} & Bicarbonate Ion Concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_H2CO3]{ecosys\_diag\_H2CO3} & Carbonic Acid Concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CO3_ALT_CO2]{ecosys\_diag\_CO3\_ALT\_CO2} & Carbonate Ion Concentration, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_HCO3_ALT_CO2]{ecosys\_diag\_HCO3\_ALT\_CO2} & Bicarbonate Ion Concentration, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_H2CO3_ALT_CO2]{ecosys\_diag\_H2CO3\_ALT\_\-CO2} & Carbonic Acid Concentration, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_pH_3D_ALT_CO2]{ecosys\_diag\_pH\_3D\_ALT\_\-CO2} & pH, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_co3_sat_calc]{ecosys\_diag\_co3\_sat\_calc} & CO3 concentration at calcite saturation \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_co3_sat_arag]{ecosys\_diag\_co3\_sat\_arag} & CO3 concentration at aragonite saturation \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_CaCO3_form]{ecosys\_diag\_CaCO3\_form} & CaCO3 Formation for sp, diat, diaz, phaeo \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_PO4_RESTORE]{ecosys\_diag\_PO4\_RESTORE} & PO4 Restoring \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_NO3_RESTORE]{ecosys\_diag\_NO3\_RESTORE} & NO3 Restoring \\
    \hline
    \hyperref[subsec:var_sec_forcing_ecosys_diag_SiO3_RESTORE]{ecosys\_diag\_SiO3\_RESTORE} & SiO3 Restoring \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4PistonVelocity]{PO4PistonVelocity} & A non-negative field controlling the rate at which PO4 is restored to PO4SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3PistonVelocity]{NO3PistonVelocity} & A non-negative field controlling the rate at which NO3 is restored to NO3SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3PistonVelocity]{SiO3PistonVelocity} & A non-negative field controlling the rate at which SiO3 is restored to SiO3SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4PistonVelocity]{NH4PistonVelocity} & A non-negative field controlling the rate at which NH4 is restored to NH4SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_FePistonVelocity]{FePistonVelocity} & A non-negative field controlling the rate at which Fe is restored to FeSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigPistonVelocity]{LigPistonVelocity} & A non-negative field controlling the rate at which Lig is restored to LigSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2PistonVelocity]{O2PistonVelocity} & A non-negative field controlling the rate at which O2 is restored to O2SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICPistonVelocity]{DICPistonVelocity} & A non-negative field controlling the rate at which DIC is restored to DICSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2PistonVelocity]{DIC\_ALT\_CO2PistonVelocity} & A non-negative field controlling the rate at which DIC\_ALT\_CO2 is restored to DIC\_ALT\_CO2SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKPistonVelocity]{ALKPistonVelocity} & A non-negative field controlling the rate at which ALK is restored to ALKSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2PistonVelocity]{ALK\_ALT\_CO2PistonVelocity} & A non-negative field controlling the rate at which ALK is restored to ALKSurfaceRestoringValue, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCPistonVelocity]{DOCPistonVelocity} & A non-negative field controlling the rate at which DOC is restored to DOCSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONPistonVelocity]{DONPistonVelocity} & A non-negative field controlling the rate at which DON is restored to DONSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPPistonVelocity]{DOPPistonVelocity} & A non-negative field controlling the rate at which DOP is restored to DOPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrPistonVelocity]{DOPrPistonVelocity} & A non-negative field controlling the rate at which DOPr is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrPistonVelocity]{DONrPistonVelocity} & A non-negative field controlling the rate at which DONr is restored to DONrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrPistonVelocity]{DOCrPistonVelocity} & A non-negative field controlling the rate at which DOCr is restored to DOCrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCPistonVelocity]{zooCPistonVelocity} & A non-negative field controlling the rate at which zooC is restored to zooCSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlPistonVelocity]{spChlPistonVelocity} & A non-negative field controlling the rate at which spChl is restored to spChlSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCPistonVelocity]{spCPistonVelocity} & A non-negative field controlling the rate at which spC is restored to spCSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFePistonVelocity]{spFePistonVelocity} & A non-negative field controlling the rate at which spFe is restored to spFeSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPPistonVelocity]{spPPistonVelocity} & A non-negative field controlling the rate at which spP is restored to spPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3PistonVelocity]{spCaCO3PistonVelocity} & A non-negative field controlling the rate at which spCaCO3 is restored to spCaCO3SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlPistonVelocity]{diatChlPistonVelocity} & A non-negative field controlling the rate at which diatChl is restored to diatChlSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCPistonVelocity]{diatCPistonVelocity} & A non-negative field controlling the rate at which diatC is restored to diatCSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFePistonVelocity]{diatFePistonVelocity} & A non-negative field controlling the rate at which diatFe is restored to diatFeSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPPistonVelocity]{diatPPistonVelocity} & A non-negative field controlling the rate at which diatP is restored to diatPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiPistonVelocity]{diatSiPistonVelocity} & A non-negative field controlling the rate at which diatSi is restored to diatSiSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlPistonVelocity]{diazChlPistonVelocity} & A non-negative field controlling the rate at which diazChl is restored to diazChlSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCPistonVelocity]{diazCPistonVelocity} & A non-negative field controlling the rate at which diazC is restored to diazCSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFePistonVelocity]{diazFePistonVelocity} & A non-negative field controlling the rate at which diazFe is restored to diazFeSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazPPistonVelocity]{diazPPistonVelocity} & A non-negative field controlling the rate at which diazP is restored to diazPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4SurfaceRestoringValue]{PO4SurfaceRestoringValue} & A non-negative field controlling the rate at which PO4 is restored to PO4SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3SurfaceRestoringValue]{NO3SurfaceRestoringValue} & A non-negative field controlling the rate at which NO3 is restored to NO3SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3SurfaceRestoringValue]{SiO3SurfaceRestoringValue} & A non-negative field controlling the rate at which SiO3 is restored to SiO3SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4SurfaceRestoringValue]{NH4SurfaceRestoringValue} & A non-negative field controlling the rate at which NH4 is restored to NH4SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_FeSurfaceRestoringValue]{FeSurfaceRestoringValue} & A non-negative field controlling the rate at which Fe is restored to FeSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigSurfaceRestoringValue]{LigSurfaceRestoringValue} & A non-negative field controlling the rate at which Lig is restored to LigSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2SurfaceRestoringValue]{O2SurfaceRestoringValue} & A non-negative field controlling the rate at which O2 is restored to O2SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICSurfaceRestoringValue]{DICSurfaceRestoringValue} & A non-negative field controlling the rate at which DIC is restored to DICSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2SurfaceRestoringValue]{DIC\_ALT\_CO2SurfaceRestoring\-Value} & A non-negative field controlling the rate at which DIC\_ALT\_CO2 is restored to DIC\_ALT\_CO2SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKSurfaceRestoringValue]{ALKSurfaceRestoringValue} & A non-negative field controlling the rate at which ALK is restored to ALKSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2SurfaceRestoringValue]{ALK\_ALT\_CO2Surface\-RestoringValue} & A non-negative field controlling the rate at which ALK is restored to ALKSurfaceRestoringValue, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCSurfaceRestoringValue]{DOCSurfaceRestoringValue} & A non-negative field controlling the rate at which DOC is restored to DOCSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONSurfaceRestoringValue]{DONSurfaceRestoringValue} & A non-negative field controlling the rate at which DON is restored to DONSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPSurfaceRestoringValue]{DOPSurfaceRestoringValue} & A non-negative field controlling the rate at which DOP is restored to DOPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrSurfaceRestoringValue]{DOPrSurfaceRestoringValue} & A non-negative field controlling the rate at which DOPr is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrSurfaceRestoringValue]{DONrSurfaceRestoringValue} & A non-negative field controlling the rate at which DONr is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrSurfaceRestoringValue]{DOCrSurfaceRestoringValue} & A non-negative field controlling the rate at which DOCr is restored to DOCrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlSurfaceRestoringValue]{spChlSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCSurfaceRestoringValue]{spCSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFeSurfaceRestoringValue]{spFeSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPSurfaceRestoringValue]{spPSurfaceRestoringValue} & A non-negative field controlling the rate at which spP is restored to spPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3SurfaceRestoringValue]{spCaCO3SurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlSurfaceRestoringValue]{diatChlSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCSurfaceRestoringValue]{diatCSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFeSurfaceRestoringValue]{diatFeSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPSurfaceRestoringValue]{diatPSurfaceRestoringValue} & A non-negative field controlling the rate at which diatP is restored to diatPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiSurfaceRestoringValue]{diatSiSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlSurfaceRestoringValue]{diazChlSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCSurfaceRestoringValue]{diazCSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFeSurfaceRestoringValue]{diazFeSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazPSurfaceRestoringValue]{diazPSurfaceRestoringValue} & A non-negative field controlling the rate at which diazP is restored to diazPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCSurfaceRestoringValue]{zooCSurfaceRestoringValue} & A non-negative field controlling the rate at which zooC is restored to DOPrSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4InteriorRestoringRate]{PO4InteriorRestoringRate} & A non-negative field controlling the rate at which PO4 is restored to PO4InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3InteriorRestoringRate]{NO3InteriorRestoringRate} & A non-negative field controlling the rate at which NO3 is restored to NO3InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3InteriorRestoringRate]{SiO3InteriorRestoringRate} & A non-negative field controlling the rate at which SiO3 is restored to SiO3InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4InteriorRestoringRate]{NH4InteriorRestoringRate} & A non-negative field controlling the rate at which NH4 is restored to NH4InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_FeInteriorRestoringRate]{FeInteriorRestoringRate} & A non-negative field controlling the rate at which Fe is restored to FeInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigInteriorRestoringRate]{LigInteriorRestoringRate} & A non-negative field controlling the rate at which Lig is restored to LigInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2InteriorRestoringRate]{O2InteriorRestoringRate} & A non-negative field controlling the rate at which O2 is restored to O2InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICInteriorRestoringRate]{DICInteriorRestoringRate} & A non-negative field controlling the rate at which DIC is restored to DICInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2InteriorRestoringRate]{DIC\_ALT\_CO2Interior\-RestoringRate} & A non-negative field controlling the rate at which DIC\_ALT\_CO2 is restored to DIC\_ALT\_CO2InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKInteriorRestoringRate]{ALKInteriorRestoringRate} & A non-negative field controlling the rate at which ALK is restored to ALKInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2InteriorRestoringRate]{ALK\_ALT\_CO2Interior\-RestoringRate} & A non-negative field controlling the rate at which ALK is restored to ALKInteriorRestoringValue, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCInteriorRestoringRate]{DOCInteriorRestoringRate} & A non-negative field controlling the rate at which DOC is restored to DOCInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONInteriorRestoringRate]{DONInteriorRestoringRate} & A non-negative field controlling the rate at which DON is restored to DONInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPInteriorRestoringRate]{DOPInteriorRestoringRate} & A non-negative field controlling the rate at which DOP is restored to DOPInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrInteriorRestoringRate]{DOPrInteriorRestoringRate} & A non-negative field controlling the rate at which DOPr is restored to DOPrInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrInteriorRestoringRate]{DONrInteriorRestoringRate} & A non-negative field controlling the rate at which DONr is restored to DONrInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrInteriorRestoringRate]{DOCrInteriorRestoringRate} & A non-negative field controlling the rate at which DOCr is restored to DOCrInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCInteriorRestoringRate]{zooCInteriorRestoringRate} & A non-negative field controlling the rate at which zooC is restored to zooCInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlInteriorRestoringRate]{spChlInteriorRestoringRate} & A non-negative field controlling the rate at which spChl is restored to spChlInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCInteriorRestoringRate]{spCInteriorRestoringRate} & A non-negative field controlling the rate at which spC is restored to spCInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFeInteriorRestoringRate]{spFeInteriorRestoringRate} & A non-negative field controlling the rate at which spFe is restored to spFeInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPInteriorRestoringRate]{spPInteriorRestoringRate} & A non-negative field controlling the rate at which spP is restored to spPInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3InteriorRestoringRate]{spCaCO3InteriorRestoringRate} & A non-negative field controlling the rate at which spCaCO3 is restored to spCaCO3InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlInteriorRestoringRate]{diatChlInteriorRestoringRate} & A non-negative field controlling the rate at which diatChl is restored to diatChlInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCInteriorRestoringRate]{diatCInteriorRestoringRate} & A non-negative field controlling the rate at which diatC is restored to diatCInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFeInteriorRestoringRate]{diatFeInteriorRestoringRate} & A non-negative field controlling the rate at which diatFe is restored to diatFeInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPInteriorRestoringRate]{diatPInteriorRestoringRate} & A non-negative field controlling the rate at which diatP is restored to diatPInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiInteriorRestoringRate]{diatSiInteriorRestoringRate} & A non-negative field controlling the rate at which diatSi is restored to diatSiInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlInteriorRestoringRate]{diazChlInteriorRestoringRate} & A non-negative field controlling the rate at which diazChl is restored to diazChlInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCInteriorRestoringRate]{diazCInteriorRestoringRate} & A non-negative field controlling the rate at which diazC is restored to diazCInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFeInteriorRestoringRate]{diazFeInteriorRestoringRate} & A non-negative field controlling the rate at which diazFe is restored to diazFeInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazPInteriorRestoringRate]{diazPInteriorRestoringRate} & A non-negative field controlling the rate at which diazP is restored to diazPInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4InteriorRestoringValue]{PO4InteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by PO4InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3InteriorRestoringValue]{NO3InteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by NO3InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3InteriorRestoringValue]{SiO3InteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by SiO3InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4InteriorRestoringValue]{NH4InteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by NH4InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_FeInteriorRestoringValue]{FeInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by FeInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigInteriorRestoringValue]{LigInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by LigInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2InteriorRestoringValue]{O2InteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by O2InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICInteriorRestoringValue]{DICInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by DICInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2InteriorRestoringValue]{DIC\_ALT\_CO2Interior\-RestoringValue} & Tracer is restored toward this field at a rate controlled by DIC\_ALT\_CO2InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKInteriorRestoringValue]{ALKInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by ALKInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2InteriorRestoringValue]{ALK\_ALT\_CO2Interior\-RestoringValue} & Tracer is restored toward this field at a rate controlled by ALKInteriorRestoringRate, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCInteriorRestoringValue]{DOCInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by DOCInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONInteriorRestoringValue]{DONInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by DONInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPInteriorRestoringValue]{DOPInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by DOPInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrInteriorRestoringValue]{DOPrInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by DOPrInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrInteriorRestoringValue]{DONrInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by DONrInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrInteriorRestoringValue]{DOCrInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by DOCrInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCInteriorRestoringValue]{zooCInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by zooCInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlInteriorRestoringValue]{spChlInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by spChlInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCInteriorRestoringValue]{spCInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by spCInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFeInteriorRestoringValue]{spFeInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by spFeInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPInteriorRestoringValue]{spPInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by spPInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3InteriorRestoringValue]{spCaCO3InteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by spCaCO3InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlInteriorRestoringValue]{diatChlInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by diatChlInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCInteriorRestoringValue]{diatCInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by diatCInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFeInteriorRestoringValue]{diatFeInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by diatFeInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPInteriorRestoringValue]{diatPInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by diatPInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiInteriorRestoringValue]{diatSiInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by diatSiInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlInteriorRestoringValue]{diazChlInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by diazChlInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCInteriorRestoringValue]{diazCInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by diazCInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFeInteriorRestoringValue]{diazFeInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by diazFeInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazPInteriorRestoringValue]{diazPInteriorRestoringValue} & diazP is restored toward this field at a rate controlled by diazPInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4ExponentialDecayRate]{PO4ExponentialDecayRate} & A non-negative field controlling the exponential decay of PO4 \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3ExponentialDecayRate]{NO3ExponentialDecayRate} & A non-negative field controlling the exponential decay of NO3 \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3ExponentialDecayRate]{SiO3ExponentialDecayRate} & A non-negative field controlling the exponential decay of SiO3 \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4ExponentialDecayRate]{NH4ExponentialDecayRate} & A non-negative field controlling the exponential decay of NH4 \\
    \hline
    \hyperref[subsec:var_sec_forcing_FeExponentialDecayRate]{FeExponentialDecayRate} & A non-negative field controlling the exponential decay of Fe \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigExponentialDecayRate]{LigExponentialDecayRate} & A non-negative field controlling the exponential decay of Lig \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2ExponentialDecayRate]{O2ExponentialDecayRate} & A non-negative field controlling the exponential decay of O2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICExponentialDecayRate]{DICExponentialDecayRate} & A non-negative field controlling the exponential decay of DIC \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2ExponentialDecayRate]{DIC\_ALT\_CO2Exponential\-DecayRate} & A non-negative field controlling the exponential decay of DIC\_ALT\_CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKExponentialDecayRate]{ALKExponentialDecayRate} & A non-negative field controlling the exponential decay of ALK \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2ExponentialDecayRate]{ALK\_ALT\_CO2Exponential\-DecayRate} & A non-negative field controlling the exponential decay of ALK, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCExponentialDecayRate]{DOCExponentialDecayRate} & A non-negative field controlling the exponential decay of DOC \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONExponentialDecayRate]{DONExponentialDecayRate} & A non-negative field controlling the exponential decay of DON \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPExponentialDecayRate]{DOPExponentialDecayRate} & A non-negative field controlling the exponential decay of DOP \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrExponentialDecayRate]{DOPrExponentialDecayRate} & A non-negative field controlling the exponential decay of DOPr \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrExponentialDecayRate]{DONrExponentialDecayRate} & A non-negative field controlling the exponential decay of DONr \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrExponentialDecayRate]{DOCrExponentialDecayRate} & A non-negative field controlling the exponential decay of DOCr \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCExponentialDecayRate]{zooCExponentialDecayRate} & A non-negative field controlling the exponential decay of zooC \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlExponentialDecayRate]{spChlExponentialDecayRate} & A non-negative field controlling the exponential decay of spChl \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCExponentialDecayRate]{spCExponentialDecayRate} & A non-negative field controlling the exponential decay of spC \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFeExponentialDecayRate]{spFeExponentialDecayRate} & A non-negative field controlling the exponential decay of spFe \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPExponentialDecayRate]{spPExponentialDecayRate} & A non-negative field controlling the exponential decay of spP \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3ExponentialDecayRate]{spCaCO3ExponentialDecayRate} & A non-negative field controlling the exponential decay of spCaCO3 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlExponentialDecayRate]{diatChlExponentialDecayRate} & A non-negative field controlling the exponential decay of diatChl \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCExponentialDecayRate]{diatCExponentialDecayRate} & A non-negative field controlling the exponential decay of diatC \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFeExponentialDecayRate]{diatFeExponentialDecayRate} & A non-negative field controlling the exponential decay of diatFe \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPExponentialDecayRate]{diatPExponentialDecayRate} & A non-negative field controlling the exponential decay of diatP \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiExponentialDecayRate]{diatSiExponentialDecayRate} & A non-negative field controlling the exponential decay of diatSi \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlExponentialDecayRate]{diazChlExponentialDecayRate} & A non-negative field controlling the exponential decay of diazChl \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCExponentialDecayRate]{diazCExponentialDecayRate} & A non-negative field controlling the exponential decay of diazC \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFeExponentialDecayRate]{diazFeExponentialDecayRate} & A non-negative field controlling the exponential decay of diazFe \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4IdealAgeMask]{PO4IdealAgeMask} & In top layer, PO4 is reset to PO4 * PO4IdealAgeMask, valid values of PO4IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3IdealAgeMask]{NO3IdealAgeMask} & In top layer, NO3 is reset to NO3 * NO3IdealAgeMask, valid values of NO3IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3IdealAgeMask]{SiO3IdealAgeMask} & In top layer, SiO3 is reset to SiO3 * SiO3IdealAgeMask, valid values of SiO3IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4IdealAgeMask]{NH4IdealAgeMask} & In top layer, NH4 is reset to NH4 * NH4IdealAgeMask, valid values of NH4IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_FeIdealAgeMask]{FeIdealAgeMask} & In top layer, Fe is reset to Fe * FeIdealAgeMask, valid values of FeIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigIdealAgeMask]{LigIdealAgeMask} & In top layer, Lig is reset to Lig * LigIdealAgeMask, valid values of LigIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2IdealAgeMask]{O2IdealAgeMask} & In top layer, O2 is reset to O2 * O2IdealAgeMask, valid values of O2IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICIdealAgeMask]{DICIdealAgeMask} & In top layer, DIC is reset to DIC * DICIdealAgeMask, valid values of DICIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2IdealAgeMask]{DIC\_ALT\_CO2IdealAgeMask} & In top layer, DIC\_ALT\_CO2 is reset to DIC\_ALT\_CO2 * DIC\_ALT\_CO2IdealAgeMask, valid values of DIC\_ALT\_CO2IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKIdealAgeMask]{ALKIdealAgeMask} & In top layer, ALK is reset to ALK * ALKIdealAgeMask, valid values of ALKIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2IdealAgeMask]{ALK\_ALT\_CO2IdealAgeMask} & In top layer, ALK is reset to ALK * ALKIdealAgeMask, valid values of ALKIdealAgeMask or 0 and 1, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCIdealAgeMask]{DOCIdealAgeMask} & In top layer, DOC is reset to DOC * DOCIdealAgeMask, valid values of DOCIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONIdealAgeMask]{DONIdealAgeMask} & In top layer, DON is reset to DON * DONIdealAgeMask, valid values of DONIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPIdealAgeMask]{DOPIdealAgeMask} & In top layer, DOP is reset to DOP * DOPIdealAgeMask, valid values of DOPIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrIdealAgeMask]{DOPrIdealAgeMask} & In top layer, DOPr is reset to DOPr * DOPrIdealAgeMask, valid values of DOPrIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrIdealAgeMask]{DONrIdealAgeMask} & In top layer, DONr is reset to DONr * DONrIdealAgeMask, valid values of DONrIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrIdealAgeMask]{DOCrIdealAgeMask} & In top layer, DOCr is reset to DOCr * DOCrIdealAgeMask, valid values of DOCrIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCIdealAgeMask]{zooCIdealAgeMask} & In top layer, zooC is reset to zooC * zooCIdealAgeMask, valid values of zooCIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlIdealAgeMask]{spChlIdealAgeMask} & In top layer, spChl is reset to spChl * spChlIdealAgeMask, valid values of spChlIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCIdealAgeMask]{spCIdealAgeMask} & In top layer, spC is reset to spC * spCIdealAgeMask, valid values of spCIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFeIdealAgeMask]{spFeIdealAgeMask} & In top layer, spFe is reset to spFe * spFeIdealAgeMask, valid values of spFeIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPIdealAgeMask]{spPIdealAgeMask} & In top layer, spP is reset to spP * spPIdealAgeMask, valid values of spPIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3IdealAgeMask]{spCaCO3IdealAgeMask} & In top layer, spCaCO3 is reset to spCaCO3 * spCaCO3IdealAgeMask, valid values of spCaCO3IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlIdealAgeMask]{diatChlIdealAgeMask} & In top layer, diatChl is reset to diatChl * diatChlIdealAgeMask, valid values of diatChlIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCIdealAgeMask]{diatCIdealAgeMask} & In top layer, diatC is reset to diatC * diatCIdealAgeMask, valid values of diatCIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFeIdealAgeMask]{diatFeIdealAgeMask} & In top layer, diatFe is reset to diatFe * diatFeIdealAgeMask, valid values of diatFeIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPIdealAgeMask]{diatPIdealAgeMask} & In top layer, diatP is reset to diatP * diatPIdealAgeMask, valid values of diatPIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiIdealAgeMask]{diatSiIdealAgeMask} & In top layer, diatSi is reset to diatSi * diatSiIdealAgeMask, valid values of diatSiIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlIdealAgeMask]{diazChlIdealAgeMask} & In top layer, diazChl is reset to diazChl * diazChlIdealAgeMask, valid values of diazChlIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCIdealAgeMask]{diazCIdealAgeMask} & In top layer, diazC is reset to diazC * diazCIdealAgeMask, valid values of diazCIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFeIdealAgeMask]{diazFeIdealAgeMask} & In top layer, diazFe is reset to diazFe * diazFeIdealAgeMask, valid values of diazFeIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazPIdealAgeMask]{diazPIdealAgeMask} & In top layer, diazP is reset to diazP * diazPIdealAgeMask, valid values of diazPIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_PO4TTDMask]{PO4TTDMask} & In top layer, PO4 is reset to TTDMask, valid values of PO4TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_NO3TTDMask]{NO3TTDMask} & In top layer, NO3 is reset to TTDMask, valid values of NO3TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_SiO3TTDMask]{SiO3TTDMask} & In top layer, SiO3 is reset to TTDMask, valid values of SiO3TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_NH4TTDMask]{NH4TTDMask} & In top layer, NH4 is reset to TTDMask, valid values of NH4TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_FeTTDMask]{FeTTDMask} & In top layer, Fe is reset to TTDMask, valid values of FeTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_LigTTDMask]{LigTTDMask} & In top layer, Lig is reset to TTDMask, valid values of LigTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_O2TTDMask]{O2TTDMask} & In top layer, O2 is reset to TTDMask, valid values of O2TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DICTTDMask]{DICTTDMask} & In top layer, DIC is reset to TTDMask, valid values of DICTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DIC_ALT_CO2TTDMask]{DIC\_ALT\_CO2TTDMask} & In top layer, DIC\_ALT\_CO2 is reset to TTDMask, valid values of DIC\_ALT\_CO2TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALKTTDMask]{ALKTTDMask} & In top layer, ALK is reset to TTDMask, valid values of ALKTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_ALK_ALT_CO2TTDMask]{ALK\_ALT\_CO2TTDMask} & In top layer, ALK is reset to TTDMask, valid values of ALKTTDMask or 0 and 1, Alternative CO2 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCTTDMask]{DOCTTDMask} & In top layer, DOC is reset to TTDMask, valid values of DOCTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONTTDMask]{DONTTDMask} & In top layer, DON is reset to TTDMask, valid values of DONTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPTTDMask]{DOPTTDMask} & In top layer, DOP is reset to TTDMask, valid values of DOPTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOPrTTDMask]{DOPrTTDMask} & In top layer, DOPr is reset to TTDMask, valid values of DOPrTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DONrTTDMask]{DONrTTDMask} & In top layer, DONr is reset to TTDMask, valid values of DONrTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DOCrTTDMask]{DOCrTTDMask} & In top layer, DOCr is reset to TTDMask, valid values of DOCrTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_zooCTTDMask]{zooCTTDMask} & In top layer, zooC is reset to TTDMask, valid values of zooCTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spChlTTDMask]{spChlTTDMask} & In top layer, spChl is reset to TTDMask, valid values of spChlTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCTTDMask]{spCTTDMask} & In top layer, spC is reset to TTDMask, valid values of spCTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spFeTTDMask]{spFeTTDMask} & In top layer, spFe is reset to TTDMask, valid values of spFeTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spPTTDMask]{spPTTDMask} & In top layer, spP is reset to TTDMask, valid values of spPTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_spCaCO3TTDMask]{spCaCO3TTDMask} & In top layer, spCaCO3 is reset to TTDMask, valid values of spCaCO3TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatChlTTDMask]{diatChlTTDMask} & In top layer, diatChl is reset to TTDMask, valid values of diatChlTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatCTTDMask]{diatCTTDMask} & In top layer, diatC is reset to TTDMask, valid values of diatCTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatFeTTDMask]{diatFeTTDMask} & In top layer, diatFe is reset to TTDMask, valid values of diatFeTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatPTTDMask]{diatPTTDMask} & In top layer, diatP is reset to TTDMask, valid values of diatPTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diatSiTTDMask]{diatSiTTDMask} & In top layer, diatSi is reset to TTDMask, valid values of diatSiTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazChlTTDMask]{diazChlTTDMask} & In top layer, diazChl is reset to TTDMask, valid values of diazChlTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazCTTDMask]{diazCTTDMask} & In top layer, diazC is reset to TTDMask, valid values of diazCTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazFeTTDMask]{diazFeTTDMask} & In top layer, diazFe is reset to TTDMask, valid values of diazFeTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_diazPTTDMask]{diazPTTDMask} & In top layer, diazP is reset to TTDMask, valid values of diazPTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSSurfaceFlux]{DMSSurfaceFlux} & Dimethyl Sulfide Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPSurfaceFlux]{DMSPSurfaceFlux} & Dimethyl Sulfoniopropionate Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSSurfaceFluxRunoff]{DMSSurfaceFluxRunoff} & Dimethyl Sulfide Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPSurfaceFluxRunoff]{DMSPSurfaceFluxRunoff} & Dimethyl Sulfoniopropionate Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSSurfaceFluxRemoved]{DMSSurfaceFluxRemoved} & Dimethyl Sulfide Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPSurfaceFluxRemoved]{DMSPSurfaceFluxRemoved} & Dimethyl Sulfoniopropionate Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceDMS]{avgOceanSurfaceDMS} & Ocean Surface DMS concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceDMSP]{avgOceanSurfaceDMSP} & Ocean Surface DMSP concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxDMS]{iceFluxDMS} & Surface DMS flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_iceFluxDMSP]{iceFluxDMSP} & Surface DMSP flux from sea ice \\
    \hline
    \hyperref[subsec:var_sec_forcing_dms_flux_diag_ifrac]{dms\_flux\_diag\_ifrac} & Ice Fraction used in DMS flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_dms_flux_diag_xkw]{dms\_flux\_diag\_xkw} & XKW used in DMS flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_dms_flux_diag_atm_press]{dms\_flux\_diag\_atm\_press} & Atm Pressure used in DMS flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_dms_flux_diag_pv]{dms\_flux\_diag\_pv} & Piston Velocity used in DMS flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_dms_flux_diag_schmidt]{dms\_flux\_diag\_schmidt} & Schmidt Number used in DMS flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_dms_flux_diag_sat]{dms\_flux\_diag\_sat} & DMS Saturation used in DMS flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_dms_flux_diag_surf]{dms\_flux\_diag\_surf} & Surface DMS Values used in DMS flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_dms_flux_diag_ws]{dms\_flux\_diag\_ws} & Wind Speed used in DMS flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPistonVelocity]{DMSPistonVelocity} & A non-negative field controlling the rate at which DMS is restored to DMSSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPPistonVelocity]{DMSPPistonVelocity} & A non-negative field controlling the rate at which DMSP is restored to DMSPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSSurfaceRestoringValue]{DMSSurfaceRestoringValue} & Tracer is restored toward this field at a rate controlled by DMSPistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPSurfaceRestoringValue]{DMSPSurfaceRestoringValue} & Tracer is restored toward this field at a rate controlled by DMSPPistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSInteriorRestoringRate]{DMSInteriorRestoringRate} & A non-negative field controlling the rate at which DMS is restored to DMSInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPInteriorRestoringRate]{DMSPInteriorRestoringRate} & A non-negative field controlling the rate at which DMSP is restored to DMSPInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSInteriorRestoringValue]{DMSInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by DMSInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPInteriorRestoringValue]{DMSPInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by DMSPInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSExponentialDecayRate]{DMSExponentialDecayRate} & A non-negative field controlling the exponential decay of DMS \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPExponentialDecayRate]{DMSPExponentialDecayRate} & A non-negative field controlling the exponential decay of DMSP \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSIdealAgeMask]{DMSIdealAgeMask} & In top layer, DMS is reset to DMS * DMSIdealAgeMask, valid values of DMSIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPIdealAgeMask]{DMSPIdealAgeMask} & In top layer, DMSP is reset to DMSP * DMSPIdealAgeMask, valid values of DMSPIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSTTDMask]{DMSTTDMask} & In top layer, DMS is reset to TTDMask, valid values of DMSTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_DMSPTTDMask]{DMSPTTDMask} & In top layer, DMSP is reset to DMSPTTDMask, valid values of DMSPTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTSurfaceFlux]{PROTSurfaceFlux} & Proteins Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYSurfaceFlux]{POLYSurfaceFlux} & Polysaccharides Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPSurfaceFlux]{LIPSurfaceFlux} & Lipids Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTSurfaceFluxRunoff]{PROTSurfaceFluxRunoff} & Proteins Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYSurfaceFluxRunoff]{POLYSurfaceFluxRunoff} & Polysaccharides Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPSurfaceFluxRunoff]{LIPSurfaceFluxRunoff} & Lipids Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTSurfaceFluxRemoved]{PROTSurfaceFluxRemoved} & Proteins Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYSurfaceFluxRemoved]{POLYSurfaceFluxRemoved} & Polysaccharides Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPSurfaceFluxRemoved]{LIPSurfaceFluxRemoved} & Lipids Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceDOC]{avgOceanSurfaceDOC} & Ocean Surface Organics concentration: (1,2,3)=>(polysaccharides,lipids,proteins) \\
    \hline
    \hyperref[subsec:var_sec_forcing_avgOceanSurfaceDON]{avgOceanSurfaceDON} & Ocean Surface Organic Proteins concentration \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTPistonVelocity]{PROTPistonVelocity} & A non-negative field controlling the rate at which PROT is restored to PROTSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYPistonVelocity]{POLYPistonVelocity} & A non-negative field controlling the rate at which POLY is restored to POLYSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPPistonVelocity]{LIPPistonVelocity} & A non-negative field controlling the rate at which LIP is restored to LIPSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTSurfaceRestoringValue]{PROTSurfaceRestoringValue} & Tracer is restored toward this field at a rate controlled by PROTPistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYSurfaceRestoringValue]{POLYSurfaceRestoringValue} & Tracer is restored toward this field at a rate controlled by POLYPistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPSurfaceRestoringValue]{LIPSurfaceRestoringValue} & Tracer is restored toward this field at a rate controlled by LIPPistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTInteriorRestoringRate]{PROTInteriorRestoringRate} & A non-negative field controlling the rate at which PROT is restored to PROTInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYInteriorRestoringRate]{POLYInteriorRestoringRate} & A non-negative field controlling the rate at which POLY is restored to POLYInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPInteriorRestoringRate]{LIPInteriorRestoringRate} & A non-negative field controlling the rate at which LIP is restored to LIPInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTInteriorRestoringValue]{PROTInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by PROTInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYInteriorRestoringValue]{POLYInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by POLYInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPInteriorRestoringValue]{LIPInteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by LIPInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTExponentialDecayRate]{PROTExponentialDecayRate} & A non-negative field controlling the exponential decay of PROT \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYExponentialDecayRate]{POLYExponentialDecayRate} & A non-negative field controlling the exponential decay of POLY \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPExponentialDecayRate]{LIPExponentialDecayRate} & A non-negative field controlling the exponential decay of LIP \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTIdealAgeMask]{PROTIdealAgeMask} & In top layer, PROT is reset to PROT * PROTIdealAgeMask, valid values of PROTIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYIdealAgeMask]{POLYIdealAgeMask} & In top layer, POLY is reset to POLY * POLYIdealAgeMask, valid values of POLYIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPIdealAgeMask]{LIPIdealAgeMask} & In top layer, LIP is reset to LIP * LIPIdealAgeMask, valid values of LIPIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_PROTTTDMask]{PROTTTDMask} & In top layer, PROT is reset to TTDMask, valid values of PROTTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_POLYTTDMask]{POLYTTDMask} & In top layer, POLY is reset to TTDMask, valid values of POLYTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_LIPTTDMask]{LIPTTDMask} & In top layer, LIP is reset to LIPTTDMask, valid values of LIPTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgeSurfaceFlux]{iAgeSurfaceFlux} & Flux of iAge through the ocean surface. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgeSurfaceFluxRunoff]{iAgeSurfaceFluxRunoff} & Flux of iAge through the ocean surface due to river runoff. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgeSurfaceFluxRemoved]{iAgeSurfaceFluxRemoved} & Flux of iAge that is ignored coming into the ocean. Positive into ocean. \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgePistonVelocity]{iAgePistonVelocity} & A non-negative field controlling the rate at which iAge is restored to iAgeSurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgeSurfaceRestoringValue]{iAgeSurfaceRestoringValue} & iAge is restored toward this field at a rate controlled by iAgePistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgeInteriorRestoringRate]{iAgeInteriorRestoringRate} & A non-negative field controlling the rate at which iAge is restored to iAgeInteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgeInteriorRestoringValue]{iAgeInteriorRestoringValue} & iAge is restored toward this field at a rate controlled by iAgeInteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgeExponentialDecayRate]{iAgeExponentialDecayRate} & A non-negative field controlling the exponential decay of iAge \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgeIdealAgeMask]{iAgeIdealAgeMask} & In top layer, iAge is reset to iAge * iAgeIdealAgeMask, valid values of iAgeIdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_iAgeTTDMask]{iAgeTTDMask} & In top layer, iAge is reset to TTDMask, valid values of iAgeTTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11SurfaceFlux]{CFC11SurfaceFlux} & CFC11 Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12SurfaceFlux]{CFC12SurfaceFlux} & CFC12 Surface Flux \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFCSurfaceFluxRunoff]{CFCSurfaceFluxRunoff} & CFC11 Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12SurfaceFluxRunoff]{CFC12SurfaceFluxRunoff} & CFC12 Surface Flux Due to Runoff \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFCSurfaceFluxRemoved]{CFCSurfaceFluxRemoved} & CFC11 Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12SurfaceFluxRemoved]{CFC12SurfaceFluxRemoved} & CFC12 Surface Flux that is ignored \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11_flux_ifrac]{CFC11\_flux\_ifrac} & Ice Fraction used in CFC11 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11_flux_xkw]{CFC11\_flux\_xkw} & XKW used in CFC11 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11_flux_atm_press]{CFC11\_flux\_atm\_press} & Atm Pressure used in CFC11 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11_flux_pv]{CFC11\_flux\_pv} & Piston Velocity used in CFC11 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11_flux_schmidt]{CFC11\_flux\_schmidt} & Schmidt Number used in CFC11 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11_flux_sat]{CFC11\_flux\_sat} & CFC11 Saturation used in CFC11 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11_flux_surf]{CFC11\_flux\_surf} & Surface CFC11 Values used in CFC11 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11_flux_ws]{CFC11\_flux\_ws} & Wind Speed used in CFC11 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12_flux_ifrac]{CFC12\_flux\_ifrac} & Ice Fraction used in CFC12 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12_flux_xkw]{CFC12\_flux\_xkw} & XKW used in CFC12 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12_flux_atm_press]{CFC12\_flux\_atm\_press} & Atm Pressure used in CFC12 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12_flux_pv]{CFC12\_flux\_pv} & Piston Velocity used in CFC12 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12_flux_schmidt]{CFC12\_flux\_schmidt} & Schmidt Number used in CFC12 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12_flux_sat]{CFC12\_flux\_sat} & CFC12 Saturation used in CFC12 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12_flux_surf]{CFC12\_flux\_surf} & Surface CFC12 Values used in CFC12 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12_flux_ws]{CFC12\_flux\_ws} & Wind Speed used in CFC12 flux calculation \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11PistonVelocity]{CFC11PistonVelocity} & A non-negative field controlling the rate at which CFC11 is restored to CFC11SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12PistonVelocity]{CFC12PistonVelocity} & A non-negative field controlling the rate at which CFC12 is restored to CFC12SurfaceRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11SurfaceRestoringValue]{CFC11SurfaceRestoringValue} & Tracer is restored toward this field at a rate controlled by CFC11PistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12SurfaceRestoringValue]{CFC12SurfaceRestoringValue} & Tracer is restored toward this field at a rate controlled by CFC12PistonVelocity. \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11InteriorRestoringRate]{CFC11InteriorRestoringRate} & A non-negative field controlling the rate at which CFC11 is restored to CFC11InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12InteriorRestoringRate]{CFC12InteriorRestoringRate} & A non-negative field controlling the rate at which CFC12 is restored to CFC12InteriorRestoringValue \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11InteriorRestoringValue]{CFC11InteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by CFC11InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12InteriorRestoringValue]{CFC12InteriorRestoringValue} & Tracer is restored toward this field at a rate controlled by CFC12InteriorRestoringRate. \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11ExponentialDecayRate]{CFC11ExponentialDecayRate} & A non-negative field controlling the exponential decay of CFC11 \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12ExponentialDecayRate]{CFC12ExponentialDecayRate} & A non-negative field controlling the exponential decay of CFC12 \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11IdealAgeMask]{CFC11IdealAgeMask} & In top layer, CFC11 is reset to CFC11 * CFC11IdealAgeMask, valid values of CFC11IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12IdealAgeMask]{CFC12IdealAgeMask} & In top layer, CFC12 is reset to CFC12 * CFC12IdealAgeMask, valid values of CFC12IdealAgeMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC11TTDMask]{CFC11TTDMask} & In top layer, CFC11 is reset to TTDMask, valid values of CFC11TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_CFC12TTDMask]{CFC12TTDMask} & In top layer, CFC12 is reset to CFC12TTDMask, valid values of CFC12TTDMask or 0 and 1 \\
    \hline
    \hyperref[subsec:var_sec_forcing_pCFC11]{pCFC11} & Mole Fraction of Atmospheric CFC11 \\
    \hline
    \hyperref[subsec:var_sec_forcing_pCFC12]{pCFC12} & Mole Fraction of Atmospheric CFC12 \\
    \hline
    \hyperref[subsec:var_sec_forcing_windSpeedSquared10mCFC]{windSpeedSquared10mCFC} & 10 meter atmospheric wind speed squared \\
    \hline
\end{longtable}
\end{center}
}
\section[timeVaryingForcing]{\hyperref[sec:var_sec_timeVaryingForcing]{timeVaryingForcing}}
\label{sec:var_tab_timeVaryingForcing}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_timeVaryingForcing_windSpeedU]{windSpeedU} & Zonal (eastward) component of wind speed at cell centers from coupler. Positive easthward. \\
    \hline
    \hyperref[subsec:var_sec_timeVaryingForcing_windSpeedV]{windSpeedV} & Meridional (northward) component of wind speed at cell centers from coupler. Positive northward. \\
    \hline
    \hyperref[subsec:var_sec_timeVaryingForcing_windSpeedMagnitude]{windSpeedMagnitude} & Magnitude of wind speed at cell centers from coupler. \\
    \hline
    \hyperref[subsec:var_sec_timeVaryingForcing_atmosPressure]{atmosPressure} & Pressure at the sea surface due to the atmosphere. \\
    \hline
    \hyperref[subsec:var_sec_timeVaryingForcing_landIceFractionForcing]{landIceFractionForcing} & The fraction of each cell covered by land ice \\
    \hline
    \hyperref[subsec:var_sec_timeVaryingForcing_landIceFloatingFractionForcing]{landIceFloatingFractionForcing} & The fraction of each cell covered by land ice \\
    \hline
    \hyperref[subsec:var_sec_timeVaryingForcing_landIcePressureForcing]{landIcePressureForcing} & Pressure defined at the sea surface due to land ice. \\
    \hline
    \hyperref[subsec:var_sec_timeVaryingForcing_landIceDraftForcing]{landIceDraftForcing} & The elevation of the interface between land ice and the ocean. \\
    \hline
\end{longtable}
\end{center}
}
\section[scratch]{\hyperref[sec:var_sec_scratch]{scratch}}
\label{sec:var_tab_scratch}
\input{ocean/section_descriptions/scratch_struct.tex}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_scratch_normalVelocityTest]{normalVelocityTest} & horizontal velocity, normal component to an edge, for testing \\
    \hline
    \hyperref[subsec:var_sec_scratch_tangentialVelocityTest]{tangentialVelocityTest} & horizontal velocity, tangential component to an edge, for testing \\
    \hline
    \hyperref[subsec:var_sec_scratch_strainRateR3Cell]{strainRateR3Cell} & strain rate tensor at cell center, R3, in symmetric 6-index form \\
    \hline
    \hyperref[subsec:var_sec_scratch_strainRateR3CellSolution]{strainRateR3CellSolution} & strain rate solution tensor at cell center, R3, in symmetric 6-index form \\
    \hline
    \hyperref[subsec:var_sec_scratch_strainRateR3Edge]{strainRateR3Edge} & strain rate tensor at edge, R3, in symmetric 6-index form \\
    \hline
    \hyperref[subsec:var_sec_scratch_strainRateLonLatRCell]{strainRateLonLatRCell} & strain rate tensor at cell center, 3D, lon-lat-r in symmetric 6-index form, {\color{red}Temporary only} \\
    \hline
    \hyperref[subsec:var_sec_scratch_strainRateLonLatRCellSolution]{strainRateLonLatRCellSolution} & strain rate tensor at cell center, 3D, lon-lat-r in symmetric 6-index form, {\color{red}Temporary only} \\
    \hline
    \hyperref[subsec:var_sec_scratch_strainRateLonLatREdge]{strainRateLonLatREdge} & strain rate tensor at edge, 3D, lon-lat-r in symmetric 6-index form, {\color{red}Temporary only} \\
    \hline
    \hyperref[subsec:var_sec_scratch_divTensorR3Cell]{divTensorR3Cell} & divergence of the tensor at cell center, as an R3 vector \\
    \hline
    \hyperref[subsec:var_sec_scratch_divTensorR3CellSolution]{divTensorR3CellSolution} & divergence of the tensor solution at cell center, as an R3 vector \\
    \hline
    \hyperref[subsec:var_sec_scratch_divTensorLonLatRCell]{divTensorLonLatRCell} & divergence of the tensor at cell center, as a lon-lat-r vector \\
    \hline
    \hyperref[subsec:var_sec_scratch_divTensorLonLatRCellSolution]{divTensorLonLatRCellSolution} & divergence of the tensor at cell center, as a lon-lat-r vector, solution \\
    \hline
    \hyperref[subsec:var_sec_scratch_outerProductEdge]{outerProductEdge} & Outer product, $u_e \otimes n_e$, at each edge. \\
    \hline
    \hyperref[subsec:var_sec_scratch_smoothedField]{smoothedField} & the smoothed version of a field on cells during iterative smoothing \\
    \hline
    \hyperref[subsec:var_sec_scratch_zInterfaceScratch]{zInterfaceScratch} & location of layer interfaces at cell centers, used for thickening layers constrained by the Haney number (rx1) \\
    \hline
    \hyperref[subsec:var_sec_scratch_goalStretchScratch]{goalStretchScratch} & the goal stretch field for the vertical coordinate \\
    \hline
    \hyperref[subsec:var_sec_scratch_goalWeightScratch]{goalWeightScratch} & the sum of weights used to determine the goal stretch field \\
    \hline
    \hyperref[subsec:var_sec_scratch_zTopScratch]{zTopScratch} & location of the upper layer used to compute the Haney number (rx1), equal to ssh for top layer and zMid of the layer for subsequent layers \\
    \hline
    \hyperref[subsec:var_sec_scratch_zBotScratch]{zBotScratch} & location of the lower layer used to compute the Haney number (rx1), equal zMid of the layer lower layer (but a 1D filed is needed for halo exchanges) \\
    \hline
    \hyperref[subsec:var_sec_scratch_zBotNewScratch]{zBotNewScratch} & updated location of the lower layer used to compute the Haney number (rx1), needed so update is agnostic to the order in which cells are accessed \\
    \hline
    \hyperref[subsec:var_sec_scratch_smoothingMaskNewScratch]{smoothingMaskNewScratch} & a copy of the smoothing mask used to iteratively expand the field into a buffer region of open ocean around land ice. \\
    \hline
    \hyperref[subsec:var_sec_scratch_cullStack]{cullStack} & Temporary space to hold a stack for culling inland seas. \\
    \hline
    \hyperref[subsec:var_sec_scratch_touchedCell]{touchedCell} & Temporary space to a hold mask if the cell has been touched or not, when culling inland seas. \\
    \hline
    \hyperref[subsec:var_sec_scratch_oceanCell]{oceanCell} & Temporary space to a hold mask if the cell is an active ocean cell or not. \\
    \hline
    \hyperref[subsec:var_sec_scratch_cullStackSize]{cullStackSize} & Integer to hold the size of the cullStack for each block. \\
    \hline
    \hyperref[subsec:var_sec_scratch_interpActiveTracer]{interpActiveTracer} & temporary space for holding one tracer at a time as part of horizontal interpolation \\
    \hline
    \hyperref[subsec:var_sec_scratch_interpEcosysTracer]{interpEcosysTracer} & temporary space for holding one tracer at a time as part of horizontal interpolation \\
    \hline
    \hyperref[subsec:var_sec_scratch_interpActiveTracerSmooth]{interpActiveTracerSmooth} & temporary space for holding one tracer at a time as part of horizontal interpolation \\
    \hline
    \hyperref[subsec:var_sec_scratch_interpEcosysTracerSmooth]{interpEcosysTracerSmooth} & temporary space for holding one tracer at a time as part of horizontal interpolation \\
    \hline
    \hyperref[subsec:var_sec_scratch_isomip_bottomPressure]{isomip\_bottomPressure} & Temporary space to hold the pressure at the bottom of the ocean, used to compute estimated sea-surface pressure under landice. \\
    \hline
\end{longtable}
\end{center}
}
\section[pointLocations]{\hyperref[sec:var_sec_pointLocations]{pointLocations}}
\label{sec:var_tab_pointLocations}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_pointLocations_pointCellGlobalID]{pointCellGlobalID} & List of global cell IDs in point set. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_pointCellLocalID]{pointCellLocalID} & List of local cell IDs in point set. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_indexToPointCellLocalID]{indexToPointCellLocalID} & Index to list of local cell IDs in point set. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_pointNames]{pointNames} & The names of each point. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_pointGroupNames]{pointGroupNames} & The names of each point group. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_nPointsInGroup]{nPointsInGroup} & The number of points in each point group. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_pointsInGroup]{pointsInGroup} & The indices of each point in a each group. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_xPoint]{xPoint} & X Coordinate in cartesian space of point locations. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_yPoint]{yPoint} & Y Coordinate in cartesian space of point locations. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_zPoint]{zPoint} & Z Coordinate in cartesian space of point locations. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_latPoint]{latPoint} & Latitude of point locations. \\
    \hline
    \hyperref[subsec:var_sec_pointLocations_lonPoint]{lonPoint} & Longitude of point locations. \\
    \hline
\end{longtable}
\end{center}
}
\section[regions]{\hyperref[sec:var_sec_regions]{regions}}
\label{sec:var_tab_regions}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_regions_regionCellMasks]{regionCellMasks} & The region masks for each cell. \\
    \hline
    \hyperref[subsec:var_sec_regions_regionVertexMasks]{regionVertexMasks} & The region masks for each vertex. \\
    \hline
    \hyperref[subsec:var_sec_regions_regionsInGroup]{regionsInGroup} & The list of region indices in each group. \\
    \hline
    \hyperref[subsec:var_sec_regions_nRegionsInGroup]{nRegionsInGroup} & The number of regions in each group. \\
    \hline
    \hyperref[subsec:var_sec_regions_regionNames]{regionNames} & The name for each region. \\
    \hline
    \hyperref[subsec:var_sec_regions_regionGroupNames]{regionGroupNames} & The name for each region group. \\
    \hline
\end{longtable}
\end{center}
}
\section[transects]{\hyperref[sec:var_sec_transects]{transects}}
\label{sec:var_tab_transects}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_transects_transectEdgeMasks]{transectEdgeMasks} & Mask of edges for measuring transport across transects \\
    \hline
    \hyperref[subsec:var_sec_transects_transectEdgeMaskSigns]{transectEdgeMaskSigns} & Sign of normalVelocity on edge for this transect \\
    \hline
    \hyperref[subsec:var_sec_transects_transectsInGroup]{transectsInGroup} & The list of transect indices in each group. \\
    \hline
    \hyperref[subsec:var_sec_transects_nTransectsInGroup]{nTransectsInGroup} & The number of transects in each group. \\
    \hline
    \hyperref[subsec:var_sec_transects_transectNames]{transectNames} & The name for each transect. \\
    \hline
    \hyperref[subsec:var_sec_transects_transectGroupNames]{transectGroupNames} & The name for each transect group. \\
    \hline
\end{longtable}
\end{center}
}
\section[LTS]{\hyperref[sec:var_sec_LTS]{LTS}}
\label{sec:var_tab_LTS}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_LTS_LTSRegion]{LTSRegion} & Definition of LTS regions. This is read from the initial condition file (typically named init.nc), and set up with a pre-processing step. The values are: 1 = fine; 2 = coarse; 3 = interface layer one; 4 = interface layer two; 5 = fine close to interface layer one. \\
    \hline
    \hyperref[subsec:var_sec_LTS_cellsInLTSRegion]{cellsInLTSRegion} & Cell mask for each region. For the first two dimensions, the regions in the array are defined as follows: (1,1): fine, (1,2) interface layer one, (1,3) fine close to interface layer one, (2,2) interface layer two, (2,1) coarse. \\
    \hline
    \hyperref[subsec:var_sec_LTS_nCellsInLTSRegion]{nCellsInLTSRegion} & Number of cells in each region of cellsInLTSRegion. \\
    \hline
    \hyperref[subsec:var_sec_LTS_edgesInLTSRegion]{edgesInLTSRegion} & Edge mask for each region. For the first two dimensions, the regions in the array are defined as follows: (1,1): fine, (1,2) interface layer one, (1,3) fine close to interface layer one, (2,2) interface layer two, (2,1) coarse. \\
    \hline
    \hyperref[subsec:var_sec_LTS_nEdgesInLTSRegion]{nEdgesInLTSRegion} & Number of edges in each region of edgesInLTSRegion. \\
    \hline
\end{longtable}
\end{center}
}
\section[surfaceSalinityMonthlyForcing]{\hyperref[sec:var_sec_surfaceSalinityMonthlyForcing]{surfaceSalinityMonthlyForcing}}
\label{sec:var_tab_surfaceSalinityMonthlyForcing}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_surfaceSalinityMonthlyForcing_surfaceSalinityMonthlyClimatologyValue]{surfaceSalinityMonthly\-ClimatologyValue} & monthly surface salinity climatology interpolated to current timestep \\
    \hline
\end{longtable}
\end{center}
}
\section[ecosysMonthlyForcing]{\hyperref[sec:var_sec_ecosysMonthlyForcing]{ecosysMonthlyForcing}}
\label{sec:var_tab_ecosysMonthlyForcing}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_depositionFluzNO3]{depositionFluzNO3} & Atmospheric Deposition of NO3 \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_depositionFluzNH4]{depositionFluzNH4} & Atmospheric Deposition of NH4 \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_riverFluzNO3]{riverFluzNO3} & River Runoff Fluz of NO3 \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_riverFluzPO4]{riverFluzPO4} & River Runoff Fluz of PO4 \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_riverFluzSiO3]{riverFluzSiO3} & River Runoff Fluz of SiO3 \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_riverFluzFe]{riverFluzFe} & River Runoff Fluz of Fe \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_riverFluzDOC]{riverFluzDOC} & River Runoff Fluz of DOC \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_riverFluzDON]{riverFluzDON} & River Runoff Fluz of DON \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_riverFluzDOP]{riverFluzDOP} & River Runoff Fluz of DOP \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_riverFluzDIC]{riverFluzDIC} & River Runoff Fluz of DIC \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_riverFluzALK]{riverFluzALK} & River Runoff Fluz of ALK \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_dust_FLUZ_IN]{dust\_FLUZ\_IN} & Surface Dust Flux \\
    \hline
    \hyperref[subsec:var_sec_ecosysMonthlyForcing_IRON_FLUZ_IN]{IRON\_FLUZ\_IN} & Surface Fe Flux \\
    \hline
\end{longtable}
\end{center}
}
\section[CFCAnnualForcing]{\hyperref[sec:var_sec_CFCAnnualForcing]{CFCAnnualForcing}}
\label{sec:var_tab_CFCAnnualForcing}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_CFCAnnualForcing_atmCFC11]{atmCFC11} & Mole Fraction of Atmospheric CFC11 \\
    \hline
    \hyperref[subsec:var_sec_CFCAnnualForcing_atmCFC12]{atmCFC12} & Mole Fraction of Atmospheric CFC12 \\
    \hline
\end{longtable}
\end{center}
}
\section[globalStatsAM]{\hyperref[sec:var_sec_globalStatsAM]{globalStatsAM}}
\label{sec:var_tab_globalStatsAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_areaCellGlobal]{areaCellGlobal} & sum of the areaCell variable over the full domain, used to normalize global statistics \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_areaEdgeGlobal]{areaEdgeGlobal} & sum of the areaEdge variable over the full domain, used to normalize global statistics \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_areaTriangleGlobal]{areaTriangleGlobal} & sum of the areaTriangle variable over the full domain, used to normalize global statistics \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_volumeCellGlobal]{volumeCellGlobal} & sum of the volumeCell variable over the full domain, used to normalize global statistics \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_volumeEdgeGlobal]{volumeEdgeGlobal} & sum of the volumeEdge variable over the full domain, used to normalize global statistics \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_CFLNumberGlobal]{CFLNumberGlobal} & maximum CFL number over the full domain \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_landIceFloatingAreaSum]{landIceFloatingAreaSum} & sum of areaCell where landIceMask == 1, used to normalize global statistics in land-ice cavities \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessMin]{layerThicknessMin} & Minimum global value of layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalVelocityMin]{normalVelocityMin} & Minimum global value of normalVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_tangentialVelocityMin]{tangentialVelocityMin} & Minimum global value of tangentialVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessEdgeMin]{layerThicknessEdgeMin} & Minimum global value of layerThicknessEdgeMean on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_relativeVorticityMin]{relativeVorticityMin} & Minimum global value of relativeVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_enstrophyMin]{enstrophyMin} & Minimum global value of enstrophy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_kineticEnergyCellMin]{kineticEnergyCellMin} & Minimum global value of kineticEnergy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalizedAbsoluteVorticityMin]{normalizedAbsoluteVorticityMin} & Minimum global value of normalizedAbsoluteVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_pressureMin]{pressureMin} & Minimum global value of pressure in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_montgomeryPotentialMin]{montgomeryPotentialMin} & Minimum global value of the Montgomery Potential in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertVelocityTopMin]{vertVelocityTopMin} & Minimum global value of vertVelocityTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertAleTransportTopMin]{vertAleTransportTopMin} & Minimum global value of vertAleTransportTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_lowFreqDivergenceMin]{lowFreqDivergenceMin} & Minimum global value of lowFreqDivergence in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_highFreqThicknessMin]{highFreqThicknessMin} & Minimum global value of highFreqThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureMin]{temperatureMin} & Minimum global value of temperature in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityMin]{salinityMin} & Minimum global value of salinity in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessPreviousTimestepMin]{layerThicknessPreviousTimestep\-Min} & Minimum global value of previous step layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_frazilLayerThicknessTendencyMin]{frazilLayerThicknessTendencyMin} & Minimum global value of layer thickness tendency due to frazil formation in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_evaporationFluxMin]{evaporationFluxMin} & Minimum global value of evaporationFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_rainFluxMin]{rainFluxMin} & Minimum global value of rainFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_snowFluxMin]{snowFluxMin} & Minimum global value of snowFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_seaIceFreshWaterFluxMin]{seaIceFreshWaterFluxMin} & Minimum global value of seaIceFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_icebergFreshWaterFluxMin]{icebergFreshWaterFluxMin} & Minimum global value of icebergFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_riverRunoffFluxMin]{riverRunoffFluxMin} & Minimum global value of riverRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_iceRunoffFluxMin]{iceRunoffFluxMin} & Minimum global value of iceRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureFluxMin]{temperatureFluxMin} & Minimum global value of temperatureFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityFluxMin]{salinityFluxMin} & Minimum global value of salinityFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityRestoringFluxMin]{salinityRestoringFluxMin} & Minimum global value of salinityRestoringFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_landIceFreshwaterFluxMin]{landIceFreshwaterFluxMin} & Minimum global value of landIceFreshwaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceMassMin]{accumulatedLandIceMassMin} & Minimum global value of accumulatedLandIceMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceHeatMin]{accumulatedLandIceHeatMin} & Minimum global value of accumulatedLandIceHeat in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceFrazilMassMin]{accumulatedLandIceFrazilMass\-Min} & Minimum global value of accumulatedLandIceFrazilMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessMax]{layerThicknessMax} & Maximum global value of layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalVelocityMax]{normalVelocityMax} & Maximum global value of normalVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_tangentialVelocityMax]{tangentialVelocityMax} & Maximum global value of tangentialVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessEdgeMax]{layerThicknessEdgeMax} & Maximum global value of layerThicknessEdgeMean on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_relativeVorticityMax]{relativeVorticityMax} & Maximum global value of relativeVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_enstrophyMax]{enstrophyMax} & Maximum global value of enstrophy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_kineticEnergyCellMax]{kineticEnergyCellMax} & Maximum global value of kineticEnergy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalizedAbsoluteVorticityMax]{normalizedAbsoluteVorticityMax} & Maximum global value of normalizedAbsoluteVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_pressureMax]{pressureMax} & Maximum global value of pressure in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_montgomeryPotentialMax]{montgomeryPotentialMax} & Maximum global value of the Montgomery Potential in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertVelocityTopMax]{vertVelocityTopMax} & Maximum global value of vertVelocityTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertAleTransportTopMax]{vertAleTransportTopMax} & Maximum global value of vertAleTransportTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_lowFreqDivergenceMax]{lowFreqDivergenceMax} & Maximum global value of lowFreqDivergence in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_highFreqThicknessMax]{highFreqThicknessMax} & Maximum global value of highFreqThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureMax]{temperatureMax} & Maximum global value of temperature in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityMax]{salinityMax} & Maximum global value of salinity in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessPreviousTimestepMax]{layerThicknessPreviousTimestep\-Max} & Maximum global value of previous step layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_frazilLayerThicknessTendencyMax]{frazilLayerThicknessTendencyMax} & Maximum global value of layer thickness tendency due to frazil formation in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_evaporationFluxMax]{evaporationFluxMax} & Maximum global value of evaporationFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_rainFluxMax]{rainFluxMax} & Maximum global value of rainFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_snowFluxMax]{snowFluxMax} & Maximum global value of snowFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_seaIceFreshWaterFluxMax]{seaIceFreshWaterFluxMax} & Maximum global value of seaIceFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_icebergFreshWaterFluxMax]{icebergFreshWaterFluxMax} & Maximum global value of icebergFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_riverRunoffFluxMax]{riverRunoffFluxMax} & Maximum global value of riverRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_iceRunoffFluxMax]{iceRunoffFluxMax} & Maximum global value of iceRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureFluxMax]{temperatureFluxMax} & Maximum global value of temperatureFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityFluxMax]{salinityFluxMax} & Maximum global value of salinityFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityRestoringFluxMax]{salinityRestoringFluxMax} & Maximum global value of salinityRestoringFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_landIceFreshwaterFluxMax]{landIceFreshwaterFluxMax} & Maximum global value of landIceFreshwaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceMassMax]{accumulatedLandIceMassMax} & Maximum global value of accumulatedLandIceMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceHeatMax]{accumulatedLandIceHeatMax} & Maximum global value of accumulatedLandIceHeat in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceFrazilMassMax]{accumulatedLandIceFrazilMass\-Max} & Maximum global value of accumulatedLandIceFrazilMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessSum]{layerThicknessSum} & Accumulated global value of layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalVelocitySum]{normalVelocitySum} & Accumulated global value of normalVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_tangentialVelocitySum]{tangentialVelocitySum} & Accumulated global value of tangentialVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessEdgeSum]{layerThicknessEdgeSum} & Accumulated global value of layerThicknessEdgeMean on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_relativeVorticitySum]{relativeVorticitySum} & Accumulated global value of relativeVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_enstrophySum]{enstrophySum} & Accumulated global value of enstrophy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_kineticEnergyCellSum]{kineticEnergyCellSum} & Accumulated global value of kineticEnergy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalizedAbsoluteVorticitySum]{normalizedAbsoluteVorticitySum} & Accumulated global value of normalizedAbsoluteVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_pressureSum]{pressureSum} & Accumulated global value of pressure in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_montgomeryPotentialSum]{montgomeryPotentialSum} & Accumulated global value of the Montgomery Potential in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertVelocityTopSum]{vertVelocityTopSum} & Accumulated global value of vertVelocityTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertAleTransportTopSum]{vertAleTransportTopSum} & Accumulated global value of vertAleTransportTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_lowFreqDivergenceSum]{lowFreqDivergenceSum} & Accumulated global value of lowFreqDivergence in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_highFreqThicknessSum]{highFreqThicknessSum} & Accumulated global value of highFreqThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureSum]{temperatureSum} & Accumulated global value of temperature in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinitySum]{salinitySum} & Accumulated global value of salinity in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessPreviousTimestepSum]{layerThicknessPreviousTimestep\-Sum} & Accumulated global value of previous step layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_frazilLayerThicknessTendencySum]{frazilLayerThicknessTendency\-Sum} & Accumulated global value of layer thickness tendency due to frazil formation in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_evaporationFluxSum]{evaporationFluxSum} & Accumulated global value of evaporationFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_rainFluxSum]{rainFluxSum} & Accumulated global value of rainFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_snowFluxSum]{snowFluxSum} & Accumulated global value of snowFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_seaIceFreshWaterFluxSum]{seaIceFreshWaterFluxSum} & Accumulated global value of seaIceFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_icebergFreshWaterFluxSum]{icebergFreshWaterFluxSum} & Accumulated global value of icebergFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_riverRunoffFluxSum]{riverRunoffFluxSum} & Accumulated global value of riverRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_iceRunoffFluxSum]{iceRunoffFluxSum} & Accumulated global value of iceRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureFluxSum]{temperatureFluxSum} & Accumulated global value of temperatureFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityFluxSum]{salinityFluxSum} & Accumulated global value of salinityFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityRestoringFluxSum]{salinityRestoringFluxSum} & Accumulated global value of salinityRestoringFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_landIceFreshwaterFluxSum]{landIceFreshwaterFluxSum} & Accumulated global value of landIceFreshwaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceMassSum]{accumulatedLandIceMassSum} & Accumulated global value of accumulatedLandIceMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceHeatSum]{accumulatedLandIceHeatSum} & Accumulated global value of accumulatedLandIceHeat in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceFrazilMassSum]{accumulatedLandIceFrazilMass\-Sum} & Accumulated global value of accumulatedLandIceFrazilMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessRms]{layerThicknessRms} & Global root mean square value of layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalVelocityRms]{normalVelocityRms} & Global root mean square value of normalVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_tangentialVelocityRms]{tangentialVelocityRms} & Global root mean square value of tangentialVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessEdgeRms]{layerThicknessEdgeRms} & Global root mean square value of layerThicknessEdgeMean on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_relativeVorticityRms]{relativeVorticityRms} & Global root mean square value of relativeVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_enstrophyRms]{enstrophyRms} & Global root mean square value of enstrophy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_kineticEnergyCellRms]{kineticEnergyCellRms} & Global root mean square value of kineticEnergy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalizedAbsoluteVorticityRms]{normalizedAbsoluteVorticityRms} & Global root mean square value of normalizedAbsoluteVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_pressureRms]{pressureRms} & Global root mean square value of pressure in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_montgomeryPotentialRms]{montgomeryPotentialRms} & Global root mean square value of the Montgomery Potential in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertVelocityTopRms]{vertVelocityTopRms} & Global root mean square value of vertVelocityTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertAleTransportTopRms]{vertAleTransportTopRms} & Global root mean square value of vertAleTransportTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_lowFreqDivergenceRms]{lowFreqDivergenceRms} & Global root mean square value of lowFreqDivergence in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_highFreqThicknessRms]{highFreqThicknessRms} & Global root mean square value of highFreqThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureRms]{temperatureRms} & Global root mean square value of temperature in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityRms]{salinityRms} & Global root mean square value of salinity in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessPreviousTimestepRms]{layerThicknessPreviousTimestep\-Rms} & Global root mean square value of previous step layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_frazilLayerThicknessTendencyRms]{frazilLayerThicknessTendencyRms} & Global root mean square value of layer thickness tendency due to frazil formation in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_evaporationFluxRms]{evaporationFluxRms} & Global root mean square value of evaporationFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_rainFluxRms]{rainFluxRms} & Global root mean square value of rainFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_snowFluxRms]{snowFluxRms} & Global root mean square value of snowFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_seaIceFreshWaterFluxRms]{seaIceFreshWaterFluxRms} & Global root mean square value of seaIceFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_icebergFreshWaterFluxRms]{icebergFreshWaterFluxRms} & Global root mean square value of icebergFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_riverRunoffFluxRms]{riverRunoffFluxRms} & Global root mean square value of riverRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_iceRunoffFluxRms]{iceRunoffFluxRms} & Global root mean square value of iceRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureFluxRms]{temperatureFluxRms} & Global root mean square value of temperatureFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityFluxRms]{salinityFluxRms} & Global root mean square value of salinityFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityRestoringFluxRms]{salinityRestoringFluxRms} & Global root mean square value of salinityRestoringFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_landIceFreshwaterFluxRms]{landIceFreshwaterFluxRms} & Global root mean square value of landIceFreshwaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceMassRms]{accumulatedLandIceMassRms} & Global root mean square value of accumulatedLandIceMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceHeatRms]{accumulatedLandIceHeatRms} & Global root mean square value of accumulatedLandIceHeat in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceFrazilMassRms]{accumulatedLandIceFrazilMass\-Rms} & Global root mean square value of accumulatedLandIceFrazilMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessAvg]{layerThicknessAvg} & Average value of layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalVelocityAvg]{normalVelocityAvg} & Average value of normalVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_tangentialVelocityAvg]{tangentialVelocityAvg} & Average value of tangentialVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessEdgeAvg]{layerThicknessEdgeAvg} & Average value of layerThicknessEdgeMean on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_relativeVorticityAvg]{relativeVorticityAvg} & Average value of relativeVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_enstrophyAvg]{enstrophyAvg} & Average value of enstrophy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_kineticEnergyCellAvg]{kineticEnergyCellAvg} & Average value of kineticEnergy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalizedAbsoluteVorticityAvg]{normalizedAbsoluteVorticityAvg} & Average value of normalizedAbsoluteVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_pressureAvg]{pressureAvg} & Average value of pressure in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_montgomeryPotentialAvg]{montgomeryPotentialAvg} & Average value of the Montgomery Potential in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertVelocityTopAvg]{vertVelocityTopAvg} & Average value of vertVelocityTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertAleTransportTopAvg]{vertAleTransportTopAvg} & Average value of vertAleTransportTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_lowFreqDivergenceAvg]{lowFreqDivergenceAvg} & Average value of lowFreqDivergence in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_highFreqThicknessAvg]{highFreqThicknessAvg} & Average value of highFreqThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureAvg]{temperatureAvg} & Average value of temperature in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityAvg]{salinityAvg} & Average value of salinity in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessPreviousTimestepAvg]{layerThicknessPreviousTimestep\-Avg} & Average value of previous step layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_frazilLayerThicknessTendencyAvg]{frazilLayerThicknessTendencyAvg} & Average value of layer thickness tendency due to frazil formation in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_evaporationFluxAvg]{evaporationFluxAvg} & Average value of evaporationFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_rainFluxAvg]{rainFluxAvg} & Average value of rainFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_snowFluxAvg]{snowFluxAvg} & Average value of snowFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_seaIceFreshWaterFluxAvg]{seaIceFreshWaterFluxAvg} & Average value of seaIceFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_icebergFreshWaterFluxAvg]{icebergFreshWaterFluxAvg} & Average value of icebergFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_riverRunoffFluxAvg]{riverRunoffFluxAvg} & Average value of riverRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_iceRunoffFluxAvg]{iceRunoffFluxAvg} & Average value of iceRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureFluxAvg]{temperatureFluxAvg} & Average value of temperatureFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityFluxAvg]{salinityFluxAvg} & Average value of salinityFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityRestoringFluxAvg]{salinityRestoringFluxAvg} & Average value of salinityRestoringFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_landIceFreshwaterFluxAvg]{landIceFreshwaterFluxAvg} & Average value of landIceFreshwaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceMassAvg]{accumulatedLandIceMassAvg} & Average value of accumulatedLandIceMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceHeatAvg]{accumulatedLandIceHeatAvg} & Average value of accumulatedLandIceHeat in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceFrazilMassAvg]{accumulatedLandIceFrazilMass\-Avg} & Average value of accumulatedLandIceFrazilMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessMinVertSum]{layerThicknessMinVertSum} & Minimum vertical sum of layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalVelocityMinVertSum]{normalVelocityMinVertSum} & Minimum vertical sum of normalVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_tangentialVelocityMinVertSum]{tangentialVelocityMinVertSum} & Minimum vertical sum of tangentialVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessEdgeMinVertSum]{layerThicknessEdgeMinVertSum} & Minimum vertical sum of layerThicknessEdgeMean on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_relativeVorticityMinVertSum]{relativeVorticityMinVertSum} & Minimum vertical sum of relativeVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_enstrophyMinVertSum]{enstrophyMinVertSum} & Minimum vertical sum of enstrophy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_kineticEnergyCellMinVertSum]{kineticEnergyCellMinVertSum} & Minimum vertical sum of kineticEnergy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalizedAbsoluteVorticityMinVertSum]{normalizedAbsoluteVorticityMin\-VertSum} & Minimum vertical sum of normalizedAbsoluteVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_pressureMinVertSum]{pressureMinVertSum} & Minimum vertical sum of pressure in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_montgomeryPotentialMinVertSum]{montgomeryPotentialMinVert\-Sum} & Minimum vertical sum of the Montgomery Potential in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertVelocityTopMinVertSum]{vertVelocityTopMinVertSum} & Minimum vertical sum of vertVelocityTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertAleTransportTopMinVertSum]{vertAleTransportTopMinVert\-Sum} & Minimum vertical sum of vertAleTransportTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_lowFreqDivergenceMinVertSum]{lowFreqDivergenceMinVertSum} & Minimum vertical sum of lowFreqDivergence in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_highFreqThicknessMinVertSum]{highFreqThicknessMinVertSum} & Minimum vertical sum of highFreqThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureMinVertSum]{temperatureMinVertSum} & Minimum vertical sum of temperature in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityMinVertSum]{salinityMinVertSum} & Minimum vertical sum of salinity in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessPreviousTimestepMinVertSum]{layerThicknessPreviousTimestep\-MinVertSum} & Minimum vertical sum of previous step layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_frazilLayerThicknessTendencyMinVertSum]{frazilLayerThicknessTendencyMin\-VertSum} & Minimum vertical sum of layer thickness tendency due to frazil formation in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_evaporationFluxMinVertSum]{evaporationFluxMinVertSum} & Minimum vertical sum of evaporationFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_rainFluxMinVertSum]{rainFluxMinVertSum} & Minimum vertical sum of rainFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_snowFluxMinVertSum]{snowFluxMinVertSum} & Minimum vertical sum of snowFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_seaIceFreshWaterFluxMinVertSum]{seaIceFreshWaterFluxMinVert\-Sum} & Minimum vertical sum of seaIceFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_icebergFreshWaterFluxMinVertSum]{icebergFreshWaterFluxMinVert\-Sum} & Minimum vertical sum of icebergFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_riverRunoffFluxMinVertSum]{riverRunoffFluxMinVertSum} & Minimum vertical sum of riverRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_iceRunoffFluxMinVertSum]{iceRunoffFluxMinVertSum} & Minimum vertical sum of iceRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureFluxMinVertSum]{temperatureFluxMinVertSum} & Minimum vertical sum of temperatureFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityFluxMinVertSum]{salinityFluxMinVertSum} & Minimum vertical sum of salinityFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityRestoringFluxMinVertSum]{salinityRestoringFluxMinVert\-Sum} & Minimum vertical sum of salinityRestoringFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_landIceFreshwaterFluxMinVertSum]{landIceFreshwaterFluxMinVert\-Sum} & Minimum vertical sum of landIceFreshwaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceMassMinVertSum]{accumulatedLandIceMassMinVert\-Sum} & Minimum vertical sum of accumulatedLandIceMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceHeatMinVertSum]{accumulatedLandIceHeatMinVert\-Sum} & Minimum vertical sum of accumulatedLandIceHeat in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceFrazilMassMinVertSum]{accumulatedLandIceFrazilMass\-MinVertSum} & Minimum vertical sum of accumulatedLandIceFrazilMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessMaxVertSum]{layerThicknessMaxVertSum} & Maximum vertical sum of layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalVelocityMaxVertSum]{normalVelocityMaxVertSum} & Maximum vertical sum of normalVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_tangentialVelocityMaxVertSum]{tangentialVelocityMaxVertSum} & Maximum vertical sum of tangentialVelocity on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessEdgeMaxVertSum]{layerThicknessEdgeMaxVertSum} & Maximum vertical sum of layerThicknessEdgeMean on ocean edges. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_relativeVorticityMaxVertSum]{relativeVorticityMaxVertSum} & Maximum vertical sum of relativeVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_enstrophyMaxVertSum]{enstrophyMaxVertSum} & Maximum vertical sum of enstrophy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_kineticEnergyCellMaxVertSum]{kineticEnergyCellMaxVertSum} & Maximum vertical sum of kineticEnergy in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_normalizedAbsoluteVorticityMaxVertSum]{normalizedAbsoluteVorticityMax\-VertSum} & Maximum vertical sum of normalizedAbsoluteVorticity on ocean vertices. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_pressureMaxVertSum]{pressureMaxVertSum} & Maximum vertical sum of pressure in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_montgomeryPotentialMaxVertSum]{montgomeryPotentialMaxVert\-Sum} & Maximum vertical sum of the Montgomery Potential in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertVelocityTopMaxVertSum]{vertVelocityTopMaxVertSum} & Maximum vertical sum of vertVelocityTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_vertAleTransportTopMaxVertSum]{vertAleTransportTopMaxVert\-Sum} & Maximum vertical sum of vertAleTransportTop in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_lowFreqDivergenceMaxVertSum]{lowFreqDivergenceMaxVertSum} & Maximum vertical sum of lowFreqDivergence in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_highFreqThicknessMaxVertSum]{highFreqThicknessMaxVertSum} & Maximum vertical sum of highFreqThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureMaxVertSum]{temperatureMaxVertSum} & Maximum vertical sum of temperature in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityMaxVertSum]{salinityMaxVertSum} & Maximum vertical sum of salinity in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_layerThicknessPreviousTimestepMaxVertSum]{layerThicknessPreviousTimestep\-MaxVertSum} & Maximum vertical sum of previous step layerThickness in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_frazilLayerThicknessTendencyMaxVertSum]{frazilLayerThicknessTendencyMax\-VertSum} & Maximum vertical sum of layer thickness tendency due to frazil formation in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_evaporationFluxMaxVertSum]{evaporationFluxMaxVertSum} & Maximum vertical sum of evaporationFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_rainFluxMaxVertSum]{rainFluxMaxVertSum} & Maximum vertical sum of rainFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_snowFluxMaxVertSum]{snowFluxMaxVertSum} & Maximum vertical sum of snowFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_seaIceFreshWaterFluxMaxVertSum]{seaIceFreshWaterFluxMaxVert\-Sum} & Maximum vertical sum of seaIceFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_icebergFreshWaterFluxMaxVertSum]{icebergFreshWaterFluxMaxVert\-Sum} & Maximum vertical sum of icebergFreshWaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_riverRunoffFluxMaxVertSum]{riverRunoffFluxMaxVertSum} & Maximum vertical sum of riverRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_iceRunoffFluxMaxVertSum]{iceRunoffFluxMaxVertSum} & Maximum vertical sum of iceRunoffFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_temperatureFluxMaxVertSum]{temperatureFluxMaxVertSum} & Maximum vertical sum of temperatureFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityFluxMaxVertSum]{salinityFluxMaxVertSum} & Maximum vertical sum of salinityFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_salinityRestoringFluxMaxVertSum]{salinityRestoringFluxMaxVert\-Sum} & Maximum vertical sum of salinityRestoringFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_landIceFreshwaterFluxMaxVertSum]{landIceFreshwaterFluxMaxVert\-Sum} & Maximum vertical sum of landIceFreshwaterFlux in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceMassMaxVertSum]{accumulatedLandIceMassMax\-VertSum} & Maximum vertical sum of accumulatedLandIceMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceHeatMaxVertSum]{accumulatedLandIceHeatMaxVert\-Sum} & Maximum vertical sum of accumulatedLandIceHeat in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_accumulatedLandIceFrazilMassMaxVertSum]{accumulatedLandIceFrazilMass\-MaxVertSum} & Maximum vertical sum of accumulatedLandIceFrazilMass in ocean cells. \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_totalVolumeChange]{totalVolumeChange} & Total volume change of the ocean relative to previous timestep \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_netFreshwaterInput]{netFreshwaterInput} & Net fresh water change (input-output) over the timestep due to surface fluxes and frazil formation \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_absoluteFreshWaterConservation]{absoluteFreshWaterConservation} & Difference between change in ocean volume and freshwater input \\
    \hline
    \hyperref[subsec:var_sec_globalStatsAM_relativeFreshWaterConservation]{relativeFreshWaterConservation} & Difference between change in ocean volume and freshwater input divided by volume change \\
    \hline
\end{longtable}
\end{center}
}
\section[surfaceAreaWeightedAveragesAM]{\hyperref[sec:var_sec_surfaceAreaWeightedAveragesAM]{surfaceAreaWeightedAveragesAM}}
\label{sec:var_tab_surfaceAreaWeightedAveragesAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceMaskValue]{minSurfaceMaskValue} & Minimum value of region mask (should always be 1 for valid regions) \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceArea]{minSurfaceArea} & Minimum area of a surface cell in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minLatentHeatFlux]{minLatentHeatFlux} & Minimum latent heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSensibleHeatFlux]{minSensibleHeatFlux} & Minimum sensible heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minLongWaveHeatFluxUp]{minLongWaveHeatFluxUp} & Minimum upwelling long wave heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minLongWaveHeatFluxDown]{minLongWaveHeatFluxDown} & Minimum downwelling long wave heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSeaIceHeatFlux]{minSeaIceHeatFlux} & Minimum sea ice heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minIcebergHeatFlux]{minIcebergHeatFlux} & Minimum iceberg heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minShortWaveHeatFlux]{minShortWaveHeatFlux} & Minimum short wave heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minEvaporationFlux]{minEvaporationFlux} & Minimum evaporation in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSeaIceFreshWaterFlux]{minSeaIceFreshWaterFlux} & Minimum sea ice melt rate in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minIcebergFreshWaterFlux]{minIcebergFreshWaterFlux} & Minimum iceberg melt rate in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minRiverRunoffFlux]{minRiverRunoffFlux} & Minimum river run off in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minIceRunoffFlux]{minIceRunoffFlux} & Minimum ice run off in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minRainFlux]{minRainFlux} & Minimum rain flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSnowFlux]{minSnowFlux} & Minimum snow flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSeaIceEnergy]{minSeaIceEnergy} & Minimum sea ice energy in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceThicknessFlux]{minSurfaceThicknessFlux} & Minimum surface thickness flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceTemperatureFlux]{minSurfaceTemperatureFlux} & Minimum surface temperature flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceSalinityFlux]{minSurfaceSalinityFlux} & Minimum surface salinity flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSeaIceSalinityFlux]{minSeaIceSalinityFlux} & Minimum sea ice salinity flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceWindStressMagnitude]{minSurfaceWindStressMagnitude} & Minimum wind stress magnitude in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minWindStressZonal]{minWindStressZonal} & Minimum zonal wind stress in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minWindStressMeridional]{minWindStressMeridional} & Minimum meridional wind stress in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSeaSurfacePressure]{minSeaSurfacePressure} & Minimum sea surface pressure in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceSSH]{minSurfaceSSH} & Minimum sea-surface height in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceTemperature]{minSurfaceTemperature} & Minimum surface temperature in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceSalinity]{minSurfaceSalinity} & Minimum surface salinity in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minBoundaryLayerDepth]{minBoundaryLayerDepth} & Minimum surface boundary layer depth in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceNetHeatFlux]{minSurfaceNetHeatFlux} & Minimum net surface heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceNetSalinitFlux]{minSurfaceNetSalinitFlux} & Minimum net surface salinity flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_minSurfaceNetFreshWaterFlux]{minSurfaceNetFreshWaterFlux} & Minimum net surface fresh water flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceMaskValue]{maxSurfaceMaskValue} & Maximum value of region mask (should always be 1 for valid regions) \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceArea]{maxSurfaceArea} & Maximum area of a surface cell in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxLatentHeatFlux]{maxLatentHeatFlux} & Maximum latent heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSensibleHeatFlux]{maxSensibleHeatFlux} & Maximum sensible heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxLongWaveHeatFluxUp]{maxLongWaveHeatFluxUp} & Maximum upwelling long wave heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxLongWaveHeatFluxDown]{maxLongWaveHeatFluxDown} & Maximum downwelling long wave heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSeaIceHeatFlux]{maxSeaIceHeatFlux} & Maximum sea ice heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxIcebergHeatFlux]{maxIcebergHeatFlux} & Maximum iceberg heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxShortWaveHeatFlux]{maxShortWaveHeatFlux} & Maximum short wave heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxEvaporationFlux]{maxEvaporationFlux} & Maximum evaporation in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSeaIceFreshWaterFlux]{maxSeaIceFreshWaterFlux} & Maximum sea ice melt rate in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxIcebergFreshWaterFlux]{maxIcebergFreshWaterFlux} & Maximum iceberg melt rate in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxRiverRunoffFlux]{maxRiverRunoffFlux} & Maximum river run off in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxIceRunoffFlux]{maxIceRunoffFlux} & Maximum ice run off in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxRainFlux]{maxRainFlux} & Maximum rain flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSnowFlux]{maxSnowFlux} & Maximum snow flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSeaIceEnergy]{maxSeaIceEnergy} & Maximum sea ice energy in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceThicknessFlux]{maxSurfaceThicknessFlux} & Maximum surface thickness flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceTemperatureFlux]{maxSurfaceTemperatureFlux} & Maximum surface temperature flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceSalinityFlux]{maxSurfaceSalinityFlux} & Maximum surface salinity flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSeaIceSalinityFlux]{maxSeaIceSalinityFlux} & Maximum sea ice salinity flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceWindStressMagnitude]{maxSurfaceWindStressMagnitude} & Maximum wind stress magnitude in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxWindStressZonal]{maxWindStressZonal} & Maximum zonal wind stress in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxWindStressMeridional]{maxWindStressMeridional} & Maximum meridional wind stress in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSeaSurfacePressure]{maxSeaSurfacePressure} & Maximum sea surface pressure in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceSSH]{maxSurfaceSSH} & Maximum sea-surface height \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceTemperature]{maxSurfaceTemperature} & Maximum surface temperature in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceSalinity]{maxSurfaceSalinity} & Maximum surface salinity in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxBoundaryLayerDepth]{maxBoundaryLayerDepth} & Maximum surface boundary layer depth in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceNetHeatFlux]{maxSurfaceNetHeatFlux} & Maximum net surface heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceNetSalinitFlux]{maxSurfaceNetSalinitFlux} & Maximum net surface salinity flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_maxSurfaceNetFreshWaterFlux]{maxSurfaceNetFreshWaterFlux} & Maximum net surface fresh water flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_sumSurfaceMaskValue]{sumSurfaceMaskValue} & Sum of region mask, represents total number of cells in region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceArea]{avgSurfaceArea} & Average area of a surface cell \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgLatentHeatFlux]{avgLatentHeatFlux} & Surface area-weighted average of latent heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSensibleHeatFlux]{avgSensibleHeatFlux} & Surface area-weighted average of sensible heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgLongWaveHeatFluxUp]{avgLongWaveHeatFluxUp} & Surface area-weighted average of upwelling long wave heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgLongWaveHeatFluxDown]{avgLongWaveHeatFluxDown} & Surface area-weighted average of downwelling long wave heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSeaIceHeatFlux]{avgSeaIceHeatFlux} & Surface area-weighted average of sea ice heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgIcebergHeatFlux]{avgIcebergHeatFlux} & Surface area-weighted average of iceberg heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgShortWaveHeatFlux]{avgShortWaveHeatFlux} & Surface area-weighted average of short wave heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgEvaporationFlux]{avgEvaporationFlux} & Surface area-weighted average of evaporation in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSeaIceFreshWaterFlux]{avgSeaIceFreshWaterFlux} & Surface area-weighted average of sea ice melt rate in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgIcebergFreshWaterFlux]{avgIcebergFreshWaterFlux} & Surface area-weighted average of iceberg melt rate in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgRiverRunoffFlux]{avgRiverRunoffFlux} & Surface area-weighted average of river run off in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgIceRunoffFlux]{avgIceRunoffFlux} & Surface area-weighted average of ice run off in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgRainFlux]{avgRainFlux} & Surface area-weighted average of rain flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSnowFlux]{avgSnowFlux} & Surface area-weighted average of snow flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSeaIceEnergy]{avgSeaIceEnergy} & Surface area-weighted average of sea ice energy in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceThicknessFlux]{avgSurfaceThicknessFlux} & Surface area-weighted average of surface thickness flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceTemperatureFlux]{avgSurfaceTemperatureFlux} & Surface area-weighted average of surface temperature flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceSalinityFlux]{avgSurfaceSalinityFlux} & Surface area-weighted average of surface salinity flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSeaIceSalinityFlux]{avgSeaIceSalinityFlux} & Surface area-weighted average of sea ice salinity flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceWindStressMagnitude]{avgSurfaceWindStressMagnitude} & Surface area-weighted average of wind stress magnitude in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgWindStressZonal]{avgWindStressZonal} & Surface area-weighted average of zonal wind stress in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgWindStressMeridional]{avgWindStressMeridional} & Surface area-weighted average of meridional wind stress in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSeaSurfacePressure]{avgSeaSurfacePressure} & Surface area-weighted average of sea surface pressure in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceSSH]{avgSurfaceSSH} & Surface area-weighted average of sea-surface height \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceTemperature]{avgSurfaceTemperature} & Surface area-weighted average of surface temperature in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceSalinity]{avgSurfaceSalinity} & Surface area-weighted average of surface salinity in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgBoundaryLayerDepth]{avgBoundaryLayerDepth} & Surface area-weighted average of surface boundary layer depth in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceNetHeatFlux]{avgSurfaceNetHeatFlux} & Surface area-weighted average of net surface heat flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceNetSalinitFlux]{avgSurfaceNetSalinitFlux} & Surface area-weighted average of net surface salinity flux in each region \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAM_avgSurfaceNetFreshWaterFlux]{avgSurfaceNetFreshWaterFlux} & Surface area-weighted average of net surface fresh water flux in each region \\
    \hline
\end{longtable}
\end{center}
}
\section[surfaceAreaWeightedAveragesAMScratch]{\hyperref[sec:var_sec_surfaceAreaWeightedAveragesAMScratch]{surfaceAreaWeightedAveragesAMScratch}}
\label{sec:var_tab_surfaceAreaWeightedAveragesAMScratch}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAMScratch_workMask]{workMask} & temporary array of 0 or 1 to mask data via multiplication \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAMScratch_workArray]{workArray} & temporary array to hold data to be analyzed \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAMScratch_workMin]{workMin} & temporary array to hold minimum values \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAMScratch_workMax]{workMax} & temporary array to hold maximum values \\
    \hline
    \hyperref[subsec:var_sec_surfaceAreaWeightedAveragesAMScratch_workSum]{workSum} & temporary array to hold sum of values \\
    \hline
\end{longtable}
\end{center}
}
\section[waterMassCensusAM]{\hyperref[sec:var_sec_waterMassCensusAM]{waterMassCensusAM}}
\label{sec:var_tab_waterMassCensusAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_waterMassCensusTemperatureValues]{waterMassCensusTemperature\-Values} & temperature values defining edges of temperature bins \\
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_waterMassCensusSalinityValues]{waterMassCensusSalinityValues} & salinity values defining edges of temperature bins \\
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_waterMassFractionalDistribution]{waterMassFractionalDistribution} & fraction of water volume contained within each temperature and salinity bin \\
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_potentialDensityOfTSDiagram]{potentialDensityOfTSDiagram} & volume-weighted potential density of each (T,S) bin \\
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_zPositionOfTSDiagram]{zPositionOfTSDiagram} & volume-weighted vertical position of each (T,S) bin \\
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_waterMassCensusTemperatureValuesRegion]{waterMassCensusTemperature\-ValuesRegion} & temperature values defining edges of temperature bins \\
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_waterMassCensusSalinityValuesRegion]{waterMassCensusSalinityValues\-Region} & salinity values defining edges of temperature bins \\
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_waterMassFractionalDistributionRegion]{waterMassFractionalDistribution\-Region} & fraction of water volume contained within each temperature and salinity bin \\
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_potentialDensityOfTSDiagramRegion]{potentialDensityOfTSDiagram\-Region} & volume-weighted potential density of each (T,S) bin \\
    \hline
    \hyperref[subsec:var_sec_waterMassCensusAM_zPositionOfTSDiagramRegion]{zPositionOfTSDiagramRegion} & volume-weighted vertical position of each (T,S) bin \\
    \hline
\end{longtable}
\end{center}
}
\section[layerVolumeWeightedAverageAM]{\hyperref[sec:var_sec_layerVolumeWeightedAverageAM]{layerVolumeWeightedAverageAM}}
\label{sec:var_tab_layerVolumeWeightedAverageAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerMaskValue]{minLayerMaskValue} & Minimum value of mask within region layer (should always be 1 for valid layers) \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerArea]{minLayerArea} & Minimum area of cell within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerThickness]{minLayerThickness} & Minimum thickness within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerDensity]{minLayerDensity} & Minimum in-situ density within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerPotentialDensity]{minLayerPotentialDensity} & Minimum potential density within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerBruntVaisalaFreqTop]{minLayerBruntVaisalaFreqTop} & Minimum Brunt Vaisala frequency within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerVelocityZonal]{minLayerVelocityZonal} & Minimum zonal velocity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerVelocityMeridional]{minLayerVelocityMeridional} & Minimum meridional velocity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerVertVelocityTop]{minLayerVertVelocityTop} & Minimum vertical velocity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerTemperature]{minLayerTemperature} & Minimum surface temperature within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerSalinity]{minLayerSalinity} & Minimum surface salinity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerKineticEnergyCell]{minLayerKineticEnergyCell} & Minimum kinetic energy within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerRelativeVorticityCell]{minLayerRelativeVorticityCell} & Minimum relative vorticity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerDivergence]{minLayerDivergence} & Minimum divergence within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerRelativeEnstrophyCell]{minLayerRelativeEnstrophyCell} & Minimum relative enstrophy within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerTemperatureHorAdv]{minLayerTemperatureHorAdv} & Minimum horizontal temperature advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerSalinityHorAdv]{minLayerSalinityHorAdv} & Minimum horizontal salinity advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerTemperatureVertAdv]{minLayerTemperatureVertAdv} & Minimum vertical temperature advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerSalinityVertAdv]{minLayerSalinityVertAdv} & Minimum vertical salinity advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerTemperatureSfcFlux]{minLayerTemperatureSfcFlux} & Minimum temperature surface flux tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerSalinitySfcFlux]{minLayerSalinitySfcFlux} & Minimum salinity surface flux tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerTemperatureSW]{minLayerTemperatureSW} & Minimum temperature short wave tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerTemperatureNL]{minLayerTemperatureNL} & Minimum temperature non local tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerSalinityNL]{minLayerSalinityNL} & Minimum salinity kpp non local tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerTemperatureVertMix]{minLayerTemperatureVertMix} & Minimum temperature vertical mixing within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minLayerSalinityVertMix]{minLayerSalinityVertMix} & Minimum salinity vertical mixing within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeMaskValue]{minVolumeMaskValue} & Minimum value of mask within region volume (should always be 1 for valid volumes) \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeArea]{minVolumeArea} & Minimum area of cell within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeThickness]{minVolumeThickness} & Minimum thickness within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeDensity]{minVolumeDensity} & Minimum in-situ density within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumePotentialDensity]{minVolumePotentialDensity} & Minimum potential density within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeBruntVaisalaFreqTop]{minVolumeBruntVaisalaFreqTop} & Minimum Brunt Vaisala frequency within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeVelocityZonal]{minVolumeVelocityZonal} & Minimum zonal velocity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeVelocityMeridional]{minVolumeVelocityMeridional} & Minimum meridional velocity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeVertVelocityTop]{minVolumeVertVelocityTop} & Minimum vertical velocity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeTemperature]{minVolumeTemperature} & Minimum surface temperature within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeSalinity]{minVolumeSalinity} & Minimum surface salinity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeKineticEnergyCell]{minVolumeKineticEnergyCell} & Minimum kinetic energy within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeRelativeVorticityCell]{minVolumeRelativeVorticityCell} & Minimum relative vorticity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeDivergence]{minVolumeDivergence} & Minimum divergence within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeRelativeEnstrophyCell]{minVolumeRelativeEnstrophyCell} & Minimum relative enstrophy within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeTemperatureHorAdv]{minVolumeTemperatureHorAdv} & Minimum horizontal temperature advection within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeSalinityHorAdv]{minVolumeSalinityHorAdv} & Minimum horizontal salinity advection within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeTemperatureVertAdv]{minVolumeTemperatureVertAdv} & Minimum vertical temperature advection within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeSalinityVertAdv]{minVolumeSalinityVertAdv} & Minimum vertical salinity advection within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeTemperatureSfcFlux]{minVolumeTemperatureSfcFlux} & Minimum temperature surface flux tend within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeSalinitySfcFlux]{minVolumeSalinitySfcFlux} & Minimum salinity surface flux tend within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeTemperatureSW]{minVolumeTemperatureSW} & {\bf \color{red} MISSING} \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeTemperatureNL]{minVolumeTemperatureNL} & Minimum temperature kpp non local tend within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeSalinityNL]{minVolumeSalinityNL} & Minimum salinity kpp non local tend within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeTemperatureVertMix]{minVolumeTemperatureVertMix} & Minimum temperature vertical mixing within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_minVolumeSalinityVertMix]{minVolumeSalinityVertMix} & Minimum salinity vertical mixing within region volumeMins \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerMaskValue]{maxLayerMaskValue} & Maximum value of mask within region layer (should always be 1 for valid layers) \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerArea]{maxLayerArea} & Maximum area of cell within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerThickness]{maxLayerThickness} & Maximum thickness within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerDensity]{maxLayerDensity} & Maximum in-situ density within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerPotentialDensity]{maxLayerPotentialDensity} & Maximum potential density within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerBruntVaisalaFreqTop]{maxLayerBruntVaisalaFreqTop} & Maximum Brunt Vaisala frequency within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerVelocityZonal]{maxLayerVelocityZonal} & Maximum zonal velocity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerVelocityMeridional]{maxLayerVelocityMeridional} & Maximum meridional velocity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerVertVelocityTop]{maxLayerVertVelocityTop} & Maximum vertical velocity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerTemperature]{maxLayerTemperature} & Maximum surface temperature within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerSalinity]{maxLayerSalinity} & Maximum surface salinity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerKineticEnergyCell]{maxLayerKineticEnergyCell} & Maximum kinetic energy within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerRelativeVorticityCell]{maxLayerRelativeVorticityCell} & Maximum relative vorticity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerDivergence]{maxLayerDivergence} & Maximum divergence within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerRelativeEnstrophyCell]{maxLayerRelativeEnstrophyCell} & Maximum relative enstrophy within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerTemperatureHorAdv]{maxLayerTemperatureHorAdv} & Maximum horizontal temperature advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerSalinityHorAdv]{maxLayerSalinityHorAdv} & Maximum horizontal salinity advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerTemperatureVertAdv]{maxLayerTemperatureVertAdv} & Maximum vertical temperature advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerSalinityVertAdv]{maxLayerSalinityVertAdv} & Maximum vertical salinity advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerTemperatureSfcFlux]{maxLayerTemperatureSfcFlux} & Maximum temperature surface flux tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerSalinitySfcFlux]{maxLayerSalinitySfcFlux} & Maximum salinity surface flux tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerTemperatureSW]{maxLayerTemperatureSW} & Maximum temperature short wave tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerTemperatureNL]{maxLayerTemperatureNL} & Maximum temperature non local tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerSalinityNL]{maxLayerSalinityNL} & Maximum salinity non local tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerTemperatureVertMix]{maxLayerTemperatureVertMix} & Maximum temperature vertical mixing within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxLayerSalinityVertMix]{maxLayerSalinityVertMix} & Maximum salinity vertical mixing within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeMaskValue]{maxVolumeMaskValue} & Maximum value of mask within region volume (should always be 1 for valid volumes) \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeArea]{maxVolumeArea} & Maximum area of cell within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeThickness]{maxVolumeThickness} & Maximum thickness within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeDensity]{maxVolumeDensity} & Maximum in-situ density within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumePotentialDensity]{maxVolumePotentialDensity} & Maximum potential density within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeBruntVaisalaFreqTop]{maxVolumeBruntVaisalaFreqTop} & Maximum Brunt Vaisala frequency within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeVelocityZonal]{maxVolumeVelocityZonal} & Maximum zonal velocity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeVelocityMeridional]{maxVolumeVelocityMeridional} & Maximum meridional velocity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeVertVelocityTop]{maxVolumeVertVelocityTop} & Maximum vertical velocity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeTemperature]{maxVolumeTemperature} & Maximum surface temperature within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeSalinity]{maxVolumeSalinity} & Maximum surface salinity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeKineticEnergyCell]{maxVolumeKineticEnergyCell} & Maximum kinetic energy within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeRelativeVorticityCell]{maxVolumeRelativeVorticityCell} & Maximum relative vorticity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeDivergence]{maxVolumeDivergence} & Maximum divergence within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeRelativeEnstrophyCell]{maxVolumeRelativeEnstrophy\-Cell} & Maximum relative enstrophy within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeTemperatureHorAdv]{maxVolumeTemperatureHorAdv} & Maximum horizontal temperature advection within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeSalinityHorAdv]{maxVolumeSalinityHorAdv} & Maximum horizontal salinity advection within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeTemperatureVertAdv]{maxVolumeTemperatureVertAdv} & Maximum vertical temperature advection within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeSalinityVertAdv]{maxVolumeSalinityVertAdv} & Maximum vertical salinity advection within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeTemperatureSfcFlux]{maxVolumeTemperatureSfcFlux} & Maximum temperature surface flux tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeSalinitySfcFlux]{maxVolumeSalinitySfcFlux} & Maximum salinity surface flux tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeTemperatureSW]{maxVolumeTemperatureSW} & Maximum temperature short wave tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeTemperatureNL]{maxVolumeTemperatureNL} & Maximum temperature non local tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeSalinityNL]{maxVolumeSalinityNL} & Maximum salinity non local tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeTemperatureVertMix]{maxVolumeTemperatureVertMix} & Maximum temperature vertical mixing within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_maxVolumeSalinityVertMix]{maxVolumeSalinityVertMix} & Maximum salinity vertical mixing within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_sumLayerMaskValue]{sumLayerMaskValue} & Sum value of mask within region volume (should always be greater than 0 for valid layer) \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerArea]{avgLayerArea} & Average area of cell within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerThickness]{avgLayerThickness} & Average thickness within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerDensity]{avgLayerDensity} & Average in-situ density within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerPotentialDensity]{avgLayerPotentialDensity} & Average potential density within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerBruntVaisalaFreqTop]{avgLayerBruntVaisalaFreqTop} & Average Brunt Vaisala frequency within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerVelocityZonal]{avgLayerVelocityZonal} & Average zonal velocity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerVelocityMeridional]{avgLayerVelocityMeridional} & Average meridional velocity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerVertVelocityTop]{avgLayerVertVelocityTop} & Average vertical velocity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerTemperature]{avgLayerTemperature} & Average surface temperature within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerSalinity]{avgLayerSalinity} & Average surface salinity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerKineticEnergyCell]{avgLayerKineticEnergyCell} & Average kinetic energy within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerRelativeVorticityCell]{avgLayerRelativeVorticityCell} & Average relative vorticity within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerDivergence]{avgLayerDivergence} & Average divergence within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerRelativeEnstrophyCell]{avgLayerRelativeEnstrophyCell} & Average relative enstrophy within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerTemperatureHorAdv]{avgLayerTemperatureHorAdv} & Average horizontal temperature advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerSalinityHorAdv]{avgLayerSalinityHorAdv} & Average horizontal salinity advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerTemperatureVertAdv]{avgLayerTemperatureVertAdv} & Average vertical temperature advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerSalinityVertAdv]{avgLayerSalinityVertAdv} & Average vertical salinity advection within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerTemperatureSfcFlux]{avgLayerTemperatureSfcFlux} & Average temperature surface flux tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerSalinitySfcFlux]{avgLayerSalinitySfcFlux} & Average salinity surface flux tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerTemperatureSW]{avgLayerTemperatureSW} & Average temperature shortwave tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerTemperatureNL]{avgLayerTemperatureNL} & Average temperature non local tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerSalinityNL]{avgLayerSalinityNL} & Average salinity non local tend within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerTemperatureVertMix]{avgLayerTemperatureVertMix} & Average temperature vertical mixing within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgLayerSalinityVertMix]{avgLayerSalinityVertMix} & Average salinity vertical mixing within region layer \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_sumVolumeMaskValue]{sumVolumeMaskValue} & Sum value of mask within region volume (should always be greater than 0 for valid volumes) \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeArea]{avgVolumeArea} & Average area of cell within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeThickness]{avgVolumeThickness} & Average thickness within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeDensity]{avgVolumeDensity} & Average in-situ density within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumePotentialDensity]{avgVolumePotentialDensity} & Average potential density within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeBruntVaisalaFreqTop]{avgVolumeBruntVaisalaFreqTop} & Average Brunt Vaisala frequency within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeVelocityZonal]{avgVolumeVelocityZonal} & Average zonal velocity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeVelocityMeridional]{avgVolumeVelocityMeridional} & Average meridional velocity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeVertVelocityTop]{avgVolumeVertVelocityTop} & Average vertical velocity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeTemperature]{avgVolumeTemperature} & Average surface temperature within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeSalinity]{avgVolumeSalinity} & Average surface salinity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeKineticEnergyCell]{avgVolumeKineticEnergyCell} & Average kinetic energy within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeRelativeVorticityCell]{avgVolumeRelativeVorticityCell} & Average relative vorticity within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeDivergence]{avgVolumeDivergence} & Average divergence within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeRelativeEnstrophyCell]{avgVolumeRelativeEnstrophyCell} & Average relative enstrophy within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeTemperatureHorAdv]{avgVolumeTemperatureHorAdv} & Average horizontal temperature advection within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeSalinityHorAdv]{avgVolumeSalinityHorAdv} & Average horizontal salinity advection within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeTemperatureVertAdv]{avgVolumeTemperatureVertAdv} & Average vertical temperature advection within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeSalinityVertAdv]{avgVolumeSalinityVertAdv} & Average vertical salinity advection within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeTemperatureSfcFlux]{avgVolumeTemperatureSfcFlux} & Average temperature surface flux tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeSalinitySfcFlux]{avgVolumeSalinitySfcFlux} & Average salinity surface flux tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeTemperatureSW]{avgVolumeTemperatureSW} & Average temperature shortwave tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeTemperatureNL]{avgVolumeTemperatureNL} & Average temperature non local tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeSalinitySfcNL]{avgVolumeSalinitySfcNL} & Average salinity non local tend within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeTemperatureVertMix]{avgVolumeTemperatureVertMix} & Average temperature vertical mixing within region volume \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAM_avgVolumeSalinityVertMix]{avgVolumeSalinityVertMix} & Average salinity vertical mixing within region volume \\
    \hline
\end{longtable}
\end{center}
}
\section[layerVolumeWeightedAverageAMScratch]{\hyperref[sec:var_sec_layerVolumeWeightedAverageAMScratch]{layerVolumeWeightedAverageAMScratch}}
\label{sec:var_tab_layerVolumeWeightedAverageAMScratch}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAMScratch_workMaskLayerVolume]{workMaskLayerVolume} & temporary array of 0 or 1 to mask data via multiplication \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAMScratch_workArrayLayerVolume]{workArrayLayerVolume} & temporary array to hold data to be analyzed \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAMScratch_workMinLayerVolume]{workMinLayerVolume} & temporary array to hold minimum values \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAMScratch_workMaxLayerVolume]{workMaxLayerVolume} & temporary array to hold maximum values \\
    \hline
    \hyperref[subsec:var_sec_layerVolumeWeightedAverageAMScratch_workSumLayerVolume]{workSumLayerVolume} & temporary array to hold sum of values \\
    \hline
\end{longtable}
\end{center}
}
\section[zonalMeanAM]{\hyperref[sec:var_sec_zonalMeanAM]{zonalMeanAM}}
\label{sec:var_tab_zonalMeanAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_zonalMeanAM_binCenterZonalMean]{binCenterZonalMean} & Central coordinate of zonal mean bin, either in latitude or y, for plotting. \\
    \hline
    \hyperref[subsec:var_sec_zonalMeanAM_binBoundaryZonalMean]{binBoundaryZonalMean} & Coordinate of lower edge of zonal mean bin, either in latitude or y, for plotting. \\
    \hline
    \hyperref[subsec:var_sec_zonalMeanAM_velocityZonalZonalMean]{velocityZonalZonalMean} & Zonal mean of component of horizontal velocity in the eastward direction \\
    \hline
    \hyperref[subsec:var_sec_zonalMeanAM_velocityMeridionalZonalMean]{velocityMeridionalZonalMean} & Zonal mean of component of horizontal velocity in the northward direction \\
    \hline
    \hyperref[subsec:var_sec_zonalMeanAM_temperatureZonalMean]{temperatureZonalMean} & Zonal mean of potential temperature \\
    \hline
    \hyperref[subsec:var_sec_zonalMeanAM_salinityZonalMean]{salinityZonalMean} & Zonal mean of salinity in grams salt per kilogram seawater \\
    \hline
    \hyperref[subsec:var_sec_zonalMeanAM_tracer1ZonalMean]{tracer1ZonalMean} & Zonal mean of tracer \\
    \hline
\end{longtable}
\end{center}
}
\section[okuboWeissScratch]{\hyperref[sec:var_sec_okuboWeissScratch]{okuboWeissScratch}}
\label{sec:var_tab_okuboWeissScratch}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_okuboWeissScratch_thresholdedOkuboWeiss]{thresholdedOkuboWeiss} & Thresholded Okubo-Weiss value \\
    \hline
    \hyperref[subsec:var_sec_okuboWeissScratch_velocityGradient]{velocityGradient} & Gradient of velocity field \\
    \hline
    \hyperref[subsec:var_sec_okuboWeissScratch_shearAndStrain]{shearAndStrain} & Shear and strain \\
    \hline
    \hyperref[subsec:var_sec_okuboWeissScratch_lambda1]{lambda1} & Lambda 1, first eigenvalue of 2d strain rate tensor \\
    \hline
    \hyperref[subsec:var_sec_okuboWeissScratch_lambda2]{lambda2} & Lambda 2, second eigenvalue of 2d strain rate tensor \\
    \hline
    \hyperref[subsec:var_sec_okuboWeissScratch_lambda2R3]{lambda2R3} & Lambda 2, second eigenvalue of full 3d strain rate tensor \\
    \hline
\end{longtable}
\end{center}
}
\section[okuboWeissAM]{\hyperref[sec:var_sec_okuboWeissAM]{okuboWeissAM}}
\label{sec:var_tab_okuboWeissAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_okuboWeissAM_okuboWeiss]{okuboWeiss} & The Okubo-Weiss value \\
    \hline
    \hyperref[subsec:var_sec_okuboWeissAM_eddyID]{eddyID} & ID of eddy connected component \\
    \hline
    \hyperref[subsec:var_sec_okuboWeissAM_vorticity]{vorticity} & Vorticity \\
    \hline
\end{longtable}
\end{center}
}
\section[meridionalHeatTransportAM]{\hyperref[sec:var_sec_meridionalHeatTransportAM]{meridionalHeatTransportAM}}
\label{sec:var_tab_meridionalHeatTransportAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_meridionalHeatTransportAM_binBoundaryMerHeatTrans]{binBoundaryMerHeatTrans} & Coordinate of southern edge of meridional heat transport bin, either in latitude or y, for plotting. \\
    \hline
    \hyperref[subsec:var_sec_meridionalHeatTransportAM_meridionalHeatTransportLatZ]{meridionalHeatTransportLatZ} & Northward heat transport at locations defined at the binBoundaryMerHeatTrans coordinates by vertical level. \\
    \hline
    \hyperref[subsec:var_sec_meridionalHeatTransportAM_merHeatTransLatZRegion]{merHeatTransLatZRegion} & Northward heat transport by vertical level and region. \\
    \hline
    \hyperref[subsec:var_sec_meridionalHeatTransportAM_meridionalHeatTransportLat]{meridionalHeatTransportLat} & Northward heat transport at locations defined at the binBoundaryMerHeatTrans coordinates. \\
    \hline
    \hyperref[subsec:var_sec_meridionalHeatTransportAM_merHeatTransLatRegion]{merHeatTransLatRegion} & Northward heat transport at locations defined at the binBoundaryMerHeatTrans coordinates, by region. \\
    \hline
    \hyperref[subsec:var_sec_meridionalHeatTransportAM_minMaxLatRegionMHT]{minMaxLatRegionMHT} & Coordinates of the southern and northern edge of each region (for drawing). \\
    \hline
\end{longtable}
\end{center}
}
\section[testComputeIntervalAM]{\hyperref[sec:var_sec_testComputeIntervalAM]{testComputeIntervalAM}}
\label{sec:var_tab_testComputeIntervalAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_testComputeIntervalAM_testComputeIntervalCounter]{testComputeIntervalCounter} & number of times test\_compute\_interval has been called \\
    \hline
\end{longtable}
\end{center}
}
\section[highFrequencyOutputAM]{\hyperref[sec:var_sec_highFrequencyOutputAM]{highFrequencyOutputAM}}
\label{sec:var_tab_highFrequencyOutputAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_kineticEnergyAtSurface]{kineticEnergyAtSurface} & kinetic energy at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_vertGMvelocitySFC]{vertGMvelocitySFC} & vertical velocity due to GM parameterization \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_vertTransportVelocitySFC]{vertTransportVelocitySFC} & vertical velocity due to normal transport velocity divergence \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_vertVelSFC]{vertVelSFC} & vertical velocity due to normal velocity divergence \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_vertGMvelocityAt250m]{vertGMvelocityAt250m} & vertical velocity due to GM parameterization at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_vertTransportVelocityAt250m]{vertTransportVelocityAt250m} & vertical velocity due to normal transport velocity divergence at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_vertVelAt250m]{vertVelAt250m} & vertical velocity due to normal velocity divergence at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalVelAtSFC]{normalVelAtSFC} & normal velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalVelAt250m]{normalVelAt250m} & normal velocity at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalVelAtBottom]{normalVelAtBottom} & normal velocity at approximately Bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialVelAtSFC]{tangentialVelAtSFC} & tangential velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialVelAt250m]{tangentialVelAt250m} & tangential velocity at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialVelAtBottom]{tangentialVelAtBottom} & tangential velocity at approximately Bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalVelAtSFC]{zonalVelAtSFC} & zonal velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalVelAt250m]{zonalVelAt250m} & zonal velocity at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalVelAtBottom]{zonalVelAtBottom} & zonal velocity at approximately Bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalAreaWeightedCellVelAtSFC]{zonalAreaWeightedCellVelAtSFC} & area-weighted cell zonal velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalAreaWeightedCellVelAt250m]{zonalAreaWeightedCellVel\-At250m} & area-weighted cell zonal velocity at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalAreaWeightedCellVelAtBottom]{zonalAreaWeightedCellVelAt\-Bottom} & area-weighted cell zonal velocity at approximately Bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalVelAtSFC]{meridionalVelAtSFC} & meridional velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalVelAt250m]{meridionalVelAt250m} & meridional velocity at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalVelAtBottom]{meridionalVelAtBottom} & meridional velocity at approximately Bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalAreaWeightedCellVelAtSFC]{meridionalAreaWeightedCellVel\-AtSFC} & area-weighted cell meridional velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalAreaWeightedCellVelAt250m]{meridionalAreaWeightedCellVel\-At250m} & area-weighted cell meridional velocity at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalAreaWeightedCellVelAtBottom]{meridionalAreaWeightedCellVel\-AtBottom} & area-weighted cell meridional velocity at approximately Bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalBarotropicVel]{normalBarotropicVel} & normal barotropic velocity \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialBarotropicVel]{tangentialBarotropicVel} & tangential barotropic velocity \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalBarotropicVel]{zonalBarotropicVel} & zonal barotropic velocity \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalBarotropicVel]{meridionalBarotropicVel} & meridional barotropic velocity \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalBaroclinicVelAtSFC]{normalBaroclinicVelAtSFC} & normal baroclinic velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalBaroclinicVelAt250m]{normalBaroclinicVelAt250m} & normal baroclinic velocity at 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalBaroclinicVelAtBottom]{normalBaroclinicVelAtBottom} & normal baroclinic velocity at bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialBaroclinicVelAtSFC]{tangentialBaroclinicVelAtSFC} & tangential baroclinic velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialBaroclinicVelAt250m]{tangentialBaroclinicVelAt250m} & tangential baroclinic velocity at 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialBaroclinicVelAtBottom]{tangentialBaroclinicVelAtBottom} & tangential baroclinic velocity at bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalBaroclinicVelAtSFC]{zonalBaroclinicVelAtSFC} & zonal baroclinic velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalBaroclinicVelAt250m]{zonalBaroclinicVelAt250m} & zonal baroclinic velocity at 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalBaroclinicVelAtBottom]{zonalBaroclinicVelAtBottom} & zonal baroclinic velocity at bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalBaroclinicVelAtSFC]{meridionalBaroclinicVelAtSFC} & meridional baroclinic velocity at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalBaroclinicVelAt250m]{meridionalBaroclinicVelAt250m} & meridional baroclinic velocity at 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalBaroclinicVelAtBottom]{meridionalBaroclinicVelAt\-Bottom} & meridional baroclinic velocity at bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalGMBolusVelAtSFC]{normalGMBolusVelAtSFC} & normal Bolus velocity in Gent-McWilliams eddy parameterization at the surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalGMBolusVelAt250m]{normalGMBolusVelAt250m} & normal Bolus velocity in Gent-McWilliams eddy parameterization at 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_normalGMBolusVelAtBottom]{normalGMBolusVelAtBottom} & normal Bolus velocity in Gent-McWilliams eddy parameterization at the bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialGMBolusVelAtSFC]{tangentialGMBolusVelAtSFC} & tangential Bolus velocity in Gent-McWilliams eddy parameterization at the surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialGMBolusVelAt250m]{tangentialGMBolusVelAt250m} & tangential Bolus velocity in Gent-McWilliams eddy parameterization at 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_tangentialGMBolusVelAtBottom]{tangentialGMBolusVelAtBottom} & tangential Bolus velocity in Gent-McWilliams eddy parameterization at the bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalGMBolusVelAtSFC]{zonalGMBolusVelAtSFC} & zonal Bolus velocity in Gent-McWilliams eddy parameterization at the surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalGMBolusVelAt250m]{zonalGMBolusVelAt250m} & zonal Bolus velocity in Gent-McWilliams eddy parameterization at 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_zonalGMBolusVelAtBottom]{zonalGMBolusVelAtBottom} & zonal Bolus velocity in Gent-McWilliams eddy parameterization at the bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalGMBolusVelAtSFC]{meridionalGMBolusVelAtSFC} & meridional Bolus velocity in Gent-McWilliams eddy parameterization at the surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalGMBolusVelAt250m]{meridionalGMBolusVelAt250m} & meridional Bolus velocity in Gent-McWilliams eddy parameterization at 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_meridionalGMBolusVelAtBottom]{meridionalGMBolusVelAtBottom} & meridional Bolus velocity in Gent-McWilliams eddy parameterization at the bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_BruntVaisalaFreqTopAtSFC]{BruntVaisalaFreqTopAtSFC} & Brunt Vaisala Frequency at surface \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_BruntVaisalaFreqTopAt250m]{BruntVaisalaFreqTopAt250m} & Brunt Vaisala Frequency at approximately 250m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_BruntVaisalaFreqTopAtBottom]{BruntVaisalaFreqTopAtBottom} & Brunt Vaisala Frequency at approximately Bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_kineticEnergyAt250m]{kineticEnergyAt250m} & kinetic energy at a depth of approximately 250 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_barotropicSpeed]{barotropicSpeed} & speed = sqrt(2*ke), where kinetic energy is computed from barotropic velocity = sum(h*u)/sum(h) over the full depth of an edge \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_columnIntegratedSpeed]{columnIntegratedSpeed} & speed = sum(h*sqrt(2*ke)), where ke is kineticEnergyCell and the sum is over the full column at cell centers. \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_relativeVorticityAt250m]{relativeVorticityAt250m} & relative vorticity at cell centers at a depth of approximately 250 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_divergenceAt250m]{divergenceAt250m} & divergence at cell centers at a depth of approximately 250 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_divergenceTransportVelAt250m]{divergenceTransportVelAt250m} & divergence of transport velocity at cell centers at a depth of approximately 250 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_relativeVorticityVertexAt250m]{relativeVorticityVertexAt250m} & relative vorticity at cell vertices at a depth of approximately 250 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_temperatureAtSurface]{temperatureAtSurface} & ocean temperature at top layer \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_salinityAtSurface]{salinityAtSurface} & salinity at top layer \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_temperatureAt250m]{temperatureAt250m} & ocean temperature at 250 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_salinityAt250m]{salinityAt250m} & salinity at 250 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_temperatureAtBottom]{temperatureAtBottom} & ocean temperature at bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_salinityAtBottom]{salinityAtBottom} & salinity at bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_kineticEnergyAtBottom]{kineticEnergyAtBottom} & kinetic energy at cell centers at bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_relativeVorticityAtBottom]{relativeVorticityAtBottom} & relative vorticity at cell centers at bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_divergenceAtBottom]{divergenceAtBottom} & divergence at cell centers at bottom \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_temperatureAvgTopto0100]{temperatureAvgTopto0100} & ocean temperature averaged between surface and 100 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_salinityAvgTopto0100]{salinityAvgTopto0100} & salinity averaged between surface and 100 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_temperatureAvg0100to0250]{temperatureAvg0100to0250} & ocean temperature averaged between surface and 100 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_salinityAvg0100to0250]{salinityAvg0100to0250} & salinity averaged between surface and 100 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_temperatureAvg0250to0700]{temperatureAvg0250to0700} & ocean temperature averaged between surface and 100 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_salinityAvg0250to0700]{salinityAvg0250to0700} & salinity averaged between surface and 100 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_temperatureAvg0700to2000]{temperatureAvg0700to2000} & ocean temperature averaged between surface and 100 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_salinityAvg0700to2000]{salinityAvg0700to2000} & salinity averaged between surface and 100 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_temperatureAvg2000toBottom]{temperatureAvg2000toBottom} & ocean temperature averaged between surface and 100 m \\
    \hline
    \hyperref[subsec:var_sec_highFrequencyOutputAM_salinityAvg2000toBottom]{salinityAvg2000toBottom} & salinity averaged between surface and 100 m \\
    \hline
\end{longtable}
\end{center}
}
\section[timeFiltersAM]{\hyperref[sec:var_sec_timeFiltersAM]{timeFiltersAM}}
\label{sec:var_tab_timeFiltersAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_normalVelocityLowPass]{normalVelocityLowPass} & Low-pass filtered normal velocity. \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_normalVelocityHighPass]{normalVelocityHighPass} & High-pass filtered normal velocity. \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_normalVelocityFilterTest]{normalVelocityFilterTest} & normalVelocityTest (for testing purposes). \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityZonalLowPass]{velocityZonalLowPass} & Low-pass time filtered component of horizontal velocity in the eastward direction \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityMeridionalLowPass]{velocityMeridionalLowPass} & Low-pass time filtered component of horizontal velocity in the northward direction \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityZonalHighPass]{velocityZonalHighPass} & High-pass time filtered component of horizontal velocity in the eastward direction \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityMeridionalHighPass]{velocityMeridionalHighPass} & High-pass time filtered component of horizontal velocity in the northward direction \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityXLowPass]{velocityXLowPass} & Low-pass time filtered component of horizontal velocity in the x-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityYLowPass]{velocityYLowPass} & Low-pass time filtered component of horizontal velocity in the x-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityZLowPass]{velocityZLowPass} & Low-pass time filtered component of horizontal velocity in the x-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityXHighPass]{velocityXHighPass} & High-pass time filtered component of horizontal velocity in the x-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityYHighPass]{velocityYHighPass} & High-pass time filtered component of horizontal velocity in the x-direction (cartesian) \\
    \hline
    \hyperref[subsec:var_sec_timeFiltersAM_velocityZHighPass]{velocityZHighPass} & High-pass time filtered component of horizontal velocity in the x-direction (cartesian) \\
    \hline
\end{longtable}
\end{center}
}
\section[lagrPartTrackRegions]{\hyperref[sec:var_sec_lagrPartTrackRegions]{lagrPartTrackRegions}}
\label{sec:var_tab_lagrPartTrackRegions}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackRegions_resetOutsideRegionMaskValue1]{resetOutsideRegionMaskValue1} & Mask for particle resets that leave this particular region (specified by 1) \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackRegions_resetInsideRegionMaskValue1]{resetInsideRegionMaskValue1} & Mask for particle resets that enter this particular region (specified by 1) \\
    \hline
\end{longtable}
\end{center}
}
\section[lagrPartTrackScalars]{\hyperref[sec:var_sec_lagrPartTrackScalars]{lagrPartTrackScalars}}
\label{sec:var_tab_lagrPartTrackScalars}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScalars_globalResetTimeValue]{globalResetTimeValue} & Time in s for a global reset. \\
    \hline
\end{longtable}
\end{center}
}
\section[lagrPartTrackFields]{\hyperref[sec:var_sec_lagrPartTrackFields]{lagrPartTrackFields}}
\label{sec:var_tab_lagrPartTrackFields}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackFields_uVertexVelocity]{uVertexVelocity} & recostructed u horizontal velocity at vertices \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackFields_vVertexVelocity]{vVertexVelocity} & recostructed v horizontal velocity at vertices \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackFields_wVertexVelocity]{wVertexVelocity} & recostructed w horizontal velocity at vertices \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackFields_buoyancy]{buoyancy} & buoyancy values at cell mid points, currently proxy for density \\
    \hline
\end{longtable}
\end{center}
}
\section[lagrPartTrackCells]{\hyperref[sec:var_sec_lagrPartTrackCells]{lagrPartTrackCells}}
\label{sec:var_tab_lagrPartTrackCells}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackCells_cellOwnerBlock]{cellOwnerBlock} & designates ownership of cell in terms of computational block \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackCells_filteredVelocityW]{filteredVelocityW} & filtered u horizontal velocity at cells \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackCells_filteredVelocityV]{filteredVelocityV} & filtered v horizontal velocity at cells \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackCells_filteredVelocityU]{filteredVelocityU} & filtered w horizontal velocity at cells \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackCells_buoyancySurfaceVelocityZonal]{buoyancySurfaceVelocityZonal} & horizontal zonal velocity on buoyancy surface \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackCells_buoyancySurfaceVelocityMeridional]{buoyancySurfaceVelocity\-Meridional} & horizontal meridional velocity on buoyancy surface \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackCells_buoyancySurfaceDepth]{buoyancySurfaceDepth} & depth of buoyancy surface \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackCells_buoyancySurfaceValues]{buoyancySurfaceValues} & definition of buoyancy surfaces in terms of potential density \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackCells_wachspressAreaB]{wachspressAreaB} & cached polygon subarea B\_i used in Wachspess calculation \\
    \hline
\end{longtable}
\end{center}
}
\section[lagrPartTrackHalo]{\hyperref[sec:var_sec_lagrPartTrackHalo]{lagrPartTrackHalo}}
\label{sec:var_tab_lagrPartTrackHalo}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_ioBlock]{ioBlock} & input / output Proc for particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_currentBlock]{currentBlock} & current block a particle is on \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_currentCell]{currentCell} & current local cell a particle is on \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_currentCellGlobalID]{currentCellGlobalID} & current global cell a particle is on \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_indexToParticleID]{indexToParticleID} & designates global ID for a particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_xParticle]{xParticle} & x location of horizontal particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_yParticle]{yParticle} & y location of horizontal particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_zParticle]{zParticle} & z location of horizontal particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_lonParticle]{lonParticle} & longitude location of horizontal particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_latParticle]{latParticle} & latitude location of horizontal particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_zLevelParticle]{zLevelParticle} & z-level for vertical elevation of particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_xParticleReset]{xParticleReset} & reset x location of horizontal particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_yParticleReset]{yParticleReset} & reset y location of horizontal particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_zParticleReset]{zParticleReset} & reset z location of horizontal particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_zLevelParticleReset]{zLevelParticleReset} & reset z-level for vertical elevation of particle position \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_currentBlockReset]{currentBlockReset} & reset block for a particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_currentCellReset]{currentCellReset} & reset cell for a particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_timeSinceReset]{timeSinceReset} & time (in seconds) since last particle reset \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_resetTime]{resetTime} & reset timer (in seconds) for particles \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_numTimesReset]{numTimesReset} & flag to specify how many times the particle was reset \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_verticalTreatment]{verticalTreatment} & select type of vertical treatment to be used, with possible\_values='indexLevel','fixedZLevel','passiveFloat','buoyancySurface','argoFloat' (ENUM) \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_indexLevel]{indexLevel} & 0 if particle is fixed, or index level if particle is free-floating \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_dtParticle]{dtParticle} & Any positive real value, but limited by CFL condition. \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_buoyancyParticle]{buoyancyParticle} & buoyancy values for particle, currently proxy for density \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_transfered]{transfered} & flag to monitor if the particle was transfered \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particleTemperature]{particleTemperature} & sampled temperature for particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particleSalinity]{particleSalinity} & sampled salinity for particle in grams salt per kilogram seawater \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particleDIC]{particleDIC} & sampled dissolved inorganic carbon for particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particleALK]{particleALK} & sampled alkalinity for particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particlePO4]{particlePO4} & sampled dissolved inorganic phosphate for particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particleNO3]{particleNO3} & sampled dissolved inorganic nitrate for particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particleSiO3]{particleSiO3} & sampled dissolved inorganic silicate for particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particleNH4]{particleNH4} & sampled dissolved inorganic ammonia for particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particleFe]{particleFe} & sampled dissolved inorganic iron for particle \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackHalo_particleO2]{particleO2} & sampled dissolved oxygen for particle \\
    \hline
\end{longtable}
\end{center}
}
\section[lagrPartTrackScratch]{\hyperref[sec:var_sec_lagrPartTrackScratch]{lagrPartTrackScratch}}
\label{sec:var_tab_lagrPartTrackScratch}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_ucReconstructX]{ucReconstructX} & reconstructed cell center velocity- x component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_ucReconstructY]{ucReconstructY} & reconstructed cell center velocity- y component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_ucReconstructZ]{ucReconstructZ} & reconstructed cell center velocity- z component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_ucTemp]{ucTemp} & cell velocity \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_ucX]{ucX} & cell velocity- x component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_ucY]{ucY} & cell velocity- y component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_ucZ]{ucZ} & cell velocity- z component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_uvX]{uvX} & vertex velocity- x component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_uvY]{uvY} & vertex velocity- y component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_uvZ]{uvZ} & vertex velocity- z component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_ucReconstructMeridional]{ucReconstructMeridional} & reconstructed cell center velocity- meridional component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_ucReconstructZonal]{ucReconstructZonal} & reconstructed cell center velocity- zonal component \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_boundaryVertexGlobal]{boundaryVertexGlobal} & Mask for determining boundary vertices, but global. A boundary vertex has at least one inactive cell neighboring it. \\
    \hline
    \hyperref[subsec:var_sec_lagrPartTrackScratch_boundaryCellGlobal]{boundaryCellGlobal} & Mask for determining boundary cells, but global. A boundary cell has at least one inactive cell neighboring it. \\
    \hline
\end{longtable}
\end{center}
}
\section[eliassenPalmAM]{\hyperref[sec:var_sec_eliassenPalmAM]{eliassenPalmAM}}
\label{sec:var_tab_eliassenPalmAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_potentialDensityMidRef]{potentialDensityMidRef} & Potential density target values of buoyancy coordinate layers \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_potentialDensityTopRef]{potentialDensityTopRef} & Potential density at top of buoyancy coordinate layers \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_buoyancyMidRef]{buoyancyMidRef} & Buoyancy of buoyancy coordinate layers \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_buoyancyInterfaceRef]{buoyancyInterfaceRef} & Buoyancy at interfaces of buoyancy coordinate layers \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_buoyancyMaskEA]{buoyancyMaskEA} & ensemble average of the buoyancy mask \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_sigmaEA]{sigmaEA} & Inverse of the derivative of buoyancy wrt z, or thickness per unit buoyancy, aka thickness, in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_nSamplesEA]{nSamplesEA} & Number of samples used in the ensamble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_heightMidBuoyCoorEA]{heightMidBuoyCoorEA} & z-coordinate of each buoyancy layer, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_montgPotGradZonalEA]{montgPotGradZonalEA} & Zonal gradient of montgomery potential at cell center in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_montgPotGradMeridEA]{montgPotGradMeridEA} & Meridional gradient of montgomery potential at cell center in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_heightMidBuoyCoorSqEA]{heightMidBuoyCoorSqEA} & z-coordinate of each buoyancy layer, squared, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_montgPotBuoyCoorEA]{montgPotBuoyCoorEA} & Montgomery potential in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_heightMGradZonalEA]{heightMGradZonalEA} & Height times zonal gradient of Montgomery potential in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_heightMGradMeridEA]{heightMGradMeridEA} & Height times meridional gradient of Montgomery potential in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_usigmaEA]{usigmaEA} & Zonal velocity times sigma, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_vsigmaEA]{vsigmaEA} & Meridional velocity times sigma, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_varpisigmaEA]{varpisigmaEA} & Vertical velocity in buoyancy coordinates times sigma, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_uusigmaEA]{uusigmaEA} & Zonal velocity times zonal velocity times sigma, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_vvsigmaEA]{vvsigmaEA} & Meridional velocity times meridional velocity times sigma, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_uvsigmaEA]{uvsigmaEA} & Zonal velocity times meridional velocity times sigma, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_uvarpisigmaEA]{uvarpisigmaEA} & Zonal velocity times vertical velocity in buoyancy coordinates times sigma, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_vvarpisigmaEA]{vvarpisigmaEA} & Meridional velocity times vertical velocity in buoyancy coordinates times sigma, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_uTWA]{uTWA} & Zonal velocity, thickness weighted \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_vTWA]{vTWA} & Meridional velocity, thickness weighted \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_varpiTWA]{varpiTWA} & Vertical velocity, thickness weighted \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_duTWAdz]{duTWAdz} & Derivative of thickness weighted zonal velocity with respect to z (vertical coordinate). \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_dvTWAdz]{dvTWAdz} & Derivative of thickness weighted meridional velocity with respect to z (vertical coordinate). \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_EPFT]{EPFT} & Eliassen-Palm flux tensor \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_uuTWACorr]{uuTWACorr} & Thickness-weighted averaged eddy u-u correlation. \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_vvTWACorr]{vvTWACorr} & Thickness-weighted averaged eddy v-v correlation. \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_uvTWACorr]{uvTWACorr} & Thickness-weighted averaged eddy u-v correlation. \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_epeTWA]{epeTWA} & Thickness-weighted averaged eddy potential energy. \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_eddyFormDragZonal]{eddyFormDragZonal} & Thickness-weighted averaged eddy form drag in x \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_eddyFormDragMerid]{eddyFormDragMerid} & Thickness-weighted averaged eddy form drag in y \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_divEPFT]{divEPFT} & Divergence of the Eliassen-Palm flux tensor, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_divEPFT1]{divEPFT1} & First component of the divergence of the Eliassen-Palm flux tensor, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_divEPFT2]{divEPFT2} & Second component of the divergence of the Eliassen-Palm flux tensor, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_divEPFTshear1]{divEPFTshear1} & First component of divergence of shear components of the Eliassen-Palm flux tensor, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_divEPFTshear2]{divEPFTshear2} & Second component of divergence of shear components of the Eliassen-Palm flux tensor, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_divEPFTdrag1]{divEPFTdrag1} & First component of divergence of form drag components of the Eliassen-Palm flux tensor, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_divEPFTdrag2]{divEPFTdrag2} & Second component of divergence of form drag components of the Eliassen-Palm flux tensor, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_ErtelPVFlux]{ErtelPVFlux} & Ertel potential vorticity flux in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_ErtelPVFlux1]{ErtelPVFlux1} & First component of the Ertel potential vorticity flux in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_ErtelPVFlux2]{ErtelPVFlux2} & Second component of the Ertel potential vorticity flux in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_ErtelPVTendency]{ErtelPVTendency} & Tendency of Ertel PV due to divergence of eddy PV fluxes \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_ErtelPV]{ErtelPV} & Ertel PV on buoyancy surfaces \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_ErtelPVGradZonal]{ErtelPVGradZonal} & Ertel PV on buoyancy surfaces \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAM_ErtelPVGradMerid]{ErtelPVGradMerid} & Ertel PV on buoyancy surfaces \\
    \hline
\end{longtable}
\end{center}
}
\section[eliassenPalmAMPKGScratch]{\hyperref[sec:var_sec_eliassenPalmAMPKGScratch]{eliassenPalmAMPKGScratch}}
\label{sec:var_tab_eliassenPalmAMPKGScratch}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_firstLayerBuoyCoor]{firstLayerBuoyCoor} & index, in buoyancy coordinates, of the first layer in column for a given cell \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_lastLayerBuoyCoor]{lastLayerBuoyCoor} & index, in buoyancy coordinates, of the last layer in column for a given cell \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_heightMidBuoyCoor]{heightMidBuoyCoor} & Height (z-coordinate) of buoyancy layer \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_heightTopBuoyCoor]{heightTopBuoyCoor} & Height (z-coordinate) at top of buoyancy layer \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_heightInterfaceBuoyCoor]{heightInterfaceBuoyCoor} & Height (z-coordinate) of the interfaces of buoyancy layer \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_sigma]{sigma} & Inverse of the derivative of buoyancy wrt z, aka thickness, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_montgPotBuoyCoor]{montgPotBuoyCoor} & Montgomery potential in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_montgPotNormalGradOnEdge]{montgPotNormalGradOnEdge} & Normal gradient of the montgomery potential in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_uMidBuoyCoor]{uMidBuoyCoor} & Longitudinal velocity at middle of layers in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_vMidBuoyCoor]{vMidBuoyCoor} & Meridional velocity at the middle of layers in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_densityMidBuoyCoor]{densityMidBuoyCoor} & In-situ density at middle of layers in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_densityTopBuoyCoor]{densityTopBuoyCoor} & In-situ density at top of layers in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_buoyancyMask]{buoyancyMask} & mask in buoyancy coordinates, ocean cells are 1 \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_montgPotGradX]{montgPotGradX} & x component of gradient of montgomery potential at cell center in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_montgPotGradY]{montgPotGradY} & y component of gradient of montgomery potential at cell center in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_montgPotGradZ]{montgPotGradZ} & z component of gradient of montgomery potential at cell center in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_montgPotGradZonal]{montgPotGradZonal} & Zonal component of gradient of montgomery potential at cell center in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_montgPotGradMerid]{montgPotGradMerid} & Meridional component of gradient of montgomery potential at cell center in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_wrk3DnVertLevelsP1]{wrk3DnVertLevelsP1} & work array \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_wrk3DnVertLevels]{wrk3DnVertLevels} & work array \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_wrk3DBuoyCoor]{wrk3DBuoyCoor} & work array \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_ErtelPVNormalGradOnEdge]{ErtelPVNormalGradOnEdge} & Normal gradient of EPV in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_ErtelPVGradX]{ErtelPVGradX} & X component of gradient of EPV in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_ErtelPVGradY]{ErtelPVGradY} & Y component of gradient of EPV in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_ErtelPVGradZ]{ErtelPVGradZ} & Z component of gradient of EPV in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_wrkVector]{wrkVector} & Work vector array \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_wrkTensor]{wrkTensor} & Work tensor array \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_array1_3D]{array1\_3D} & test array 1, in depth coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_array2_3D]{array2\_3D} & test array 2, in depth coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_array3_3D]{array3\_3D} & test array 3, in depth coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_array1_3Dbuoy]{array1\_3Dbuoy} & test array 1, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_array2_3Dbuoy]{array2\_3Dbuoy} & test array 2, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_PVMidBuoyCoor]{PVMidBuoyCoor} & Potential vorticity at cell center, in buoyancy coordinates \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_PVMidBuoyCoorEA]{PVMidBuoyCoorEA} & Potential vorticity at cell center, in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_uMidBuoyCoorEA]{uMidBuoyCoorEA} & Zonal velocity at cell center, in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_vMidBuoyCoorEA]{vMidBuoyCoorEA} & Meridional velocity at cell center, in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_uPVMidBuoyCoorEA]{uPVMidBuoyCoorEA} & Zonal velocity times Potential vorticity at cell center, in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_vPVMidBuoyCoorEA]{vPVMidBuoyCoorEA} & Meridional velocity times Potential vorticity at cell center, in buoyancy coordinates, ensemble average \\
    \hline
    \hyperref[subsec:var_sec_eliassenPalmAMPKGScratch_PVFluxTest]{PVFluxTest} & Potential vorticity flux test vector, in buoyancy coordinates \\
    \hline
\end{longtable}
\end{center}
}
\section[mixedLayerDepthsAM]{\hyperref[sec:var_sec_mixedLayerDepthsAM]{mixedLayerDepthsAM}}
\label{sec:var_tab_mixedLayerDepthsAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_mixedLayerDepthsAM_tThreshMLD]{tThreshMLD} & mixed layer depth based on temperature threshold \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerDepthsAM_tGradMLD]{tGradMLD} & mixed layer depth based on gradient of temperature \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerDepthsAM_dGradMLD]{dGradMLD} & mixed layer depth based on gradient of density \\
    \hline
\end{longtable}
\end{center}
}
\section[mixedLayerDepthAMScratch]{\hyperref[sec:var_sec_mixedLayerDepthAMScratch]{mixedLayerDepthAMScratch}}
\label{sec:var_tab_mixedLayerDepthAMScratch}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_mixedLayerDepthAMScratch_pressureAdjustedForLandIceScratch]{pressureAdjustedForLandIce\-Scratch} & temporary array to hold pressure  \\
    \hline
\end{longtable}
\end{center}
}
\section[regionalStatsAM]{\hyperref[sec:var_sec_regionalStatsAM]{regionalStatsAM}}
\label{sec:var_tab_regionalStatsAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_regionalStatsAM_regionalStatsOneString]{regionalStatsOneString} & a placeholder string so that regionalStats has a memory to duplicate per instance \\
    \hline
    \hyperref[subsec:var_sec_regionalStatsAM_regionalStatsOneInteger]{regionalStatsOneInteger} & a placeholder integer so that regionalStats has a memory to duplicate per instance \\
    \hline
    \hyperref[subsec:var_sec_regionalStatsAM_regionalStatsOneReal]{regionalStatsOneReal} & a placeholder real so that regionalStats has a memory to duplicate per instance \\
    \hline
\end{longtable}
\end{center}
}
\section[timeSeriesStatsAM]{\hyperref[sec:var_sec_timeSeriesStatsAM]{timeSeriesStatsAM}}
\label{sec:var_tab_timeSeriesStatsAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_timeSeriesStatsAM_timeSeriesStatsOneString]{timeSeriesStatsOneString} & {\bf \color{red} MISSING} \\
    \hline
    \hyperref[subsec:var_sec_timeSeriesStatsAM_timeSeriesStatsOneInteger]{timeSeriesStatsOneInteger} & {\bf \color{red} MISSING} \\
    \hline
    \hyperref[subsec:var_sec_timeSeriesStatsAM_timeSeriesStatsOneReal]{timeSeriesStatsOneReal} & {\bf \color{red} MISSING} \\
    \hline
\end{longtable}
\end{center}
}
\section[transectTransportAM]{\hyperref[sec:var_sec_transectTransportAM]{transectTransportAM}}
\label{sec:var_tab_transectTransportAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_transectTransportAM_transectEdgeMasksMax]{transectEdgeMasksMax} & max of transectEdgeMasks for this processor. \\
    \hline
    \hyperref[subsec:var_sec_transectTransportAM_transectVolumeTransport]{transectVolumeTransport} & Transport through transect of edges. \\
    \hline
    \hyperref[subsec:var_sec_transectTransportAM_transectVolumeTransportZ]{transectVolumeTransportZ} & Transport through transect of edges, with depth coordinate. \\
    \hline
\end{longtable}
\end{center}
}
\section[eddyProductVariablesAM]{\hyperref[sec:var_sec_eddyProductVariablesAM]{eddyProductVariablesAM}}
\label{sec:var_tab_eddyProductVariablesAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_SSHSquared]{SSHSquared} & cell-wise square of sea surface height \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityZonalSquared]{velocityZonalSquared} & cell-wise square of component of horizontal velocity in the eastward direction \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityMeridionalSquared]{velocityMeridionalSquared} & cell-wise square of component of horizontal velocity in the northward direction \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityZonalTimesTemperature]{velocityZonalTimesTemperature} & cell-wise product of component of horizontal velocity in the eastward direction and temperature \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityMeridionalTimesTemperature]{velocityMeridionalTimes\-Temperature} & cell-wise product of component of horizontal velocity in the northward direction and temperature \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_normalVelocitySquared]{normalVelocitySquared} & edge based square of normal velocity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_normalVelocityTimesTemperature]{normalVelocityTimesTemperature} & edge based product of normal velocity and temperature \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityZonalTimesTemperature_GM]{velocityZonalTimesTemperature\_\-GM} & cell-wise product of component of horizontal bolus velocity in the eastward direction and temperature \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityMeridionalTimesTemperature_GM]{velocityMeridionalTimes\-Temperature\_GM} & cell-wise product of component of horizontal bolus velocity in the northward direction and temperature \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_normalGMBolusVelocitySquared]{normalGMBolusVelocitySquared} & edge based square of normal velocity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_normalGMBolusVelocityTimesTemperature]{normalGMBolusVelocityTimes\-Temperature} & edge based product of normal velocity and temperature \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityZonalTimesSalinity]{velocityZonalTimesSalinity} & cell-wise product of component of horizontal velocity in the eastward direction and salinity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityMeridionalTimesSalinity]{velocityMeridionalTimesSalinity} & cell-wise product of component of horizontal velocity in the northward direction and salinity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_normalVelocityTimesSalinity]{normalVelocityTimesSalinity} & edge based product of normal velocity and salinity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityZonalTimesSalinity_GM]{velocityZonalTimesSalinity\_GM} & cell-wise product of component of horizontal bolus velocity in the eastward direction and salinity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityMeridionalTimesSalinity_GM]{velocityMeridionalTimesSalinity\_\-GM} & cell-wise product of component of horizontal bolus velocity in the northward direction and salinity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_normalGMBolusVelocityTimesSalinity]{normalGMBolusVelocityTimes\-Salinity} & edge based product of normal velocity and salinity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityZonalTimesTemperature_MLE]{velocityZonalTimesTemperature\_\-MLE} & cell-wise product of component of horizontal submeso velocity in the eastward direction and temperature \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityMeridionalTimesTemperature_MLE]{velocityMeridionalTimes\-Temperature\_MLE} & cell-wise product of component of horizontal submeso velocity in the northward direction and temperature \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_normalMLEVelocityTimesTemperature]{normalMLEVelocityTimes\-Temperature} & edge based product of normal velocity and temperature \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityZonalTimesSalinity_MLE]{velocityZonalTimesSalinity\_MLE} & cell-wise product of component of horizontal submeso velocity in the eastward direction and salinity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_velocityMeridionalTimesSalinity_MLE]{velocityMeridionalTimesSalinity\_\-MLE} & cell-wise product of component of horizontal submeso velocity in the northward direction and salinity \\
    \hline
    \hyperref[subsec:var_sec_eddyProductVariablesAM_normalMLEVelocityTimesSalinity]{normalMLEVelocityTimesSalinity} & edge based product of normal velocity and salinity \\
    \hline
\end{longtable}
\end{center}
}
\section[mocStreamfunctionAM]{\hyperref[sec:var_sec_mocStreamfunctionAM]{mocStreamfunctionAM}}
\label{sec:var_tab_mocStreamfunctionAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_mocStreamfunctionAM_mocStreamvalLatAndDepth]{mocStreamvalLatAndDepth} & The value of the MOC streamfunction for each latitude-bin (first dimension) and depth (second dimension) \\
    \hline
    \hyperref[subsec:var_sec_mocStreamfunctionAM_mocStreamvalLatAndDepthRegion]{mocStreamvalLatAndDepth\-Region} & The value of the MOC streamfunction for each latitude-bin (first dimension) and depth (second dimension) \\
    \hline
    \hyperref[subsec:var_sec_mocStreamfunctionAM_mocStreamvalLatAndDepthGM]{mocStreamvalLatAndDepthGM} & The value of the MOC streamfunction for each latitude-bin (first dimension) and depth (second dimension) based on the Gent McWilliams Bolus Velocity \\
    \hline
    \hyperref[subsec:var_sec_mocStreamfunctionAM_mocStreamvalLatAndDepthMLE]{mocStreamvalLatAndDepthMLE} & The value of the MOC streamfunction for each latitude-bin (first dimension) and depth (second dimension) based on the Submesoscale eddy Bolus Velocity \\
    \hline
    \hyperref[subsec:var_sec_mocStreamfunctionAM_mocStreamvalLatAndDepthRegionGM]{mocStreamvalLatAndDepth\-RegionGM} & The value of the MOC streamfunction for each latitude-bin (first dimension) and depth (second dimension) based on the Gent McWilliams Bolus Velocity \\
    \hline
    \hyperref[subsec:var_sec_mocStreamfunctionAM_mocStreamvalLatAndDepthRegionMLE]{mocStreamvalLatAndDepth\-RegionMLE} & The value of the MOC streamfunction for each latitude-bin (first dimension) and depth (second dimension) based on the Submesoscale eddy Bolus Velocity \\
    \hline
    \hyperref[subsec:var_sec_mocStreamfunctionAM_binBoundaryMocStreamfunction]{binBoundaryMocStreamfunction} & Coordinate of southern edge of meridional heat transport bin, either in latitude or y, for plotting. \\
    \hline
    \hyperref[subsec:var_sec_mocStreamfunctionAM_minMaxLatRegion]{minMaxLatRegion} & Coordinates of the southern and northern boundaries of each region (for drawing). \\
    \hline
\end{longtable}
\end{center}
}
\section[layeredOceanHeatContent]{\hyperref[sec:var_sec_layeredOceanHeatContent]{layeredOceanHeatContent}}
\label{sec:var_tab_layeredOceanHeatContent}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_layeredOceanHeatContent_oceanHeatContentSfcToBot]{oceanHeatContentSfcToBot} & Integrated heat content from surface to bottom \\
    \hline
    \hyperref[subsec:var_sec_layeredOceanHeatContent_oceanHeatContentSfcTo700m]{oceanHeatContentSfcTo700m} & Integrated heat content from the surface to 700m \\
    \hline
    \hyperref[subsec:var_sec_layeredOceanHeatContent_oceanHeatContent700mTo2000m]{oceanHeatContent700mTo2000m} & Integrated heat content from the 700m to 2000m \\
    \hline
    \hyperref[subsec:var_sec_layeredOceanHeatContent_oceanHeatContent2000mToBot]{oceanHeatContent2000mToBot} & Integrated heat content from the 2000m to bottom \\
    \hline
\end{longtable}
\end{center}
}
\section[mixedLayerHeatBudgetAM]{\hyperref[sec:var_sec_mixedLayerHeatBudgetAM]{mixedLayerHeatBudgetAM}}
\label{sec:var_tab_mixedLayerHeatBudgetAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_temperatureHorAdvectionMLTend]{temperatureHorAdvection\-MLTend} & ML average horizontal advection tendency for temperature \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_salinityHorAdvectionMLTend]{salinityHorAdvectionMLTend} & ML average horizontal advection tendency for salinity \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_temperatureVertAdvectionMLTend]{temperatureVertAdvection\-MLTend} & ML average vertical advection tendency for temperature \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_salinityVertAdvectionMLTend]{salinityVertAdvectionMLTend} & ML average vertical advection tendency for salinity \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_temperatureVertMixMLTend]{temperatureVertMixMLTend} & ML average vertical mixing tendency for temperature \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_salinityVertMixMLTend]{salinityVertMixMLTend} & ML average vertical mxiing tendency for salinity \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_temperatureHorMixMLTend]{temperatureHorMixMLTend} & ML average horizontal mixing tendency for temperature \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_salinityHorMixMLTend]{salinityHorMixMLTend} & ML average horizontal mxiing tendency for salinity \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_temperatureNonLocalMLTend]{temperatureNonLocalMLTend} & ML average non local kpp tendency for temperature \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_salinityNonLocalMLTend]{salinityNonLocalMLTend} & ML average nonlocal KPP tendency for salinity \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_temperatureForcingMLTend]{temperatureForcingMLTend} & ML average forcing tendency (including shortwave) for temperature \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_salinityForcingMLTend]{salinityForcingMLTend} & ML average forcing tendency (non thickness flux changes) for salinity \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_temperatureML]{temperatureML} & ML average temperature \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_salinityML]{salinityML} & ML average salinity \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_temperatureTendML]{temperatureTendML} & ML average temperature \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_salinityTendML]{salinityTendML} & ML average salinity \\
    \hline
    \hyperref[subsec:var_sec_mixedLayerHeatBudgetAM_bruntVaisalaFreqML]{bruntVaisalaFreqML} & ML average BVF \\
    \hline
\end{longtable}
\end{center}
}
\section[sedimentFluxIndexAM]{\hyperref[sec:var_sec_sedimentFluxIndexAM]{sedimentFluxIndexAM}}
\label{sec:var_tab_sedimentFluxIndexAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_sedimentFluxIndexAM_sedimentFluxIndexVAX]{sedimentFluxIndexVAX} & Index of Vertically-Averaged sediment flux in X-direction \\
    \hline
    \hyperref[subsec:var_sec_sedimentFluxIndexAM_sedimentFluxIndexVAY]{sedimentFluxIndexVAY} & Index of Vertically-Averaged sediment flux in Y-direction \\
    \hline
    \hyperref[subsec:var_sec_sedimentFluxIndexAM_sedimentFluxIndexBX]{sedimentFluxIndexBX} & Index of Bottom sediment flux in X-direction \\
    \hline
    \hyperref[subsec:var_sec_sedimentFluxIndexAM_sedimentFluxIndexBY]{sedimentFluxIndexBY} & Index of Bottom sediment flux in Y-direction \\
    \hline
\end{longtable}
\end{center}
}
\section[sedimentTransportAM]{\hyperref[sec:var_sec_sedimentTransportAM]{sedimentTransportAM}}
\label{sec:var_tab_sedimentTransportAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentFallVelocity]{sedimentFallVelocity} & Sediment settling velocity in the water column \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentErosionFlux]{sedimentErosionFlux} & bed sediment erosion flux \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentDepositionFlux]{sedimentDepositionFlux} & bed sediment deposition flux \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentFluxVAX]{sedimentFluxVAX} & Vertically-Averaged sediment flux in X-direction \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentFluxVAY]{sedimentFluxVAY} & Vertically-Averaged sediment flux in Y-direction \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentFluxBX]{sedimentFluxBX} & Bottom sediment flux in X-direction \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentFluxBY]{sedimentFluxBY} & Bottom sediment flux in Y-direction \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentBedloadX]{sedimentBedloadX} & Sediment bedload transport rate in X-direction \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentBedloadY]{sedimentBedloadY} & Sediment bedload transport rate in Y-direction \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentBottomReferenceConcentration]{sedimentBottomReference\-Concentration} & near-bottom suspended sediment concentration (reference concentration) \\
    \hline
    \hyperref[subsec:var_sec_sedimentTransportAM_sedimentConcentration]{sedimentConcentration} & suspended sediment concentration in water column \\
    \hline
\end{longtable}
\end{center}
}
\section[harmonicAnalysisAM]{\hyperref[sec:var_sec_harmonicAnalysisAM]{harmonicAnalysisAM}}
\label{sec:var_tab_harmonicAnalysisAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_nAnalysisConstituents]{nAnalysisConstituents} & Number of tidal constituents used in analysis \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_analysisConstituentFrequency]{analysisConstituentFrequency} & Frequency of each constituent \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_analysisConstituentNodalAmplitude]{analysisConstituentNodal\-Amplitude} & Frequency of each constituent \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_analysisConstituentNodalPhase]{analysisConstituentNodalPhase} & Frequency of each constituent \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_leastSquaresLHSMatrix]{leastSquaresLHSMatrix} & Frequency of each constituent \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_leastSquaresRHSVector]{leastSquaresRHSVector} & Frequency of each constituent \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_decomposedConstituentAmplitude]{decomposedConstituent\-Amplitude} & Amplitude of each tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_decomposedConstituentPhase]{decomposedConstituentPhase} & Phase of each tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_M2Amplitude]{M2Amplitude} & Amplitude of M2 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_M2Phase]{M2Phase} & Phase of M2 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_S2Amplitude]{S2Amplitude} & Amplitude of S2 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_S2Phase]{S2Phase} & Phase of S2 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_N2Amplitude]{N2Amplitude} & Amplitude of N2 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_N2Phase]{N2Phase} & Phase of N2 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_K2Amplitude]{K2Amplitude} & Amplitude of K2 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_K2Phase]{K2Phase} & Phase of K2 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_K1Amplitude]{K1Amplitude} & Amplitude of K1 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_K1Phase]{K1Phase} & Phase of K1 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_O1Amplitude]{O1Amplitude} & Amplitude of O1 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_O1Phase]{O1Phase} & Phase of O1 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_Q1Amplitude]{Q1Amplitude} & Amplitude of Q1 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_Q1Phase]{Q1Phase} & Phase of Q1 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_P1Amplitude]{P1Amplitude} & Amplitude of P1 tidal constituent at each cell center \\
    \hline
    \hyperref[subsec:var_sec_harmonicAnalysisAM_P1Phase]{P1Phase} & Phase of P1 tidal constituent at each cell center \\
    \hline
\end{longtable}
\end{center}
}
\section[conservationCheckAM]{\hyperref[sec:var_sec_conservationCheckAM]{conservationCheckAM}}
\label{sec:var_tab_conservationCheckAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_conservationCheckAM_performConservationPrecompute]{performConservationPrecompute} & {\bf \color{red} MISSING} \\
    \hline
\end{longtable}
\end{center}
}
\section[conservationCheckEnergyAM]{\hyperref[sec:var_sec_conservationCheckEnergyAM]{conservationCheckEnergyAM}}
\label{sec:var_tab_conservationCheckEnergyAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_initialEnergy]{initialEnergy} & Total initial energy of ice and snow \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_finalEnergy]{finalEnergy} & Total final energy of ice and snow \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_energyChange]{energyChange} & Total energy change of ice and snow during time step \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_netEnergyFlux]{netEnergyFlux} & Net energy flux to ice \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_absoluteEnergyError]{absoluteEnergyError} & Absolute energy conservation error \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_relativeEnergyError]{relativeEnergyError} & Relative energy conservation error \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedLatentHeatFlux]{accumulatedLatentHeatFlux} & Latent heat flux from coupler, integrated in space and time. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedSensibleHeatFlux]{accumulatedSensibleHeatFlux} & Sensible heat flux from coupler, integrated in space and time. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedLongWaveHeatFluxUp]{accumulatedLongWaveHeatFlux\-Up} & Upward long Wave heat flux from coupler, integrated in space and time. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedLongWaveHeatFluxDown]{accumulatedLongWaveHeatFlux\-Down} & Downward long wave heat flux from coupler, integrated in space and time. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedShortWaveHeatFlux]{accumulatedShortWaveHeatFlux} & shortwave heat flux from coupler, integrated in space and time. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedSeaIceHeatFlux]{accumulatedSeaIceHeatFlux} & Sea ice heat flux from coupler, integrated in space and time. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedMeltingSnowHeatFlux]{accumulatedMeltingSnowHeat\-Flux} & This is snowFlux * latent\_heat\_fusion\_mks. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedMeltingIceRunoffHeatFlux]{accumulatedMeltingIceRunoff\-HeatFlux} & This is iceRunoffFlux * latent\_heat\_fusion\_mks. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedRemovedIceRunoffHeatFlux]{accumulatedRemovedIceRunoff\-HeatFlux} & This is iceRunoffFlux * latent\_heat\_fusion\_mks. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedIcebergHeatFlux]{accumulatedIcebergHeatFlux} & Iceberg heat flux from coupler, integrated in space and time. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedFrazilHeatFlux]{accumulatedFrazilHeatFlux} & Heat flux from frazil, integrated in space and time, given to couipler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedLandIceHeatFlux]{accumulatedLandIceHeatFlux} & Land ice heat flux, integrated in space and time. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedLandIceFrazilHeatFlux]{accumulatedLandIceFrazilHeat\-Flux} & Land ice heat flux from frazil, integrated in space and time, given to couipler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedRainTemperatureFlux]{accumulatedRainTemperature\-Flux} & Heat flux associated with rain. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedEvapTemperatureFlux]{accumulatedEvapTemperature\-Flux} & Heat flux associated with Evaporation. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedSeaIceTemperatureFlux]{accumulatedSeaIceTemperature\-Flux} & Heat flux associated with sea ice melt water. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedRiverRunoffTemperatureFlux]{accumulatedRiverRunoff\-TemperatureFlux} & Heat flux associated with river runoff. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckEnergyAM_accumulatedIcebergTemperatureFlux]{accumulatedIcebergTemperature\-Flux} & Heat flux associated with iceberg melt. Positive into the ocean. \\
    \hline
\end{longtable}
\end{center}
}
\section[conservationCheckMassAM]{\hyperref[sec:var_sec_conservationCheckMassAM]{conservationCheckMassAM}}
\label{sec:var_tab_conservationCheckMassAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_initialMass]{initialMass} & Total initial mass of ice and snow \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_finalMass]{finalMass} & Total final mass of ice and snow \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_massChange]{massChange} & Total mass change of ice and snow during time step \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_netMassFlux]{netMassFlux} & Net mass flux to ice \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_absoluteMassError]{absoluteMassError} & Absolute mass conservation error \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_relativeMassError]{relativeMassError} & Relative mass conservation error \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedRainFlux]{accumulatedRainFlux} & Fresh water flux from rain from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedSnowFlux]{accumulatedSnowFlux} & Fresh water flux from snow from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedEvaporationFlux]{accumulatedEvaporationFlux} & Evaporation flux from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedSeaIceFlux]{accumulatedSeaIceFlux} & Fresh water flux from sea ice from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedRiverRunoffFlux]{accumulatedRiverRunoffFlux} & Fresh water flux from river runoff from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedIceRunoffFlux]{accumulatedIceRunoffFlux} & Fresh water flux from ice runoff from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedRemovedRiverRunoffFlux]{accumulatedRemovedRiverRunoff\-Flux} & Fresh water flux from river runoff from the coupler that was removed due to config\_remove\_AIS\_coupler\_runoff option. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedRemovedIceRunoffFlux]{accumulatedRemovedIceRunoff\-Flux} & Fresh water flux from ice runoff from the coupler that was removed due to config\_remove\_AIS\_coupler\_runoff option. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedIcebergFlux]{accumulatedIcebergFlux} & Fresh water flux from iceberg melt from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedFrazilFlux]{accumulatedFrazilFlux} & Fresh water flux from frazil freezing under sea ice. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedLandIceFlux]{accumulatedLandIceFlux} & Fresh water flux from land ice melt from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckMassAM_accumulatedLandIceFrazilFlux]{accumulatedLandIceFrazilFlux} & Fresh water flux from frazil freezing under land ice. Positive into the ocean. \\
    \hline
\end{longtable}
\end{center}
}
\section[conservationCheckSaltAM]{\hyperref[sec:var_sec_conservationCheckSaltAM]{conservationCheckSaltAM}}
\label{sec:var_tab_conservationCheckSaltAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_conservationCheckSaltAM_initialSalt]{initialSalt} & Total initial salt of ice and snow \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckSaltAM_finalSalt]{finalSalt} & Total final salt of ice and snow \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckSaltAM_saltChange]{saltChange} & Total salt change of ice and snow during time step \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckSaltAM_netSaltFlux]{netSaltFlux} & Net salt flux to ice \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckSaltAM_absoluteSaltError]{absoluteSaltError} & Absolute salt conservation error \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckSaltAM_relativeSaltError]{relativeSaltError} & Relative salt conservation error \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckSaltAM_accumulatedSeaIceSalinityFlux]{accumulatedSeaIceSalinityFlux} & Sea ice salinity flux from coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckSaltAM_accumulatedFrazilSalinityFlux]{accumulatedFrazilSalinityFlux} & Salinity flux from frazil to sea ice, given to coupler. Positive into the ocean. \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckSaltAM_accumulatedLandIceFrazilSalinityFlux]{accumulatedLandIceFrazil\-SalinityFlux} & Salinity flux from frazil to Land Ice, given to coupler. Positive into the ocean. \\
    \hline
\end{longtable}
\end{center}
}
\section[conservationCheckCarbonAM]{\hyperref[sec:var_sec_conservationCheckCarbonAM]{conservationCheckCarbonAM}}
\label{sec:var_tab_conservationCheckCarbonAM}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_initialCarbon]{initialCarbon} & Total ocean carbon at start of conservation interval \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_finalCarbon]{finalCarbon} & Total ocean carbon at end of conservation interval \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_carbonChange]{carbonChange} & Change in ocean carbon over conservation interval \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_netCarbonFlux]{netCarbonFlux} & Net surface flux of ocean carbon over conservation interval \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_absoluteCarbonError]{absoluteCarbonError} & Absolute carbon conservation error over conservation interval \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_relativeCarbonError]{relativeCarbonError} & Relative carbon conservation error over conservation interval \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_accumulatedAbsoluteCarbonError]{accumulatedAbsoluteCarbon\-Error} & Accumulated absolute carbon conservation error over entire simulation \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_accumulatedRelativeCarbonError]{accumulatedRelativeCarbonError} & Accumulated relative carbon conservation error over entire simulation \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_accumulatedCarbonSourceSink]{accumulatedCarbonSourceSink} & Volume integral of all carbon source-sink terms from MarBL \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_accumulatedCarbonSedimentFlux]{accumulatedCarbonSedimentFlux} & Surface integral of all carbon sediment fluxes \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_accumulatedCarbonSurfaceFlux]{accumulatedCarbonSurfaceFlux} & Surface integral of all carbon ocean surface fluxes \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_accumulatedCarbonTend]{accumulatedCarbonTend} & Volume integral of all carbon-containing prognostic variable tendencies \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_accumulatedCO2gasFlux]{accumulatedCO2gasFlux} & Surface integral of air-sea CO2 gas flux \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_accumulatedIceOceanOrganicCarbonFlux]{accumulatedIceOceanOrganic\-CarbonFlux} & Surface integral of all organic ice-ocean carbon fluxes \\
    \hline
    \hyperref[subsec:var_sec_conservationCheckCarbonAM_accumulatedIceOceanInorganicCarbonFlux]{accumulatedIceOceanInorganic\-CarbonFlux} & Surface integral of all inorganic ice-ocean carbon fluxes \\
    \hline
\end{longtable}
\end{center}
}
\section[landIceInit]{\hyperref[sec:var_sec_landIceInit]{landIceInit}}
\label{sec:var_tab_landIceInit}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_landIceInit_landIceDraftObserved]{landIceDraftObserved} & z-coordinate of land ice bottom, read in from data file \\
    \hline
    \hyperref[subsec:var_sec_landIceInit_landIceThkObserved]{landIceThkObserved} & Thickness of land ice, read in from data file \\
    \hline
    \hyperref[subsec:var_sec_landIceInit_landIceFracObserved]{landIceFracObserved} & Fraction of land ice, read in from data file \\
    \hline
    \hyperref[subsec:var_sec_landIceInit_landIceGroundedFracObserved]{landIceGroundedFracObserved} & Fraction of grounded land ice, read in from data file \\
    \hline
\end{longtable}
\end{center}
}
\section[criticalPassages]{\hyperref[sec:var_sec_criticalPassages]{criticalPassages}}
\label{sec:var_tab_criticalPassages}
\vspace{0.5in}
{\small
\begin{center}
\begin{longtable}{| p{2.0in} | p{4.0in} |}
    \hline
    {\bf Name} & {\bf Description} \endfirsthead
    \hline 
    {\bf Name} & {\bf Description} (Continued) \endhead
    \hline
    \hyperref[subsec:var_sec_criticalPassages_transectCellMasks]{transectCellMasks} & Masks for transects describing critical passages \\
    \hline
    \hyperref[subsec:var_sec_criticalPassages_depthTransects]{depthTransects} & Minimum depth of critical passages \\
    \hline
    \hyperref[subsec:var_sec_criticalPassages_criticalPassageLevel]{criticalPassageLevel} & the vertical level corresponding to the depth of the critical passage \\
    \hline
\end{longtable}
\end{center}
}
